### 2020-11-03 docs/src/assets/tex/pipeline.tex
Add more tests

\documentclass[tikz, convert=pdf2svg]{standalone}

\usepackage{tikz}
\tikzset{>=stealth}
\usetikzlibrary{shapes,arrows}

% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text centered, rounded corners, minimum height=2.5em]
\tikzstyle{input} = [rectangle, draw, fill=green!20, 
    text centered, rounded corners, minimum height=2.5em]
\tikzstyle{line} = [draw, ->]
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

\usetikzlibrary{arrows.meta}
\tikzset{%
      >={Latex[width=2mm,length=2mm]},
}
\begin{document}
    \begin{tikzpicture}[node distance=2.2cm,
    every node/.style={fill=white, font=\sffamily}, align=center]

        \node[block] (start) {rec \\(variables to optimize for)};
        \node[block, below of=start] (map) {Mapping \\ \footnotesize (sets constraints like positivity)};
        \node[block, below of=map, left of=map] (forw) {Forward \\\footnotesize(convolution)};
        \node[block, below of=forw] (loss) {Loss};
        \node[block, below of=loss, right of=map] (reg) {Regularizer};

        \node[block, below of=map, node distance=6cm] (tloss) {Total Loss};
        \node[cloud, below of=tloss, node distance=2cm] (opt) {Optimizer\\\footnotesize (Optim.jl)};

        \node[input, left of=forw, above of=forw] (psf) {PSF}; 
        \node[input, left of=loss, node distance=2.5cm] (meas) {Measured};

        \path [line] (start) -- (map);
        \path [line] (map) -| (reg);
        \path [line] (map) -| (forw);
        \path [line] (forw) -- (loss);
        \path [line] (loss) -- (tloss);
        \path [line] (tloss) -- (opt);
        \path [line] (reg) --node [midway] {Weighting with $\lambda \cdot$} (tloss) ;

        \path[line] (opt) --++ (5, 0) --++ (0, 10.2) node[] {AD calculates gradient \\ to optimize for rec} -- (start) ;

        \path [line] (psf)-- (forw);
        \path [line] (meas)-- (loss);
    \end{tikzpicture}
\end{document}

### 2020-11-03 test/forward_models.jl

@@ -1,0 +1,16 @@
+@testset "Forward Models: Convolution" begin
+
+    N = 5
+    psf = zeros((N, N))
+    psf[1, 1] = 1
+    img = randn((N, N))
+    
+    c(img, psf) = conv_psf(img, psf, [1, 2])
+    conv(img, psf) = DeconvOptim.conv_aux(c, img, psf)
+
+    @test conv(img, psf) ≈ img 
+    s(img, psf) = sum(conv(img, psf))
+    
+    @test all(1 .≈ Zygote.gradient(s, img, psf)[1])
+
+end

### 2020-11-03 test/lossfunctions.jl

@@ -1,0 +1,32 @@
+@testset "Poisson loss" begin
+    N = 6
+    img = abs.(randn((N, N)))
+
+    @test 0.22741127776021886 ≈ poisson_aux([1.,2.], [3.,4.]) 
+
+    @test all(0 .≈ Zygote.gradient(poisson_aux, img, img)[1])
+    
+    @test all( -1 .≈ Zygote.gradient(poisson_aux, [1.], [2.])[1])
+end
+
+
+@testset "Gaussian Loss" begin
+    N = 6
+    img = abs.(randn((N, N)))
+    @test 0 ≈ gauss_aux(img, img)
+    
+    @test all(0 .≈ Zygote.gradient(gauss_aux, img, img)[1])
+
+end
+
+
+@testset "Scaled Gauss" begin
+    N = 6
+    img = abs.(randn((N, N)))
+    
+    @test 1.7047189562170502 ≈ scaled_gauss_aux([5.], [2.]) 
+    
+    @test all( -1 .≈ Zygote.gradient(scaled_gauss_aux, [1.], [2.])[1])
+
+
+end

### 2020-11-03 test/main.jl

@@ -1,0 +1,19 @@
+@testset "Testing Main deconvolution code" begin
+    Random.seed!(42)
+
+    img = randn((3, 3))
+    psf = randn((3, 3))
+    
+    res = [2.2651480070562995 0.37020823409183323 0.60212775719812; 0.002927465797471582 0.012945404132307292 0.1377756221162511; 0.3971985245368018 0.00019987879871227046 0.31339228191542085]
+    @test all(res .≈ deconvolution(img, psf)[1])
+    @test all(res .≈ deconvolution(img, psf, plan_fft=false)[1])
+    @test all(res .≈ deconvolution(img, psf, plan_fft=false, iterations=50)[1])
+
+    res2 = [2.2607906616359643 0.3655684460899124 0.6031252012437225; 0.0026905888577756073 0.013530167239603945 0.13853059609167315; 0.3985361939201093 0.0001444152709048845 0.3084041861830485]
+    @test all(res2 .≈ deconvolution(img, psf, regularizer=nothing, padding=0.0)[1])
+   
+    img = abs.(20 .* randn((3, 3)))
+    psf = abs.(randn((3, 3)))
+    res3 = [3.244891818080811 17.141098646772267 0.0007561293841754774; 0.034517228270906045 9.034036257026907 0.2063824116147499; 0.0015189996589895396 41.21712794995631 32.96060746230941]
+    @show all(res3 .≈ deconvolution(img, psf, regularizer=nothing, padding=0.1)[1])
+end

### 2020-11-03 test/mappings.jl

@@ -1,0 +1,27 @@
+
+
+@testset "Non_negative" begin
+
+    p, p_inv = Non_negative()
+
+    x = abs.(randn((10, 10)))
+    x2 = 100 .*randn((10, 10))
+
+    @test x ≈ p(p_inv(x))
+    @test x ≈ p_inv(p(x))
+
+    @test all(p(x2) .>= 0)
+end
+
+@testset "Map_0_1" begin
+
+    p, p_inv = Map_0_1()
+
+    x = abs.(randn((10, 10)))
+    x2 = 100 .*randn((10, 10))
+
+    @test x ≈ p_inv(p(x))
+
+    @test all(p(x2) .>= 0)
+    @test all(p(x2) .<= 1)
+end

### 2020-11-03 test/regularizer.jl

@@ -1,0 +1,9 @@
+@testset "Good's roughness" begin
+    Random.seed!(42)
+    img = abs.(100 .* randn((50, 50)))
+
+    reg = GR()
+    reg2 = GR(weights=[2,2])
+
+
+end

### 2020-11-03 test/runtests.jl
Modify existing tests

@@ -1,8 +1,9 @@
 using DeconvOptim
 using Test
-using FFTW, Noise, Statistics
+using FFTW, Noise, Statistics, Zygote
 using Random
 
+ # fix seed for reproducibility
 Random.seed!(42)
 
 @testset "Utils" begin
@@ -10,3 +11,13 @@ Random.seed!(42)
 end
 
 
+include("mappings.jl")
+
+include("forward_models.jl")
+
+include("lossfunctions.jl")
+
+ # testing is rather hard, but include at least some basic testing
+include("regularizer.jl")
+
+include("main.jl")

### 2020-11-03 test/utils.jl

@@ -15,6 +15,14 @@ end
     center_test(5, 4, 4, 7, 8, 4)
     center_test(5, 4, 4, 8, 8, 8)
     center_test(6, 4, 4, 7, 8, 8)
+
+
+    @test 1 == center_pos(1)
+    @test 2 == center_pos(2)
+    @test 2 == center_pos(3)
+    @test 3 == center_pos(4)
+    @test 3 == center_pos(5)
+    @test 513 == center_pos(1024)
 end
 
 
@@ -33,6 +41,15 @@ end
     y = my_interpolate(x, size(x)[1] * 3 + 2)
     y2 = my_interpolate(y, size(x)[1])
     @test isapprox(y2, x, rtol=1e-6)
+
+    
+    x = [12,2,2,1,2,4,3,1]
+    y = [12, 7, 2, 2, 2, 1.5, 1, 1.5, 2, 3, 4, 3.5, 3, 2, 1]
+    y_2d = reshape(y, 1, :)
+    x_2d = my_interpolate(reshape(x, 1, :), size(y_2d))
+    @test isapprox(x_2d, y_2d, rtol=1e-6)
+
+     
 end
 
 
@@ -82,3 +99,51 @@ end
     conv_test(psf, img, img, dims, "Convolution with 5D delta peak and random 5D image over 4 Dimensions")
 
 end
+
+
+@testset "Generate downsample" begin
+    ds = generate_downsample(2, [1,2], 2)
+    @test [2.5] ≈ ds([1 2; 3 4]) 
+    
+    ds = generate_downsample(2, [2], 2)
+    @test [1.5; 3.5; 5.5; 7.5] ≈ ds([1 2; 3 4; 5 6; 7 8]) 
+    
+    ds = generate_downsample(2, [1], 2)
+    @test [2.0 3.0; 6.0 7.0] ≈ ds([1 2; 3 4; 5 6; 7 8]) 
+end
+
+
+@testset "Generate PSF method" begin
+    # large aperture is delta peak
+    out = zeros((5, 5))
+    out[1,1] = 1
+    
+    @test out ≈ generate_psf((5, 5), 100)
+
+    # pinhole aperture
+    out = ones((10, 10))
+    out ./= sum(out)
+    @test out ≈ generate_psf((10, 10), 0.01)
+    
+    # normalized
+    @test 1 ≈ sum(generate_psf((100, 100), 10))
+end
+
+
+
[…]

### 2020-11-03 src/regularizer.jl
Minor fixes in regularizer

@@ -135,7 +135,11 @@ of a n-dimensional array.
 To create a regularizer for a 3D dataset where the third dimension
 has different contribution.
 ```julia-repl
-julia> Tikhonov(sum_dims=[1, 2, 3], weights=[1, 1, 0.25])
+julia> reg = Tikhonov(num_dim=2, sum_dims=[1, 2], weights=[1, 1], mode="identity")
+#97 (generic function with 1 method)
+
+julia> reg([1 2 3; 4 5 6; 7 8 9])
+285
 ```
 """
 function Tikhonov(;num_dim=2, sum_dims=[1, 2], weights=[1, 1], step=1, mode="laplace")
@@ -198,11 +202,15 @@ of a n-dimensional array.
 To create a regularizer for a 3D dataset where the third dimension
 has different contribution. For the derivative we use forward mode.
 ```julia-repl
-julia> GR(sum_dims=[1, 2, 3], weights=[1, 1, 0.25], mode="forward")
+julia> reg = GR(num_dim=2, sum_dims=[1, 2], weights=[1, 1], mode="forward")
+... (generic function with 1 method)
+
+julia> reg([1 2 3; 4 5 6; 7 8 9])
+-26.36561871738898
 ```
 """
 function GR(; num_dim=2, sum_dims=[1, 2], weights=[1, 1], step=1,
-              mode="central", ϵ=1f-6)
+              mode="central", ϵ=1f-8)
     if mode == "central"
         GRf = @eval arr -> ($(generate_GR(num_dim, sum_dims, weights,
                                         step, (-1) * step)...))
@@ -247,8 +255,8 @@ This function returns a function to calculate the Total Variation regularizer
 of a n-dimensional array. 
 # Arguments
 - `num_dim=2`: 
-- `sum_dims=[1, 2, 3]`: A array containing the dimensions we want to sum over
-- `weights=[1, 1, 0.25]`: A array containing weights to weight the contribution of 
+- `sum_dims=[1, 2]`: A array containing the dimensions we want to sum over
+- `weights=[1, 1]`: A array containing weights to weight the contribution of 
     different dimensions
 - `step=1`: A integer indicating the step width for the array indexing
 - `mode="central"`: Either `"central"` or `"forward"` accounting for different
@@ -257,7 +265,11 @@ of a n-dimensional array.
 To create a regularizer for a 3D dataset where the third dimension
[…]

### 2020-11-03 src/mappings.jl
Clean mappings

@@ -1,62 +1,57 @@
 export Non_negative
-export Non_negative2
-export Non_negative3
 export Map_0_1
-export Exp
  
 
  # All these functions return a mapping function and 
  # the inverse of it 
  # they are used to map the real numbers to non-negative real numbers
+
+
+"""
+    Non_negative()
+
+Returns a function and a inverse function inverse function
+to map numbers to non-negative numbers.
+We use a parabola.
+
+# Examples
+```julia-repl
+julia> p, p_inv = Non_negative()
+(DeconvOptim.var"#5#7"(), DeconvOptim.var"#6#8"())
+
+julia> x = [-1, 2, -3]
+3-element Array{Int64,1}:
+ -1
+  2
+ -3
+
+julia> p(x)
+3-element Array{Int64,1}:
+ 1
+ 4
+ 9
+
+julia> p_inv(p(x))
+3-element Array{Float64,1}:
+ 1.0
+ 2.0
+ 3.0
+```
+"""
 function Non_negative()
     return x -> map(abs2, x) , (x -> sqrt.(x))
 end
 
 
+"""
+    Map_0_1()
 
+Returns a function and a inverse function inverse function
+to map numbers to an interval between 0 and 1. 
 
- # old functions with old semantics
- # leave them here unused. Will be replaced in future
+"""
 function Map_0_1()
     f(x) = 1 .- exp.(.- x.^2)
-    ∇f(x) = 2 .* x .* exp.(.- x.^2)
-    f_inv(x) = sqrt.(.- log.(1 .- min.(1, x)))
-    return f, ∇f, f_inv
-end
-
-
-function Exp()
-    return (x -> exp.(x)), (x -> exp.(x)) , (x -> log.(x))
-end
-
-
-function Non_negative3()
-    function ∇f(x)
-        if x > 0
-            return 1
-        elseif x < 0 
-            return -1
-        else
-            return 0
-        end
-    end
-    return (x -> abs.(x)), (x -> ∇f.(x)),  (x -> abs.(x))
-end
-
-
-function Non_negative2()
-    f1(x) = 1 / (1 - x)
-    ∇f1(x) = 1 / (1 - x) ^ 2
-    f1_inv(y) = 1 - 1 / y
-
-
-    f2(x) = (x + 0.5) ^ 2 + 0.75
[…]

### 2020-11-03 src/lossfunctions.jl
Fixes in lsosfunctions

@@ -1,6 +1,6 @@
 export Poisson, poisson_aux
 export Gauss, gauss_aux
-export ScaledGauss, scaled_gauss
+export ScaledGauss, scaled_gauss_aux
 
 
 """

### 2020-11-03 dev/search_index.js
build based on 686c5a6

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/regularizer/#Regularizers","page":"Regularizers","title":"Regularizers","text":"","category":"section"},{"location":"function_references/regularizer/","page":"Regularizers","title":"Regularizers","text":"TV\nTikhonov\nGR","category":"page"},{"location":"function_references/regularizer/#DeconvOptim.TV","page":"Regularizers","title":"DeconvOptim.TV","text":"TV(; <keyword arguments>)\n\nThis function returns a function to calculate the Total Variation regularizer of a n-dimensional array. \n\nArguments\n\nnum_dim=2: \nsum_dims=[1, 2, 3]: A array containing the dimensions we want to sum over\nweights=[1, 1, 0.25]: A array containing weights to weight the contribution of    different dimensions\nstep=1: A integer indicating the step width for the array indexing\nmode=\"central\": Either \"central\" or \"forward\" accounting for different   modes of the spatial gradient. Default is \"central\".\n\nExamples\n\nTo create a regularizer for a 3D dataset where the third dimension has different contribution. For the derivative we use forward mode.\n\njulia> TV(num_dim=3, sum_dims=[1, 2, 3], weights=[1, 1, 0.25], mode=\"forward\")\n\n\n\n\n\n","category":"function"},{"location":"function_references/regularizer/#DeconvOptim.Tikhonov","page":"Regularizers","title":"DeconvOptim.Tikhonov","text":"Tikhonov(; <keyword arguments>)\n\nThis function returns a function to calculate the Tikhonov regularizer of a n-dimensional array. \n\nArguments\n\nnum_dim=2: \nsum_dims=[1, 2]: A array containing the dimensions we want to sum over\nweights=[1, 1]: A array containing weights to weight the contribution of    different dimensions\nstep=1: A integer indicating the step width for the array indexing\nmode=\"laplace\": Either \"laplace\", \"spatial_grad_square\", \"identity\" accounting for different   modes of the Tikhonov regularizer. Default is \"laplace\".\n\nExamples\n\nTo create a regularizer for a 3D dataset where the third dimension has different contribution.\n\njulia> Tikhono
[…]

### 2020-11-03 test/main.jl
Fix broadcasting of PSF

@@ -9,11 +9,33 @@
     @test all(res .≈ deconvolution(img, psf, plan_fft=false)[1])
     @test all(res .≈ deconvolution(img, psf, plan_fft=false, iterations=50)[1])
 
+    # testing regularizer
     res2 = [2.2607906616359643 0.3655684460899124 0.6031252012437225; 0.0026905888577756073 0.013530167239603945 0.13853059609167315; 0.3985361939201093 0.0001444152709048845 0.3084041861830485]
     @test all(res2 .≈ deconvolution(img, psf, regularizer=nothing, padding=0.0)[1])
    
+    # testing padding
     img = abs.(20 .* randn((3, 3)))
     psf = abs.(randn((3, 3)))
     res3 = [3.244891818080811 17.141098646772267 0.0007561293841754774; 0.034517228270906045 9.034036257026907 0.2063824116147499; 0.0015189996589895396 41.21712794995631 32.96060746230941]
-    @show all(res3 .≈ deconvolution(img, psf, regularizer=nothing, padding=0.1)[1])
+    @test all(res3 .≈ deconvolution(img, psf, regularizer=nothing, padding=0.1)[1])
+
+
+    # test without mapping
+    res4 = [-19.24648922082771 39.61274950533089 -15.220294412294914; -18.611821434506325 59.7605384098004 1.8270388012669567; 9.25158195360382 -4.14983150380469 33.25226235037082]
+    @test all(res4 .≈ deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1])
+
+
+    
+    # test broadcasting with image having more dimensions
+    img = zeros((3, 3, 2))
+    imgc = randn((3, 3, 1))
+    img[:, :, 1] = imgc
+    img[:, :, 2] = imgc
+    psf = zeros((3, 3))
+    psf[1,1] = 1
+   
+    res = deconvolution(img, psf, regularizer=GR(num_dims=3, sum_dims=[1,2]))[1]
+    @test all(res[:, :, 1] .≈ res[:, :, 2]) 
+
+
 end

### 2020-11-03 test/lossfunctions.jl
Add test cases for lossfunctions

@@ -13,6 +13,10 @@ end
 @testset "Gaussian Loss" begin
     N = 6
     img = abs.(randn((N, N)))
+
+    gauss = Gauss()
+    @test 0 ≈ gauss(img, img)
+
     @test 0 ≈ gauss_aux(img, img)
     
     @test all(0 .≈ Zygote.gradient(gauss_aux, img, img)[1])
@@ -24,6 +28,9 @@ end
     N = 6
     img = abs.(randn((N, N)))
     
+    scaled_gauss = ScaledGauss()
+    
+    @test 1.7047189562170502 ≈ scaled_gauss([5.], [2.]) 
     @test 1.7047189562170502 ≈ scaled_gauss_aux([5.], [2.]) 
     
     @test all( -1 .≈ Zygote.gradient(scaled_gauss_aux, [1.], [2.])[1])

### 2020-11-03 src/regularizer.jl
Renaming to num_dim to num_dims in regularizer

@@ -15,10 +15,10 @@ export generate_spatial_grad_square, generate_GR, generate_TV
 
 
 """
-    generate_indices(num_dim, d, ind1, ind2)
+    generate_indices(num_dims, d, ind1, ind2)
 Generates a list of symbols which can be used to generate Tullio expressions
 via metaprogramming.
-`num_dim` is the total number of dimensions.
+`num_dims` is the total number of dimensions.
 `d` is the dimension where there is a offset in the index.
 `ind1` and `ind2` are the offsets each.
  # Examples
@@ -27,17 +27,17 @@ julia> a, b = generate_indices(5, 2, 1, 1)
 (Any[:i1, :(i2 + 1), :i3, :i4, :i5], Any[:i1, :(i2 + 1), :i3, :i4, :i5])
 ```
 """
-function generate_indices(num_dim, d, ind1, ind2)
+function generate_indices(num_dims, d, ind1, ind2)
     # create initial symbol
     ind = :i
     # create the array of symbols for each dimension
-    inds1 = map(1:num_dim) do di
+    inds1 = map(1:num_dims) do di
         # map over numbers and append the number of the position to symbol i
         i = Symbol(ind, di)
         # at the dimension where we want to do the step, add $ind1
         di == d ? :($i + $ind1) : i
     end
-    inds2 = map(1:num_dim) do di
+    inds2 = map(1:num_dims) do di
         i = Symbol(ind, di)
         # here we do the step but in the other dimension. ind2 should be 
         # (-1) * ind1 or negative
@@ -48,13 +48,13 @@ end
 
 
 """
-    generate_laplace(num_dim, sum_dims_arr, weights)
+    generate_laplace(num_dims, sum_dims_arr, weights)
 Generate the Tullio statement for computing the Laplacian.
-`num_dim` is the dimension of the array. 
+`num_dims` is the dimension of the array. 
 `sum_dims_arr` is a array indicating over which dimensions we must sum over.
 `weights` is a array of a weight for the different dimension.
 """
-function generate_laplace(num_dim, sum_dims_arr, weights)
+function generate_laplace(num_dims, sum_dims_arr, weights)
     # create out list for the final expression
     # add accumulates the different add expressions
     out, add = [], []
@@ -62,17 +62,17 @@ function generate_laplace(num_dim, sum_dims_arr, weights)
[…]

### 2020-11-03 src/DeconvOptim.jl
Fix broadcasting of PSF

@@ -119,10 +119,19 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
     # the dimensions we do the Fourier Transform over
     fft_dims = collect(1:ndims(psf)) 
 
-    # psf_n is the psf with the same size as rec0
+    # psf_n is the psf with the same size as rec0 but only in that dimensions
+    # that were supported by the initial psf. Broadcasting of psf with less 
+    # dimensions is still supported
     # we put the small psf into the new one
     # it is important to pad the PSF instead of the OTF
-    psf_n = zeros(eltype(rec0), size(rec0))
+    
+    psf_new_size = Array{Int}(undef, 0)
+    for i = 1:ndims(psf)
+        push!(psf_new_size, size(rec0)[i])
+    end
+    
+    psf_new_size = tuple(psf_new_size...)
+    psf_n = zeros(eltype(rec0), psf_new_size)
     psf_n = center_set!(psf_n, fftshift(psf))
     psf = ifftshift(psf_n)
 

### 2020-11-03 test/main.jl
Test also with trailing singleton dimensions

@@ -37,5 +37,14 @@
     res = deconvolution(img, psf, regularizer=GR(num_dims=3, sum_dims=[1,2]))[1]
     @test all(res[:, :, 1] .≈ res[:, :, 2]) 
 
+    img = zeros((3, 3, 2, 1))
+    imgc = randn((3, 3, 1, 1))
+    img[:, :, 1, 1] = imgc
+    img[:, :, 2, 1] = imgc
+    psf = zeros((3, 3))
+    psf[1,1] = 1
+   
+    res = deconvolution(img, psf, regularizer=GR(num_dims=4, sum_dims=[1,2]))[1]
+    @test all(res[:, :, 1, :] .≈ res[:, :, 2, :]) 
 
 end

### 2020-11-03 dev/search_index.js
build based on 7f15747

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/regularizer/#Regularizers","page":"Regularizers","title":"Regularizers","text":"","category":"section"},{"location":"function_references/regularizer/","page":"Regularizers","title":"Regularizers","text":"TV\nTikhonov\nGR","category":"page"},{"location":"function_references/regularizer/#DeconvOptim.TV","page":"Regularizers","title":"DeconvOptim.TV","text":"TV(; <keyword arguments>)\n\nThis function returns a function to calculate the Total Variation regularizer of a n-dimensional array. \n\nArguments\n\nnum_dim=2: \nsum_dims=[1, 2]: A array containing the dimensions we want to sum over\nweights=[1, 1]: A array containing weights to weight the contribution of    different dimensions\nstep=1: A integer indicating the step width for the array indexing\nmode=\"central\": Either \"central\" or \"forward\" accounting for different   modes of the spatial gradient. Default is \"central\".\n\nExamples\n\nTo create a regularizer for a 3D dataset where the third dimension has different contribution. For the derivative we use forward mode.\n\njulia> reg = TV(num_dim=2, sum_dims=[1, 2], weights=[1, 1], mode=\"forward\")\n... (generic function with 1 method)\n\njulia> reg([1 2 3; 4 5 6; 7 8 9])\n12.649111f0\n\n\n\n\n\n","category":"function"},{"location":"function_references/regularizer/#DeconvOptim.Tikhonov","page":"Regularizers","title":"DeconvOptim.Tikhonov","text":"Tikhonov(; <keyword arguments>)\n\nThis function returns a function to calculate the Tikhonov regularizer of a n-dimensional array. \n\nArguments\n\nnum_dim=2: \nsum_dims=[1, 2]: A array containing the dimensions we want to sum over\nweights=[1, 1]: A array containing weights to weight the contribution of    different dimensions\nstep=1: A integer indicating the step width for the array indexing\nmode=\"laplace\": Either \"laplace\", \"spatial_grad_square\", \"identity\" accounting for different   modes of the Tikhonov regularizer. Default is \"laplace\".\n\nExamples\n\nTo create a regularizer for a 3D dataset wh
[…]

### 2020-11-05 docs/make.jl
Add 3D example to documentation

@@ -13,6 +13,7 @@ makedocs(cite_bib, modules=[DeconvOptim],
                         "workflow/basic_workflow.md",
                         "workflow/changing_regularizers.md",
                         "workflow/changing_loss.md",
+                        "workflow/3D_dataset.md",
                     ],
                 "Background" => Any[
                     "background/physical_background.md",

### 2020-11-05 src/regularizer.jl
Change default behaviour of weights

@@ -126,8 +126,8 @@ of a n-dimensional array.
 # Arguments
 - `num_dims=2`: 
 - `sum_dims=[1, 2]`: A array containing the dimensions we want to sum over
-- `weights=[1, 1]`: A array containing weights to weight the contribution of 
-    different dimensions
+- `weights=nothing`: A array containing weights to weight the contribution of 
+    different dimensions. If `weights=nothing` all dimensions are weighted equally.
 - `step=1`: A integer indicating the step width for the array indexing
 - `mode="laplace"`: Either `"laplace"`, `"spatial_grad_square"`, `"identity"` accounting for different
     modes of the Tikhonov regularizer. Default is `"laplace"`.
@@ -135,14 +135,16 @@ of a n-dimensional array.
 To create a regularizer for a 3D dataset where the third dimension
 has different contribution.
 ```julia-repl
-julia> reg = Tikhonov(num_dims=2, sum_dims=[1, 2], weights=[1, 1], mode="identity")
-#97 (generic function with 1 method)
+julia> reg = Tikhonov(num_dims=2, sum_dims=[1, 2], weights=[1, 1], mode="identity");
 
 julia> reg([1 2 3; 4 5 6; 7 8 9])
 285
 ```
 """
 function Tikhonov(;num_dims=2, sum_dims=[1, 2], weights=[1, 1], step=1, mode="laplace")
+    if weights == nothing
+        weights = ones(num_dims)
+    end
     if mode == "laplace"
         Γ = @eval arr -> ($(generate_laplace(num_dims, sum_dims, weights)...))
     elseif mode == "spatial_grad_square"
@@ -193,8 +195,8 @@ of a n-dimensional array.
 # Arguments
 - `num_dims=2`: Dimension of the array that should be regularized 
 - `sum_dims=[1, 2]`: A array containing the dimensions we want to sum over
-- `weights=[1, 1]`: A array containing weights to weight the contribution of 
-    different dimensions
+- `weights=nothing`: A array containing weights to weight the contribution of 
+    different dimensions. If `weights=nothing` all dimensions are weighted equally.
 - `step=1`: A integer indicating the step width for the array indexing
 - `mode="forward"`: Either `"central"` or `"forward"` accounting for different
     modes of the spatial gradient. Default is "central".
@@ -202,8 +204,7 @@ of a n-dimensional array.
[…]

### 2020-11-05 src/DeconvOptim.jl
Minor changes in main code

@@ -45,7 +45,9 @@ using Zygote: @adjoint, gradient
 
 """
     deconvolution(measured, psf; <keyword arguments>)
-Computes the deconvolution of `measured` and `psf`.
+Computes the deconvolution of `measured` and `psf`. Return parameter is a tuple with
+two elements. The first entry is the deconvolved image. The second return parameter 
+is the output of the optimization of Optim.jl
 
 Multiple keyword arguments can be specified for different loss functions,
 regularizers and mappings.
@@ -60,14 +62,33 @@ regularizers and mappings.
               parabola which achieves a non-negativity constraint.
 - `iterations=20`: Specifies a number of iterations after the optimization.
     definitely should stop.
-- `plan_fft=true`: Boolean whether plan_fft is used
+- `plan_fft=true`: Boolean whether plan_fft is used. Gives a slight speed improvement.
 - `padding=0`: an float indicating the amount (fraction of the size in that dimension) 
         of padded regions around the reconstruction. Prevents wrap around effects of the FFT.
         A array with `size(arr)=(400, 400)` with `padding=0.05` would result in reconstruction size of 
         `(440, 440)`. However, we only return the reconstruction cropped to the original size.
         `padding=0` disables any padding.
 - `optim_options=nothing`: Can be a options file required by Optim.jl. Will overwrite iterations.
-- `optim_optimizer=LBFGS()`: The choosen Optim.jl optimizer. 
+- `optim_optimizer=LBFGS()`: The chosen Optim.jl optimizer. 
+
+
+# Example
+```julia-repl
+julia> using DeconvOptim, TestImages, Images, FFTW, Noise, ImageView;
+
+julia> img = 300 .* channelview(testimage("resolution_test_512"));
+
+julia> psf = generate_psf(size(img), 30);
+
+julia> img_b = conv_psf(img, psf);
+
+julia> img_n = poisson(img_b, 300);
+
+julia> @time res, o = deconvolution(img_n, psf);
+
+julia> colorview(Gray, [img img_n res]) |> imshow
+[...]
+```
 """
 function deconvolution(measured::AbstractArray{T, N}, psf;
         loss=Poisson(),

### 2020-11-05 docs/make.jl
Add function references

@@ -22,6 +22,9 @@ makedocs(cite_bib, modules=[DeconvOptim],
                     "background/regularizer.md",
                     ],
                 "Function references" => Any[
+                    "function_references/deconvolution.md",
+                    "function_references/loss.md",
+                    "function_references/mapping.md",
                     "function_references/regularizer.md",
                     "function_references/utils.md",
                     ],

### 2020-11-05 dev/search_index.js
build based on 4a99ab7

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/regularizer/#Regularizers","page":"Regularizers","title":"Regularizers","text":"","category":"section"},{"location":"function_references/regularizer/","page":"Regularizers","title":"Regularizers","text":"TV\nTikhonov\nGR","category":"page"},{"location":"function_references/regularizer/#DeconvOptim.TV","page":"Regularizers","title":"DeconvOptim.TV","text":"TV(; <keyword arguments>)\n\nThis function returns a function to calculate the Total Variation regularizer of a n-dimensional array. \n\nArguments\n\nnum_dims=2: \nsum_dims=[1, 2]: A array containing the dimensions we want to sum over\nweights=[1, 1]: A array containing weights to weight the contribution of    different dimensions\nstep=1: A integer indicating the step width for the array indexing\nmode=\"central\": Either \"central\" or \"forward\" accounting for different   modes of the spatial gradient. Default is \"central\".\n\nExamples\n\nTo create a regularizer for a 3D dataset where the third dimension has different contribution. For the derivative we use forward mode.\n\njulia> reg = TV(num_dims=2, sum_dims=[1, 2], weights=[1, 1], mode=\"forward\")\n... (generic function with 1 method)\n\njulia> reg([1 2 3; 4 5 6; 7 8 9])\n12.649111f0\n\n\n\n\n\n","category":"function"},{"location":"function_references/regularizer/#DeconvOptim.Tikhonov","page":"Regularizers","title":"DeconvOptim.Tikhonov","text":"Tikhonov(; <keyword arguments>)\n\nThis function returns a function to calculate the Tikhonov regularizer of a n-dimensional array. \n\nArguments\n\nnum_dims=2: \nsum_dims=[1, 2]: A array containing the dimensions we want to sum over\nweights=[1, 1]: A array containing weights to weight the contribution of    different dimensions\nstep=1: A integer indicating the step width for the array indexing\nmode=\"laplace\": Either \"laplace\", \"spatial_grad_square\", \"identity\" accounting for different   modes of the Tikhonov regularizer. Default is \"laplace\".\n\nExamples\n\nTo create a regularizer for a 3D dataset wher
[…]

### 2020-11-05 docs/generate_images.jl
Fix generate script for demonstration purpose

@@ -1,44 +1,6 @@
 using DeconvOptim, TestImages, Images, FFTW, Noise, ImageView
 using Plots
 
-function generate_overview()
-    
-    img = channelview(testimage("resolution_test_512"))
-    img ./= maximum(img)
-    
-    dist = [sqrt((-1 + i - size(img)[1] / 2)^2 + (-1 + j - size(img)[2] / 2)^2)
-                for i = 1:size(img)[1],  j = 1:size(img)[2]]
-    psf = ifftshift(exp.(-dist .^2 ./ 4.0 .^2))
-    psf ./= sum(psf)
-    
-    img_b = conv_psf(img, psf, [1, 2])
-    img_n = poisson(img_b .* 300, 300)
-    
-   
-    reg = DeconvOptim.GR()
-    
-    @time res, o = deconvolution(img_n, psf, iterations=10,
-                                 λ=0.001, lossf=Poisson(), regularizerf=reg)
-    @show o
-    # simple example of deconvolution
-    save("src/assets/img.png", clamp01!(img))
-    save("src/assets/img_noisy_index.png", clamp01!(img_n ./ 300))
-    save("src/assets/img_rec_index.png", clamp01!(res ./ 300))
-    
-    
-    
-    
-    img_ft = abs.(fft(img))
-    img_ft ./= maximum(img_ft)
-    
-    img_n_ft = abs.(fft(img_n))
-    img_n_ft ./= maximum(img_n_ft)
-    
-    res_ft = real(fft(res))
-    res_ft ./= maximum(res_ft)
-    return
-end
-
 function norm_fft(x)
     x = fftshift(abs.(fft(x)))
     n = div(size(x)[1], 2)
@@ -66,9 +28,9 @@ function ideal_freq()
     img_b = conv_psf(img, psf, [1, 2])
     img_n = poisson(img_b, N_phot)
     
-    reg = DeconvOptim.TV(num_dim=2, sum_dims=[1, 2])
-    @time res, o = deconvolution(img_n, psf, iterations=60, λ=0.001f0,
-            lossf=Poisson(), regularizerf=reg, padding=0.00, plan_fft=true)
+    reg = DeconvOptim.TV(num_dims=2, sum_dims=[1, 2])
+    @time res, o = deconvolution(img_n, psf, iterations=10, λ=0.001f0,
+            loss=Poisson(), regularizer=reg, padding=0.00, plan_fft=true)
[…]

### 2020-11-05 v0.1.1/search_index.js
build based on 1725e34

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas)\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas)\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_gauss_aux","page":"Loss Functions","title":"DeconvOptim.scaled_gauss_aux","t
[…]

### 2021-06-28 src/lossfunctions.jl
Update loss

@@ -4,7 +4,7 @@ export ScaledGauss, scaled_gauss_aux
 
 
 """
-    poisson_aux(μ, meas)
+    poisson_aux(μ, meas, storage=copy(μ))
 
 Calculates the Poisson loss for `μ` and `meas`.
 `μ` can be of larger size than `meas`. In that case
@@ -13,7 +13,7 @@ we extract a centered region from `μ` of the same size as `meas`.
 function poisson_aux(μ, meas, storage=copy(μ))
     # due to numerical errors, μ can be negative or 0
     if minimum(μ) <= 0
-        μ .+= eps(maximum(μ)) .+ abs.(minimum(μ))
+        μ .= μ .+ eps(maximum(μ)) .+ abs.(minimum(μ))
     end
     storage .= μ .- meas .* log.(μ)
     return sum(storage)
@@ -48,7 +48,7 @@ end
 
 
 """
-    gauss_aux(μ, meas)
+    gauss_aux(μ, meas, storage=copy(μ))
 
 Calculates the Gauss loss for `μ` and `meas`.
 `μ` can be of larger size than `meas`. In that case

### 2021-06-28 src/generic_invert.jl
Deepcopy instead of copy

@@ -44,7 +44,7 @@ function invert(measured, rec0, forward;
     mf, m_invf = get_mapping(mapping)
     regularizer = get_regularizer(regularizer, eltype(rec0))
     
-    storage_μ = copy(measured)
+    storage_μ = deepcopy(measured)
     function total_loss(rec)
         # handle if there is a provided mapping function
         mf_rec = mf(rec) 

### 2021-06-28 examples/juliacon_2021.jl
Update exampes

@@ -45,17 +45,37 @@ end
 begin
 	x = range(-1.5, 1.5, length=size(img, 1))
 	freqs = fftshift(fftfreq(size(img_1D, 1), 1))
-	psf = DeconvOptim.generate_psf(size(img), 30)
+	psf = Float32.(DeconvOptim.generate_psf(size(img), 20))
 	psf_1D = psf[1, :]
 	psf_1D ./= sum(psf_1D)
 	otf_1D = abs.(ffts(psf_1D))
 end;
 
 # ╔═╡ 24fc86da-0b7c-493c-8977-2a19ef6dc133
-img_n = poisson(DeconvOptim.conv(img, psf), 1000);
+img_n = Float32.(poisson(DeconvOptim.conv(img, psf), 1000));
 
 # ╔═╡ 3bda922d-552b-42ec-9055-33a141b5841a
 blur(x, otf=otf_1D) = iffts(ffts(x) .* otf)
+
+# ╔═╡ 308e2562-5a20-4082-8a6d-9fb135738c49
+md"
+Mathematically:
+
+$(S * \text{PSF})(\mathbf r) = \int_{-\infty}^{\infty} S(\mathbf r - \mathbf x) \cdot \text{PSF}(\mathbf x) \, \mathrm d \mathbf x$
+"
+
+# ╔═╡ b542187a-3ae7-4430-a81d-f968d9000427
+img_blurry = DeconvOptim.conv(img, psf);
+
+# ╔═╡ 88d83629-f1b2-4d69-928f-d4acfbc76b70
+reg_1D = TV(num_dims=1);
+
+# ╔═╡ d6d0f436-48fd-4e8a-863c-3e9d3850cc91
+begin
+	reg_tik = Tikhonov()
+	reg_TV = TV()
+	reg_GR = DeconvOptim.GR()
+end
 
 # ╔═╡ 061faf49-662c-4508-83b4-ddcf0970ed0d
 md"### DeconvOptim.jl: Microscopy Image Deconvolution
@@ -66,7 +86,7 @@ load("../docs/src/assets/logo.png")
 
 # ╔═╡ 30f21bb8-6d09-4fce-9d2a-568bfaf3ff7a
 md"
-* **Felix Wechsler:** Master Student at the IPHT Jena, Germany
+* **Felix Wechsler:** Master Student at the Leibniz Institute of Photonic Technology in  Jena, Germany
[…]

### 2021-06-28 dev/search_index.js
build based on 75635a6

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas)\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas)\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_gauss_aux","page":"Loss Functions","title":"DeconvOptim.
[…]

### 2021-06-29 src/utils.jl
Add rounding to next fast FFT size in padding

@@ -333,3 +333,19 @@ end
 function get_regularizer(reg::Nothing, etype)
     x -> zero(etype)
 end
+
+
+"""
+    next_fast_fft_size(x)
+
+`x` is a tuple of sizes.
+It rounds to the next fast FFT size.
+FFT is especially fast on small prime factors.
+"""
+function next_fast_fft_size(x)
+    nextprod([2, 3, 5, 7], x)
+end
+
+function next_fast_fft_size(x::Tuple)
+    next_fast_fft_size.(x)
+end

### 2021-06-29 test/utils.jl

@@ -99,5 +99,8 @@ end
 end
 
 
-
+@testset "next fast fft size" begin
+    @test DeconvOptim.next_fast_fft_size(23) == 24
+    @test DeconvOptim.next_fast_fft_size((23, 46)) == (24, 48)
+end
 

### 2021-06-29 src/deconvolution.jl
Change boundary handling

@@ -79,7 +79,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
             if ~iszero(padding)
                 # 2 * ensures symmetric padding
                 # minimum padding is 2 (4 in total) on each side
-                x = max(4, 2 * round(Int, size(measured)[i] * padding))
+                x = next_fast_fft_size(max(4, 2 * round(Int, size(measured)[i] * padding)))
             else
                 x = 0
             end
@@ -94,7 +94,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
     measured = measured ./ rescaling
     # create rec0 which will be the initial guess for the reconstruction
     rec0 = similar(measured, (size_padded)...)
-    fill!(rec0, zero(eltype(measured))) 
+    fill!(rec0, one(eltype(measured))) 
     
     # alternative rec0_center, unused at the moment
     #rec0_center = m_invf(abs.(conv_psf(measured, psf, conv_dims)))
@@ -104,9 +104,8 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
     # measured
     one_arr = similar(measured, size(measured))
     fill!(one_arr, one(eltype(measured)))
-    rec0_center = mean(measured) .* one_arr
-    center_set!(rec0, rec0_center)
-
+    center_set!(rec0, one_arr)
+    rec0 .*= mean(measured)
     mf, mf_inv = get_mapping(mapping)
     rec0 = mf_inv(rec0)
     # psf_n is the psf with the same size as rec0 but only in that dimensions
@@ -120,6 +119,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
         push!(psf_new_size, size(rec0)[i])
     end
     
+
     psf_new_size = tuple(psf_new_size...)
     psf_n = similar(rec0, psf_new_size)
     fill!(psf_n, zero(eltype(rec0)))

### 2021-06-29 examples/paper_figures/conv_speed_comparison.jl
Rename folder

@@ -1,68 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.14.8
-
-using Markdown
-using InteractiveUtils
-
-# ╔═╡ 1d248a02-cdb3-11eb-25c2-552ed8a37503
-begin
-	import Pkg
-    Pkg.activate(".")
-end
-
-# ╔═╡ 44be0bb5-155b-4311-aa9a-b0ad93ee5010
-using Tullio, PGFPlotsX, OffsetArrays, FourierTools
-
-# ╔═╡ 4c3c0f8a-9678-4584-9f6d-a2945a5250bb
-begin
-	conv_2(x,k) = @tullio y[i+_, j+_] := x[i+a, j+b] * k[a,b]
-	conv_3(x,k) = @tullio y[i+_, j+_, l+_] := x[i+a, j+b, l+c] * k[a,b,c]
-end
-
-# ╔═╡ af2d1ca4-3835-4108-bd4c-9b080ce07c81
-function extend_kernel(kernel, s)
-	return collect(FourierTools.select_region(kernel, new_size=s))
-end	
-
-# ╔═╡ f54b482c-88d7-4e6f-8dd6-bdb01c17d15a
-function compare_speed(N, K)
-	img_2 = randn((N, N))
-	kernel_2 = ones((K, K))
-	kernel_full_2 = extend_kernel(kernel_2, (N, N))
-	
-	img_3 = randn((N, N, N))
-	kernel_3 = ones((K, K, K))
-	kernel_full_3 = extend_kernel(kernel_3, (N, N, N))
-	
-	v_ft, pconv = plan_conv(img_2, kernel_full_2) 
-	@time res_conv = conv_2(img_2, kernel_2)
-	@time res_fft = pconv(img_2)
-	
-	_, pconv3 = plan_conv(img_3, kernel_full_3) 
-	@time res_conv = conv_3(img_3, kernel_3)
-	@time res_fft = pconv3(img_3)
-	
-	end
-
-# ╔═╡ d79ccda2-9905-46a4-8b91-d074e6fdb7d1
-compare_speed(80, 5);
-
-# ╔═╡ b6f7210e-6d8b-4919-af08-74239190afaf
-
-
-# ╔═╡ ce20536f-5af4-42c8-b7d5-e89a4a473c67
-
-
[…]

### 2021-06-29 examples/paper_figures/convolution_padding.jl

@@ -1,57 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.14.8
-
-using Markdown
-using InteractiveUtils
-
-# ╔═╡ 0552a944-cdbe-11eb-2e63-49f12bee1624
-using FourierTools, TestImages, Colors, ImageShow, ImageCore, Statistics
-
-# ╔═╡ 9a73fe7d-d298-4791-8f29-5a962d1242d1
-gauss(y, x, σ=1) = 1 / σ / √(2π) * exp(-0.5 * (x^2 + y^2) / σ^2)
-
-# ╔═╡ b8b2b314-4fed-420e-9061-6c2716c134c8
-begin
-	y = fftpos(512, 512)
-	x = y'
-end;
-
-# ╔═╡ 97dc4b9d-0b32-4057-8a22-85cb40ae1ebf
-begin
-	kernel = ifftshift_view(gauss.(y, x, Ref(3)))
-	kernel ./= sum(kernel)
-end;
-
-# ╔═╡ 7500e8d2-16a7-4ea3-9192-78b4acfa327e
-function conv_pad(A, B, value=zero(eltype(A)), pad=10)
-	A_1 = value .+ FourierTools.select_region(A .- value, new_size=size(A) .+ pad)
-	B_1 = ifftshift_view(FourierTools.select_region(fftshift_view(B), new_size=size(A) .+ pad))
-	return FourierTools.select_region(conv(A_1, B_1), new_size=size(A))
-end
-
-# ╔═╡ 44370313-62d3-4774-aed6-72a51410503d
-img = Float64.(Gray.(testimage("house")));
-
-# ╔═╡ d190772c-885f-405b-b0c9-bd11b6ac992c
-img_blurry = Gray.(conv(kernel, img))
-
-# ╔═╡ 0e57683e-7af8-4940-8494-032d6190f2cf
-img_blurry[end-100:end-51, 1:50]
-
-# ╔═╡ b8a8adfb-af4a-4ff9-b739-a040f05e2896
-img_blurry2 = Gray.(conv_pad(img, kernel, 0.7, 10))
-
-# ╔═╡ 94816b91-0ff3-41ef-9146-b71f150be161
-img_blurry2[end-100:end-51, 1:50]
-
-# ╔═╡ Cell order:
-# ╠═0552a944-cdbe-11eb-2e63-49f12bee1624
[…]

### 2021-06-29 examples/paper_figures/regularizer_speed.jl

@@ -1,253 +1,0 @@
-{
- "cells": [
-  {
-   "cell_type": "code",
-   "execution_count": 1,
-   "metadata": {},
-   "outputs": [],
-   "source": [
-    "using Pkg, Revise\n",
-    "Pkg.activate(\"paper_figures/.\")"
-   ]
-  },
-  {
-   "cell_type": "code",
-   "execution_count": 254,
-   "metadata": {},
-   "outputs": [],
-   "source": [
-    "using Tullio, BenchmarkTools, CUDA, CUDAKernels, KernelAbstractions, Zygote, Distributed\n",
-    "CUDA.allowscalar(false)"
-   ]
-  },
-  {
-   "cell_type": "code",
-   "execution_count": 367,
-   "metadata": {
-    "scrolled": true
-   },
-   "outputs": [
-    {
-     "data": {
-      "text/plain": [
-       "TV_tullio_2 (generic function with 2 methods)"
-      ]
-     },
-     "execution_count": 367,
-     "metadata": {},
-     "output_type": "execute_result"
-    }
-   ],
-   "source": [
-    "function TV_cpu(arr, ϵ=eltype(arr)(1e-8))\n",
-    "    @tullio r = sqrt(ϵ + abs2(arr[i,j,k] - arr[i+1,j,k])\n",
-    "                       + abs2(arr[i,j,k] - arr[i,j+1,k])\n",
-    "                       + abs2(arr[i,j,k] - arr[i,j,k+1]))\n",
-    "end\n",
-    "\n",
-    "# see here https://github.com/mcabbott/Tullio.jl/issues/85\n",
-    "# gradient pass is super slow\n",
-    "function TV_gpu(arr, ϵ=eltype(arr)(1e-8))\n",
-    "    arr1 = arr\n",
-    "    arr2 = arr\n",
-    "    arr3 = arr\n",
-    "    @tullio r[i, j, k] := sqrt(ϵ + abs2(arr[i,j,k] - arr1[i+1,j,k])\n",
-    "                       + abs2(arr[i,j,k] - arr2[i,j+1,k])\n",
-    "                       + abs2(arr[i,j,k] - arr3[i,j,k+1]))\n",
-    "    return sum(r)\n",
-    "end\n",
-    "\n",
-    "\n",
-    "f_inds(rs, b) = ntuple(i -> i == b ? rs[i] .+ 1 : rs[i], length(rs))\n",
[…]

### 2021-06-29 examples/paper/convolution_padding.jl
Add more examples

@@ -1,0 +1,57 @@
+### A Pluto.jl notebook ###
+# v0.14.8
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ 0552a944-cdbe-11eb-2e63-49f12bee1624
+using FourierTools, TestImages, Colors, ImageShow, ImageCore, Statistics
+
+# ╔═╡ 9a73fe7d-d298-4791-8f29-5a962d1242d1
+gauss(y, x, σ=1) = 1 / σ / √(2π) * exp(-0.5 * (x^2 + y^2) / σ^2)
+
+# ╔═╡ b8b2b314-4fed-420e-9061-6c2716c134c8
+begin
+	y = fftpos(512, 512)
+	x = y'
+end;
+
+# ╔═╡ 97dc4b9d-0b32-4057-8a22-85cb40ae1ebf
+begin
+	kernel = ifftshift_view(gauss.(y, x, Ref(3)))
+	kernel ./= sum(kernel)
+end;
+
+# ╔═╡ 7500e8d2-16a7-4ea3-9192-78b4acfa327e
+function conv_pad(A, B, value=zero(eltype(A)), pad=10)
+	A_1 = value .+ FourierTools.select_region(A .- value, new_size=size(A) .+ pad)
+	B_1 = ifftshift_view(FourierTools.select_region(fftshift_view(B), new_size=size(A) .+ pad))
+	return FourierTools.select_region(conv(A_1, B_1), new_size=size(A))
+end
+
+# ╔═╡ 44370313-62d3-4774-aed6-72a51410503d
+img = Float64.(Gray.(testimage("house")));
+
+# ╔═╡ d190772c-885f-405b-b0c9-bd11b6ac992c
+img_blurry = Gray.(conv(kernel, img))
+
+# ╔═╡ 0e57683e-7af8-4940-8494-032d6190f2cf
+img_blurry[end-100:end-51, 1:50]
+
+# ╔═╡ b8a8adfb-af4a-4ff9-b739-a040f05e2896
+img_blurry2 = Gray.(conv_pad(img, kernel, 0.7, 10))
+
+# ╔═╡ 94816b91-0ff3-41ef-9146-b71f150be161
+img_blurry2[end-100:end-51, 1:50]
+
+# ╔═╡ Cell order:
+# ╠═0552a944-cdbe-11eb-2e63-49f12bee1624
[…]

### 2021-06-29 test/main.jl
Update test code

@@ -22,12 +22,12 @@
     psf = [0.37240087577993225 0.562668812321259 0.6810849274435286; 0.36901028455183293 0.10686911035365092 1.3391251213773154; 0.007612980079313577 0.5694584949295476 0.23828371819888622]
 
     #@show deconvolution(img, psf, regularizer=nothing, padding=0.1)[1]
-    res3 = [1.0406577489364471e-7 91.81363444807677 2.272608189988653e-7; 1.2703220368343009e-7 89.01393312854161 5.487620214472806e-8; 3.5819990308679853e-9 18.814647865228448 89.76902076477796] 
+    res3 = [3.700346192004195 16.163004402781457 0.0005317269571170434; 0.3852386808335988 14.378882057906575 0.04691706650167405; 1.5059695704739982 16.94303953714345 22.72731111751148] 
     @test all(≈(res3, deconvolution(img, psf, regularizer=nothing, padding=0.1)[1], rtol=1e-2))
 
 
     # test without mapping
-    res4 = [-5.332320754919289 40.63633433786456 -18.173096688407522; -15.597390722842547 59.01033285248438 -4.122592175577954; 13.402949467681973 6.4622595721116465 42.82143693411391] 
+    res4 = [-13.085096066984729 34.39174935297922 -11.353417020874208; -13.01079706662783 43.76596781851713 -7.565144283495296; 16.740081837985805 -7.488374542587605 37.666978022259336] 
     #= @show deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1] =# 
     @test all(≈(res4, deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1], rtol=0.1))
 

### 2021-06-29 paper/header.tex
Add files for paper

% **************GENERATED FILE, DO NOT EDIT**************

\title{DeconvOptim.jl - Image Deconvolution with Julia}

\author[1, 2]{Felix Wechsler}
\author[1, 2, 3]{Rainer Heintzmann}
\affil[1]{Faculty of Physics and Astronomy, Friedrich-Schiller-University,Jena, Germany}
\affil[2]{Leibniz Institute of Photonic Technology, Albert-Einstein-Straße 9,07745 Jena, Germany}
\affil[3]{Institute of Physical Chemistry and Abbe Center of Photonics, Friedrich-Schiller-University, Helmholtzweg 4, Jena, Germany}

\keywords{Julia, Image Processing, Deconvolution, Microscopy}

\hypersetup{
pdftitle = {DeconvOptim.jl - Image Deconvolution with Julia},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Felix Wechsler, Rainer Heintzmann},
pdfkeywords = {Julia, Image Processing, Deconvolution, Microscopy},
}

### 2021-06-29 paper/paper.tex
Add files for paper

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{siunitx}
\newcommand\todo[1]{\textcolor{red}{\textbf{TODO: #1}}}
\begin{document}

\input{header}

\maketitle

\begin{abstract}

Deconvolution is a versatile method to enhance the quality of signals measured with systems which can 
be mathematically expressed as a convolution of a system's response function with a signal. 
In this paper, we present \verb|DeconvOptim.jl|, a flexible toolbox written in Julia to deconvolve multi-dimensional signals which have been
degraded by a multi-dimensional signal response function. 
\verb|DeconvOptim.jl| works both on CPUs and GPUs and utilizes recent advancements in Julias Automatic Differentiation ecosystem. The performance on CPUs surpasses the one of existing open source libraries. 
The library is applicable to one dimensional time series datasets but also to multi-dimensional microscopy imaging datasets.
\end{abstract}

\todo{consistent notation with vector and indices}
\todo{fix code formatting}

\section{Introduction}
Deconvolution has been a long addressed problem especially in astronomical imaging, digital signal processing or microscopy imaging.
The assumption is that images are degraded by some kind of blur which can be described as a convolution between a kernel $h$ and the image $S$:
\begin{equation}
    I(\mathbf r) = (h * S)(\mathbf r)
\end{equation}
$h$ is often called the point spread function (PSF) since it characterizes how the systems maps a point in the object to a blurred area
in the image.
Often this convolution operation is disturbed by different types of noise where the most common are additive Gaussian noise due to the read out of the camera sensors or Poisson shot noise due to the quantum nature of photons:
\begin{align}
    Y_{\text{Poisson}}(\mathbf r) &= \text{Poisson}[(h * S)(\mathbf r)]\\
    Y_{\text{Gauss}}(\mathbf r) &= (h * S)(\mathbf r) + \text{Gauss}_{\mu, \sigma}(\mathbf r)
\end{align}
Due to the noise, deconvolution is an ill-posed problem which cannot be solved directly.\\
A well known approach, because of its simplicity, has been the iterative Richardson-Lucy deconvolution algorithm \cite{Richardson:72}, \cite{lucy:74} for Poisson noise degraded signals.
Another common method is the non-iterative Wiener filter \cite{wiener2013extrapolation} because of its predictable runtime.
Wiener filter assumes additive noise which is often not suitable, especially in low light conditions as in microscopy or astronomy. 
Recently machine learning based methods have become more and more favoured in deconvolution methods because
of the possibility to add learned properties of similar images to the algorithm \cite{Kruse_2017_ICCV}.
However, those implementations are usually restricted to cases where many experimental datasets are available for the characterization.

\section{Convolution}
To obtain fast deconvolution algorithms we also need a fast way to calculate the convolution operations.
In these times, convolution operations of spatially small kernels $h$ can be calculated on GPUs very efficiently.
However, often the blurring kernel $h$ is not spatially small and might be also multi dimensional. In that case, FFT based convolutions
outperform sliding kernels. In microscopy and astronomy that is often the case, since a defocus broadens the PSF.

\subsection{FFT Based Convolution}
    The basis for fast convolution operations lies in the convolution theorem. It states that
    \begin{equation}
        \mathcal F\left\{(h * g)\right\}(\mathbf k) = \mathcal F\{h\} (\mathbf k) \cdot \mathcal F\{g\} (\mathbf k),
        \label{eq:fftconv}
    \end{equation} 
        which means that a Fourier transform of a  convolution operation is equivalent to a point wise multiplication of the Fourier transforms 
        of $h$ and $g$.
        Fortunately, the Fourier transform operations can be calculated even for moderate large 3D arrays quickly on modern computing machines via
        the Fast Fourier Transform (FFT).
        In Julia, \verb|FFTW.jl| offers a convenient interface to the fast FFTW library \cite{FFTW05}.
        The time complexity to calculate \autoref{eq:fftconv} is $\mathcal{O}(N \cdot \log N)$ for a one dimensional discretized dataset with $N$ samples.
        For a 2D dataset with size $N \times M$ it is $\mathcal{O}(N \cdot M \log(N + M))$ and similar for higher dimensions.

\subsection{Sliding Convolution Windows}
Convolutions can be also calculated with a sliding windows as show in \todo{figure}. 
That mechanism is the working principle
behind the convolutions in neural nets. The reason is that this operation can be parallelized easily and therefore 
is suitable on GPUs. However, the computational complexity for a 2D kernel with size $K \times L$ applied on an image with
$N \times M$ data points is $\mathcal O(N \cdot M \cdot K \cdot L)$. It is clear that for larger kernel sizes the sliding method 
has worse computational complexity than the FFT based convolutions. The many cores of a GPU can mitigate that to a certain extent
but since the FFT based method can be also executed in parallel fashion, both approaches profit from parallelization.

\subsection{Wrap-Around Artifacts in FFT based Convolutions}
    One drawback of the FFT based convolution are wrap-around artifacts. The reason is, that the FFT operation calculates the discrete
    Fourier transform (DFT) which inherently assumes periodic data. If one applies a FFT on a finite data set the assumption is that
    this finite data set repeats itself. 
    To weaken the wrap-around artifacts in the convolution one can zero or mean pad the image before convolution and remove the boundaries afterwards.

    \begin{figure}[h]
        \centering
        \begin{subfigure}[b]{.25\textwidth}
            \centering
            \begin{tikzpicture}
                \node at (0,0) {\includegraphics[width=.9\textwidth]{figures/full_house_no_pad.png}};
                \draw[red] (-2.0, -1.6) rectangle (-1.6, -1.2);
                \node[color=red] at (0,0) {\includegraphics[width=.4\textwidth]{figures/edge_house_no_pad.png}};
                \draw[color=red] (-0.91, -0.9) rectangle (0.9, 0.9); 
                \draw[color=red] (-2.0, -1.2) -- (-0.9, 0.9);
                \draw[color=red] (-1.6, -1.6) -- (0.9, -0.9);
            \end{tikzpicture}
            \caption{Without padding}
            \label{fig:withoutpad}
        \end{subfigure}%
        \begin{subfigure}[b]{.25\textwidth}
            \centering
            \begin{tikzpicture}
                \node at (0,0) {\includegraphics[width=.9\textwidth]{figures/full_house_pad.png}};
                \draw[red] (-2.0, -1.6) rectangle (-1.6, -1.2);
                \node[color=red] at (0,0) {\includegraphics[width=.4\textwidth]{figures/edge_house_pad.png}};
                \draw[color=red] (-0.90, -0.9) rectangle (0.9, 0.9); 
                \draw[color=red] (-2.0, -1.2) -- (-0.9, 0.9);
                \draw[color=red] (-1.6, -1.6) -- (0.9, -0.9);
            \end{tikzpicture}
            \caption{With padding.}
            \label{fig:withpad}
        \end{subfigure}
        \caption{Comparison between two blurred images. The left images is a straightforward FFT based blurred image.
        The zoomed region shows dark artifacts at the left side. Also at the top of the image some dark regions from
        the bottom scattered into the bright sky.
        The right image was padded before blurring with 10 pixels on each side with value 0.7. The blur kernel was a Gaussian kernel
        with standard deviation $\sigma=\SI{3}{pixel}$.}
        \label{fig:}
    \end{figure}

\section{Inverse Modelling}
In \autoref{fig:pipeline} we show our approach to deconvolution.
The general idea is to create a physical forward model describing the measurement process.
At the beginning of the optimization we start with an initial guess $x(\mathbf r)$. 
Via a mapping function we can impose some restrictions to the final solution (e.g. non-negativity, certain value intervals).
The forward model (can be a convolution) is then applied to the mapped reconstruction. This result is compared
with our noisy measurement with a certain loss function.
Since deconvolution is an ill-posed problem we regularize the loss function with a regularizer.
Via automatic differentation (AD) we then calculate the gradient with respect to the reconstruction $x(\mathbf r)$. 
The values of the total loss and the gradient are then used by an optimizer to apply some kind of gradient descent optimization to get a proper reconstruction.\\

As typical for Julia packages, except \verb|FFTW.jl| and \verb|CUDA.jl| \cite{besard2018juliagpu}, all code is written in Julia.
Therefore it is easy to replace the forward model with any Julia code, as long as we can 
automatically differentiate through the code. The gradient step is currently calculated with the reverse mode AD of \verb|Zygote.jl| \cite{Zygote.jl-2018}. 
As default for the optimization we use the L-BFGS \cite{LBFGS} routine provided by \verb|Optim.jl| \cite{mogensen2018optim}.
L-BFGS is suitable for optimization with many million parameters as it only stores a sparse representation of the inverse Hessian matrix
which is built from a finite number of past function and gradient evaluations. 
In comparison to the Richardson-Lucy algorithm often results are converged after 20 to 50 iterations whereas Richardson-Lucy often takes
a few hundreds iterations. However, as we will see later due to the more complex optimization routine the speed-up in using L-BFGS is for simple 
deconvolution often minor.

\begin{figure}[h]
    \centering
    \includegraphics[width = .5\textwidth]{figures/pipeline.pdf}
    \caption{}
    \label{fig:pipeline}
\end{figure}

\subsection{Mapping Function}
    Mapping functions are an easy way to constrain the resulting reconstruction to certain values.
    For example, if the optimizer optimizes the variables $\text{rec}$ which are then squared, we know that
    $\text{rec}^2$ is definitely non-negative. Instead of directly using $\text{rec}$ we compare
    $\text{rec}^2$ with the measurement $Y$. This mapping function does not change the result as long
    as it is an surjective function for the desired number space (e.g. a parabola is non-negative and covers all positive values) 
    and does not change the convexity of a problem.
    Functions like shifted $\tanh$ are possible as well since it is an bijective function in $[-1, 1]$ and monotonic increasing
    in the whole definition space.

\subsection{Wrap-around Artifacts Suppression}

\section{Loss Function}
    Besides the forward model, the loss function is the most critical part in the optimization.
    It has to take account for the noise created by the measurement process or device.

\subsection{Data Term}
    As already mentioned, Poisson shot noise is often the dominant source of noise.
    The key idea is to interpret the measurement as a stochastic process. Our aim is to find a deconvolved image which describes as accurate as possible the measured image.
Mathematically the probability for a certain measurement $Y$ is

\begin{equation}
    p(Y(\mathbf r)|\mu(\mathbf r)) = \prod_r \frac{\mu(\mathbf r)^{Y(\mathbf r)}}{\Gamma(Y(\mathbf r) + 1)} \exp(- \mu(\mathbf r))
\end{equation}

where $Y$ is the measurement, $\mu$ is the expected measurement (ideal measurement without noise) and $\Gamma$ is the generalized factorial function.
In the deconvolution process we get $Y$ as measured input and want to find the ideal specimen $S$ which results in a measurement $\mu(\mathbf r) = (S * \text{PSF})(\mathbf r))$.
Since we want to obtain for the best reconstruction, we want to find a $\mu(\mathbf r)$ so that $p(Y(\mathbf r) | \mu(\mathbf r))$ gets as large as possible. Because that means
that we find the specimen which describes the measurement with the highest probability.
Instead of maximizing $p(Y(\mathbf r) | \mu(\mathbf r))$ a common trick is to minimize $- \log(p(Y(\mathbf r)|\mu(\mathbf r)))$. 
Mathematically, the optimization of both functions provides same results but the latter is numerically more stable.

\begin{align}
&\underset{S(\mathbf r)}{\arg \min} (- \log(p(Y(\mathbf r)|\mu(\mathbf r)))) =\\ &\underset{S(\mathbf r)}{\arg \min} \sum_r (\mu(\mathbf r) + \log(\Gamma(Y(\mathbf r) + 1)) - Y(\mathbf r) \log(\mu(\mathbf r))
\end{align}

which is equivalent to

\begin{equation}
    \underset{S(\mathbf r)}{\arg \min}\, L = \underset{S(\mathbf r)}{\arg \min} \sum_r (\mu(\mathbf r)  - Y(\mathbf r) \log(\mu(\mathbf r))
    \label{eq:poisson_loss}
\end{equation}

since the second term only depends on $Y(\mathbf r)$ but not on $\mu(\mathbf r)$.
The gradient of $L$ with respect to $\mu(\mathbf r)$ is simply

\begin{equation}
    \nabla L = 1 - \frac{Y(\mathbf r)}{\mu(\mathbf r)}
    \label{eq:gradpoisson}
\end{equation}

The function $L$ and the gradient $\nabla L$ are needed for any gradient descent optimization algorithm.
The numerical evaluation of the Poisson loss can lead to issues. Since $\mu(r)=0$ can happen for a measurement with zero intensity background. However, the loss is not defined for $\mu \leq 0$. In our source code we set all intensity values below a certain threshold $\epsilon$ to $\epsilon$ itself. This prevents the evaluation of the logarithm at undefined values.
The final source code has a modified version of \autoref{eq:gradpoisson} as registered gradient for \autoref{eq:poisson_loss}.
The reason is, that for values of $\mu(\mathbf r) \leq 0$ the equation is not defined and has to be handled separately.

\subsection{Regularizer}
    The regularizer is an additional part in the total loss to add some additional priors like sparsity and smoothness.
    Most real samples are smooth over large regions and such regularizers enhance the quality of the reconstruction.
    In our toolbox we currently implement several regularizer like (smoothed) Total variation, Good's roughness \cite{Verveer:98}, \cite{Good:71} and Tikhonov. 
    \subsubsection{Total Variation as example}
        As the name suggests, Total variation tries to penalize variation in the image intensity. Therefore it sums up the gradient strength at each point
        of the image. In 2D this is:
        \begin{equation}
            \text{Reg}(S(\mathbf r)) = \sum_r  |(\nabla S)(\mathbf r)|
        \end{equation}
        Since we look at the magnitude of the gradient strength, this regularizer is anisotropic.
        In 2D this is:
        \begin{equation}
        \begin{split}
            \text{Reg}(S(\mathbf r)) = \sum_{x,y} \big[& |S(x + 1, y) - S(x, y)|^2 \\ 
                                                & + |S(x, y + 1) - S(x, y)|^2\big]^{\frac12}
        \end{split}
        \end{equation}
        In many frameworks such a regularizer is implemented via functions like \lstinline{circshift}. 
        However, such approaches create often several copies of the data. We currently use \verb|Tullio.jl|\footnote{\url{https://github.com/mcabbott/Tullio.jl}} to create efficient functions providing a function to calculate the regularizer and the gradient. For simple expressions
        such as below, \verb|Tullio.jl| registers an analytical gradient and therefore allows to apply the same mechanisms to the gradient calculation which have been used for the regularizer evaluation itself \todo{ask McAbott for reason}.
        A (smoothed) Total variation with \verb|Tullio.jl| is defined here:
        \begin{lstlisting}[language = Julia]
function total_variation(arr, ϵ=eltype(arr)(1e-8))
    @tullio r = sqrt(ϵ + 
                abs2(arr[i,j] - arr[i+1,j]) +
                abs2(arr[i,j] - arr[i,j+1]))
end
        \end{lstlisting}
        \lstinline{ϵ} is needed because for regions where \lstinline{arr == 0} the gradient would result in singularities.
        Note, that definition here just demonstrates how the regularizer can be written down.
        In our toolbox we allow for much for options. \verb|Tullio.jl| cannot handle multi dimensional data yet.
        Via Julia's metaprogramming capability we create regularizers which can vary in step size, dimensionality and
        different weighting in dimensions.
        A call like 
        \begin{lstlisting}[language = Julia]
julia> using DeconvOptim

julia> reg = TV(num_dims=4, sum_dims=[1,2,3],
                weights=[1,1,2])
#169 (generic function with 1 method)

julia> reg(randn((10,20,30,40)))
417810.11332404887
        \end{lstlisting}
        results in a regularizer accepting four dimensional arrays. However, the regularization only happens along the first three dimension
        and the third dimensions is weighted differently.
        Such options are available for most of the regularizers.

\section{Experiments}
    In this section we show some experiments and compare parts of the software to other solutions.
    All experiments were executed on Ubuntu 20.04 using a AMD Ryzen 5 5600X 6-Core processor (12 threads) with \SI{32}{GB} DDR4 RAM and Julia 1.6.1.
    If possible, all threads were used.
    As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.

    \subsection{One-Dimensional Time Series}
        First, we want to demonstrate the deconvolution of an artificial one dimensional dataset blurred with a certain PSF.
        Additionally, we want to demonstrate the mechanism to reduce wrap-around artifacts in the deconvolution.

        \todo{1D dataset}

    \subsection{Influence of Regularizer}

    \subsection{Multi-Dimensional Microscopy Data}
        To show the full power, we deconvolve a four dimensional dataset where the measured volume consists of a 3D datasets
        with three different color channels. The PSF is only three dimensional.
        Julia's broadcast mechanism handles that the PSF is only three dimensional and therefore
        we only need to specify over which dimensions the convolution should happen.

        \todo{4D dataset}

    \subsection{Performance Comparison}
        Since Julia is often advertised with great performance we compare parts and the full deconvolution to other implementations in
        terms of their total performance.

        \subsubsection{Regularizer}
            In \autoref{tab:reg} we can see the runtimes for different TV regularizer implementations. As we can see, \verb|Tullio.jl| outperforms a plain 
            Julia implementation by more than order of magnitude. Partially, that is caused by the reason that \verb|Tullio.jl| can make 
            use of all threads whereas Julia's built in broadcast mechanism is not multi threaded.
            By \textit{plain Julia} we are referring to an implementation which is written with standard Julia Base functions.
            The same plain Julia implementation was then used together with \verb|CUDA.jl|
            to make use of the GPU capabilities. We see that there is a minor benefit in using a GPU for the regularizer instead of 
            the \verb|Tullio.jl| version on the CPU. Unfortunately, GPU support by \verb|Tullio.jl| is still experimental and especially on the gradient step 
            we could not achieve reasonable results with it.
            \begin{table}[h]
                \begin{tabular}{l l l l l}
                    & plain & $\nabla$ plain & \verb|Tullio.jl| & $\nabla$ \verb|Tullio.jl| \\
                \hline
                CPU & \SI{83.9}{\milli\second} & \SI{7.18}{\second} & \SI{5.53}{\milli\second}  & \SI{119.8}{\milli\second}   \\ 
                GPU & \SI{2.5}{\milli\second}  & \SI{22.9}{\milli\second}& \SI{4.00}{\milli\second}  & \SI{12.53}{\second} \\
                \hline
                \hline
                    & Jax & $\nabla$ JAX && \\
                \hline
                CPU & \SI{48}{\milli\second}   & \SI{364}{\milli\second}&   & \\
                GPU & \SI{887}{\micro\second}   & \SI{10.2}{\milli\second}&   &
                \end{tabular}
                \caption{Runtimes of the Total Variation regularizer for different Julia versions and Jax. 
                    We used a 3 dimensional Float32 array with size $300 \times 300 \times 300$.  }
                \label{tab:reg}
            \end{table}
            We also compare the performance to an implementation written in Python with the Framework JAX \cite{jax2018github}. 
            The GPU version seems to outperform the Julia version by roughly a factor of $2 - 3$ in both forward and gradient pass.
            However, on the CPU \verb|Tullio.jl| is considerably faster on CPUs. 
            One could always squeeze more performance out of the gradient calculations if the kernels would be hand optimized.
            However, in our package we especially try avoid that because of the multi dimensionality it is much more convenient
            to rely on AD and as shown above the performance is usually acceptable.

    \subsection{Full Deconvolution}
        The aim of this comparison is not to compare the quality of the results but the computing time to achieve similar reconstructions. The algorithms used in \verb|DeconvOptim.jl| are not fundamentally different to a plain Lucy-Richardson deconvolution and therefore the results will 
        not exceed those results significantly in terms of quality.\\
        In \autoref{tab:deconv} we show the computing time for different algorithms and packages and in \autoref{tab:deconvprop} the basic settings
        in each package.
        To account for the fact that we do not make a quantitative comparison of the results, we add a conservative \SI{50}{\percent} error
        to the runtimes.
        The different packages used were \verb|ThreeDeconv.jl| \cite{ikoma2018convex}, \verb|Huygens| Professional version 21.04 (Scientific Volume Imaging, The Netherlands, \url{http://svi.nl}), \verb|DeconvolutionLab2| \cite{deconvlab2} and \verb|GenericDeconv|.

        For the results of \verb|GenericDeconv| (written in Matlab by Rainer Heintzmann) we used a Poisson loss function with a L-BFGS minimizer and a quadratic non-negativity constraint.
        When the TV regularizer was added the weight was $\lambda = 0.002$.
        The general idea of \verb|GenericDeconv| is very similar to \verb|DeconvOptim.jl|.
        \verb|DeconvolutionLab2| offers a wide variety of different algorithms which however only run on a CPU. To put the numbers into context, even the non-iterative Tikhonov Regularization Inverse Filter (TRIF/TR) had a runtime of \SI{4}{\second}. In the table we show the results of an 
        iterative Lucy-Richardson deconvolution. As number of iterations we set 80 and as regularizer weight $\lambda=0.002$.\\
        In \verb|DeconvOptim.jl| we measured the runtime of the default deconvolution routine with a Poisson loss function
        and the runtime of straightforward Lucy-Richardson deconvolution without a regularizer.
        \verb|ThreeDeconv.jl| is another Julia deconvolution toolbox for deconvolution of three dimensional data.
        In contrast to their according publication \cite{ikoma2018convex} we needed more iterations to achieve good results
        on our used dataset. The regularizer weight was $\lambda=10^{-7}$. 
        The software requires a flat and a dark field image we could not provide. That might influence the quality of the reconstructed images
        but in terms of performance the runtimes might by only by a factor of 2-4 faster than the runtimes we obtained(Ikoma et al. used 140 iterations in their deconvolutions.).

        Since it is hard to compare all different images with a numerical loss function value, we compare them visually.
        The CPU versions were multi threaded (if possible). \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
        \begin{table}[h]
            \begin{tabular}{l l l}
                &  CPU in s& GPU in s\\ 
            \hline
            \verb|DeconvOptim.jl| & 14.0 & 0.86\\
            \verb|DeconvOptim.jl| - TV & 18.9 & 1.55 \\
            Lucy-Richardson (Julia) & 14.8 & 1.26 \\
            \verb|ThreeDeconv.jl|& 2415 & 44.5 \\
            \verb|GenericDeconv|  & 127 & 5.9\\
            \verb|GenericDeconv| - TV & 213 & 8.7 \\
            \verb|Huygens|  & & \\
            \verb|DeconvolutionLab2| - LR & 1089 & \\
            \verb|DeconvolutionLab2| - LR TV& 1131 & 
            \end{tabular}
            \caption{Runtimes of different deconvolution implementations.}
            \label{tab:deconv}
        \end{table}

        \begin{table}[h]
            \begin{tabular}{l l l}
                & Loss & iterations \\ 
            \hline
            \verb|DeconvOptim.jl| & Poisson & 15 \\
            \verb|DeconvOptim.jl| TV & Poisson & 15\\
            Lucy-Richardson & Poisson & 120 \\
            \verb|ThreeDeconv.jl|  & Gauss+Poisson& 500\\
            \verb|GenericDeconv|  & Poisson & 40\\
            \verb|GenericDeconv| TV & Poisson & 40 \\
            \verb|Huygens|  & & \\
            \verb|DeconvolutionLab2| LR & Poisson & 200\\
            \verb|DeconvolutionLab2| LR TV& Poisson & 200 
            \end{tabular}
            \caption{Overview which loss function (noise model) and the number of iterations is used.}
            \label{tab:deconvprop}
        \end{table}

        As summary of those performance tests we can state that our Julia implementation is very competitive and especially on the CPU it is only
        beaten by the commercial \verb|Huygens| software. Despite \verb|ThreeDeconv.jl| written in Julia 
        it is notably slower in comparison to our implementation.
        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its performance is poor in comparison to all
        other packages.

        \begin{figure}[h]
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/DeconvOptim_cuda_no_regularizer_0.87s.png}
                \caption{\texttt{DeconvOptim.jl} without regularizer}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/DeconvOptim_TV_0.002.png}
                \caption{\texttt{DeconvOptim.jl} with TV}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/Lucy_richardson_julia.png}
                \caption{\texttt{DeconvOptim.jl} Lucy-Richardson}
            \end{subfigure}
            \bigskip
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/Deconvolution_Lab2_200iterations.PNG}
                \caption{\texttt{Deconvolution\\Lab2} with TV}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/ThreeDeconv_600_iterations.png}
                \caption{\texttt{ThreeDeconv.jl}}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/noisy.png}
                \caption{~~Measured image with Poisson noise}
            \end{subfigure}
            \caption{Overview of some of the deconvolution results of different packages.}
            \label{img:results}
        \end{figure}

\section{Summary}
    In conclusion, \verb|DeconvOptim.jl| is a very performant, flexible deconvolution software to deconvolve multi dimensional datasets.
    Its focus has been from the beginning to be fast and the source code should be automatic differentiated by the available
    packages in Julia. Usually we would expect that AD decreases performances however our software is faster than
    many other packages which have been written with hand-optimized gradients.
    Furthermore, our toolbox is not restricted in dimensionality and has mechanism to prevent wrap-around artifacts which
    occurs with FFT based convolutions.
    Julia's metaprogramming capabilities allow together with \verb|Tullio.jl| to generate regularizer which have high performance
    and are easy to adapt.
    In future, we want to support more regularizers on GPUs since they can not be handled efficiently with the current \verb|Tullio.jl| solution.

\input{bib.tex}

\end{document}

### 2021-06-29 paper/paper.tex
Update paper draft

@@
 
-\todo{consistent notation with vector and indices}
 \todo{fix code formatting}
@@
         However, such approaches create often several copies of the data. 
-We currently use \verb|Tullio.jl|\footnote{\url{https://github.com/mcabbott/Tullio.jl}} to create efficient functions providing a function to calculate the regularizer and the gradient.
-For simple expressions
-        such as below, \verb|Tullio.jl| registers an analytical gradient and therefore allows to apply the same mechanisms to the gradient calculation which have been used for the regularizer evaluation itself \todo{ask McAbott for reason}.
+        We currently use \verb|Tullio.jl|\footnote{\url{https://github.com/mcabbott/Tullio.jl}} to create efficient functions 
+        calculating the regularizer and the gradient. For simple expressions
+        such as below, \verb|Tullio.jl| registers an analytical gradient and therefore allows to apply the same efficient mechanisms 
+        to the gradient calculation which have been used for the regularizer evaluation itself \todo{ask McAbott for reason}.
         A (smoothed) Total variation with \verb|Tullio.jl| is defined here:
@@
         Additionally, we want to demonstrate the mechanism to reduce wrap-around artifacts in the deconvolution.
-
-        \todo{1D dataset}
+        In \autoref{fig:1D_dataset} we can see on the left hand side a data series which has been simulated 
+        as a convolution with a PSF and degraded with additive Gaussian noise.
+        \begin{figure}[h]
+            \begin{subfigure}[b]{.25\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{figures/1d_plot_data_blurred.pdf}
+                \caption{}
+                \label{fig:1D_dataseta}
+            \end{subfigure}%
+            \begin{subfigure}[b]{.25\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{figures/1d_plot_data_res_pad_vs_nopad.pdf}
+                \caption{}
+                \label{fig:1D_datasetb}
+            \end{subfigure}
+            \caption{1D data which has been convolved with a PSF and was degraded with additive Gaussian noise with $\sigma=1.0$.}
+            \label{fig:1D_dataset}
+        \end{figure}
+        On the right hand we can see the results of the following deconvolution:
+        \begin{lstlisting}[language=Julia]
+r_p, o = deconvolution(measured, psf, loss=Gauss(),
+     iterations=12, regularizer=TV(num_dims=1),
+     λ=0.05, padding=1)
+r, o = deconvolution(measured, psf, loss=Gauss(), 
+     iterations=12, regularizer=TV(num_dims=1),
+     λ=0.05, padding=0)
+        \end{lstlisting}
+    The firs statement applies a total padding of $1$ meaning that the size is doubled and therefore the measured data is padded.
+    As we can see, the blue curve in \autoref{fig:1D_datasetb} does not have the spikes at the boundaries as the green curve does have.
+    Also we notice that the deconvolved data in \autoref{fig:1D_datasetb} does not show all the details which are visible in the ground truth.
+    The reason is that the PSF is a low pass filter and therefore only frequencies which have been passed through the filter 
+    can be enhanced in terms of contrast in a deconvolved result.
 
     \subsection{Influence of Regularizer}
+        In this part we want to demonstrate the influence of the regularizer.
+        \autoref{fig:fabioa} is a simulated imaged which has been affected by Poisson shot noise and blurred by a PSF.
+        \autoref{fig:fabiob} shows the results after 15 iterations of the deconvolution. 
+        We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.
+        \autoref{fig:fabioc} shows the results after 15 iterations of the deconvolution but regularized with a Good's roughness regularizer.
+        The total image quality is much better. A larger regularizer weight dampens the artifacts even more but also results in lower
+        resolution.
+        \begin{figure}[h]
+            \begin{subfigure}[b]{.166\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{figures/fabio_blurry.png}
+                \caption{Measured}
+                \label{fig:fabioa}
+            \end{subfigure}%
+            \begin{subfigure}[b]{.166\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{figures/fabio_deconv_no_reg_iter_30.png}
+                \caption{Without regularizer}
+                \label{fig:fabiob}
+            \end{subfigure}%
+            \begin{subfigure}[b]{.166\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{figures/fabio_deconv_regularizer_005_iter_30.png}
+                \caption{With regularizer}
+                \label{fig:fabioc}
+            \end{subfigure}%            
+            \caption{The left image has been convolved with a PSF and affected by Poisson shot noise (1000 photons expected for the brightest pixel).
+The image in the middle and the right are results from the deconvolution.}
+            \label{fig:image}
+        \end{figure}
+        In \autoref{fig:fft_data_image} we show the absolute value of the FFT of the data. The blue curve is the measured data and as it can
+        be seen the value is lower than the red ground truth value. This is again due to the low pass filter effect of the PSF.
+        The measured curve also contains high frequency information which has been added due to noise and would not be expected 
+        after a pure convolution.
+        \begin{figure}[h]
+            \centering
+            \includegraphics[width = .4\textwidth]{figures/frequencies_img.pdf}
+            \caption{This plot shows the absolute value of the FFT of the data.}
+            \label{fig:fft_data_image}
+        \end{figure}
+        We see that the orange curve also contains high spatial frequency information. The reason is, that the deconvolution does amplify also noise
+        without a regularizer. The green curve shows that the regularizer indeed dampens the high frequencies and results in a visually much
+        nicer image which is also closer to the ground truth
 
@@
         terms of their total performance.
-
         \subsubsection{Regularizer}

### 2021-06-30 paper/paper.tex
Update paper content

@@
 \usepackage{siunitx}
+\usepackage{here}
 \newcommand\todo[1]{\textcolor{red}{\textbf{TODO: #1}}}
@@
 \end{align}
-Due to the noise, deconvolution is an ill-posed problem which cannot be solved directly.\\
+Due to the noise and the low pass filter effect of the PSF, deconvolution is an ill-posed problem which cannot be solved directly.\\
 A well known approach, because of its simplicity, has been the iterative Richardson-Lucy deconvolution algorithm \cite{Richardson:72}, \cite{lucy:74} for Poisson noise degraded signals.
 Another common method is the non-iterative Wiener filter \cite{wiener2013extrapolation} because of its predictable runtime.
-Wiener filter assumes additive noise which is often not suitable, especially in low light conditions as in microscopy or astronomy. 
+Wiener filter assumes additive noise which is often not true, especially in low light conditions as in microscopy or astronomy. 
 Recently machine learning based methods have become more and more favoured in deconvolution methods because
 of the possibility to add learned properties of similar images to the algorithm \cite{Kruse_2017_ICCV}.
-However, those implementations are usually restricted to cases where many experimental datasets are available for the characterization.
+However, those implementations are usually restricted to cases where experimental datasets are available for the characterization and training.
+\verb|DeconvOptim.jl| offers several deconvolution algorithms like the iterative Richardson-Lucy algorithms but also
+a much more flexible method which is based on a loss function being minimized by a gradient descent.
+Also this toolbox is not restricted in dimensionality and therefore can be applied to deconvolution problems in many different fields.
 
-\section{Convolution}
-To obtain fast deconvolution algorithms we also need a fast way to calculate the convolution operations.
+\section{Efficient Convolutions}
+The mathematical definition of a convolution is
+\begin{equation}
+    (h * S)(\mathbf r) = \int_{-\infty}^{\infty} h(\mathbf r - \mathbf x) \cdot S(\mathbf x) \, \mathrm d \mathbf x.
+    \label{eq:conv}
+\end{equation}
+To obtain efficient deconvolution algorithms we also need a efficient way to calculate the convolution operations.
 In these times, convolution operations of spatially small kernels $h$ can be calculated on GPUs very efficiently.
-However, often the blurring kernel $h$ is not spatially small and might be also multi dimensional. In that case, FFT based convolutions
+However, often the blurring kernel $h$ is not spatially small and might be also multi-dimensional. In that case, FFT based convolutions
 outperform sliding kernels. In microscopy and astronomy that is often the case, since a defocus broadens the PSF.
@@
     \begin{equation}
-        \mathcal F\left\{(h * g)\right\}(\mathbf k) = \mathcal F\{h\} (\mathbf k) \cdot \mathcal F\{g\} (\mathbf k),
+        \mathcal F\left\{(h * S)\right\}(\mathbf k) = \mathcal F\{h\} (\mathbf k) \cdot \mathcal F\{S\} (\mathbf k),
         \label{eq:fftconv}
@@
         which means that a Fourier transform of a  convolution operation is equivalent to a point wise multiplication of the Fourier transforms 
-        of $h$ and $g$.
+        of $h$ and $S$.
         Fortunately, the Fourier transform operations can be calculated even for moderate large 3D arrays quickly on modern computing machines via
         the Fast Fourier Transform (FFT).
-        In Julia, \verb|FFTW.jl| offers a convenient interface to the fast FFTW library \cite{FFTW05}.
+        In Julia, \verb|FFTW.jl| offers a convenient interface to the FFTW library \cite{FFTW05}.
         The time complexity to calculate \autoref{eq:fftconv} is $\mathcal{O}(N \cdot \log N)$ for a one dimensional discretized dataset with $N$ samples.
@@
 \subsection{Sliding Convolution Windows}
-Convolutions can be also calculated with a sliding windows as show in \todo{figure}. 
+Convolutions can be also calculated with a sliding kernel in real space which is the direct approach to
+solve the integral in \autoref{eq:conv}.
 That mechanism is the working principle
@@
 is suitable on GPUs. However, the computational complexity for a 2D kernel with size $K \times L$ applied on an image with
-$N \times M$ data points is $\mathcal O(N \cdot M \cdot K \cdot L)$. It is clear that for larger kernel sizes the sliding method 
+$N \times M$ data points is $\mathcal O(N \cdot M \cdot K \cdot L)$. It is clear that for larger kernel sizes ($K,L \gg 1$) the sliding method 
 has worse computational complexity than the FFT based convolutions. The many cores of a GPU can mitigate that to a certain extent
-but since the FFT based method can be also executed in parallel fashion, both approaches profit from parallelization.
+but since the FFT (CuFFT in the CUDA library \cite{CUDA}) can be also executed in parallel fashion, both approaches profit from parallelization.
 
@@
         \end{subfigure}
-        \caption{Comparison between two blurred images. The left images is a straightforward FFT based blurred image.
-        The zoomed region shows dark artifacts at the left side. Also at the top of the image some dark regions from
+        \caption{Comparison between two blurred images. The image a) is a straightforward FFT based blurred image.
+        The zoomed region shows dark artifacts at the left side originated from the right hand side. Also at the top of the image some dark regions from
         the bottom scattered into the bright sky.
-        The right image was padded before blurring with 10 pixels on each side with value 0.7. The blur kernel was a Gaussian kernel
+        Image b) was padded before blurring with 10 pixels on each side with value 0.7. The blur kernel was a Gaussian kernel
         with standard deviation $\sigma=\SI{3}{pixel}$.}
@@
 
+\subsection{Preferred Convolution}
+The current state of \verb|DeconvOptim.jl| uses the FFT approach to calculate the convolution.
+However, in principle one could add the possibility to change to spatially based convolutions.
+But since the runtime gets especially long in multi-dimensional signal deconvolution where FFT based methods
+are faster, we always use FFT based convolutions.
+
 \section{Inverse Modelling}
 In \autoref{fig:pipeline} we show our approach to deconvolution.
-The general idea is to create a physical forward model describing the measurement process.
+The general idea is to create a (physical) forward model describing the measurement process.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width = .5\textwidth]{figures/pipeline.pdf}
+    \caption{}
+    \label{fig:pipeline}
+\end{figure}
+
 At the beginning of the optimization we start with an initial guess $x(\mathbf r)$. 
 Via a mapping function we can impose some restrictions to the final solution (e.g. non-negativity, certain value intervals).
-The forward model (can be a convolution) is then applied to the mapped reconstruction. This result is compared
-with our noisy measurement with a certain loss function.
+The forward model is then applied to the mapped reconstruction. We provide a default function where 
+the forward function is a convolution but we also allow to plug in a different forward model into the pipeline.
+This output of the forward function is compared
+with our noisy measurement under a certain loss function.
 Since deconvolution is an ill-posed problem we regularize the loss function with a regularizer.
-Via automatic differentation (AD) we then calculate the gradient with respect to the reconstruction $x(\mathbf r)$. 
-The values of the total loss and the gradient are then used by an optimizer to apply some kind of gradient descent optimization to get a proper reconstruction.\\
+Afterwards we calculate the gradient of the loss function with respect to reconstruction $x(\mathbf r)$ via automatic differentation (AD).
+The values of the total loss and the gradient are then used by an optimizer (to minimize the total loss) to apply some kind of gradient descent optimization to get a proper reconstruction.\\
 
@@
 which is built from a finite number of past function and gradient evaluations. 
-In comparison to the Richardson-Lucy algorithm often results are converged after 20 to 50 iterations whereas Richardson-Lucy often takes
-a few hundreds iterations. However, as we will see later due to the more complex optimization routine the speed-up in using L-BFGS is for simple 
-deconvolution often minor.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = .5\textwidth]{figures/pipeline.pdf}
-    \caption{}
-    \label{fig:pipeline}
-\end{figure}
+In comparison to the Richardson-Lucy algorithm results are often good after 10 to 30 iterations whereas Richardson-Lucy takes
+a few hundreds iterations. 
+However, as we will see later due to the more complex optimization routine the speed-up in using L-BFGS is for simple 
+deconvolution minor.
 
@@
     $\text{rec}^2$ is definitely non-negative. Instead of directly using $\text{rec}$ we compare
-    $\text{rec}^2$ with the measurement $Y$. This mapping function does not change the result as long
+    $\text{rec}^2$ with the measurement $Y$. This mapping function does not change the outcome as long
     as it is an surjective function for the desired number space (e.g. a parabola is non-negative and covers all positive values) 
@@
     in the whole definition space.
+    Hence the final result is $\text{rec}^2$ in case of the quadratic mapping.
 
 \subsection{Wrap-around Artifacts Suppression}
+    To prevent that wrap-around artifacts occur during deconvolution we can instead
+    of reconstructing an object having the same size as the measurement, reconstruct
+    an object having a slightly larger size. This is shown in \autoref{fig:wrap_around}.
+    \begin{figure}[h]
+        \centering
+        \begin{tikzpicture}
+            \draw[fill=red!20!white] (0,0) rectangle (4,4);
+            \node[color=red] at (2, 3.8) {Padded area};
+            \draw[fill=gray!40!white] (0.5,0.5) rectangle (3.5,3.5); 
+            \node[text width=2.5cm, color=black] at (2, 2) {area compared with measurement};
+        \end{tikzpicture}
+        \caption{Reconstructed data is padded before deconvolution but only the red region is compared with the measurement.}
+        \label{fig:wrap_around}
+    \end{figure}
+    Consequently, we only compare the grey part of the reconstruction with the measurement.
+    Through the AD and the convolution operations we still optimize for the whole area (including the red one).
+    With that padding we prevent that images on the boundary influence in circular manner the reconstruction.
 
@@
 
-\subsection{Data Term}
-    As already mentioned, Poisson shot noise is often the dominant source of noise.
+\subsection{Poisson Data Term}
+    As already mentioned, Poisson shot noise is often the dominant source of noise hence we 
+    explain the details.
     The key idea is to interpret the measurement as a stochastic process. Our aim is to find a deconvolved image which describes as accurate as possible the measured image.
-Mathematically the probability for a certain measurement $Y$ is
+    Mathematically the probability for a certain measurement $Y$ under Poisson noise is
 
@@
         As the name suggests, Total variation tries to penalize variation in the image intensity. Therefore it sums up the gradient strength at each point
-        of the image. In 2D this is:
+        of the image:
         \begin{equation}
@@
         Since we look at the magnitude of the gradient strength, this regularizer is anisotropic.
-        In 2D this is:
+        In 2D TV is defined like: 
         \begin{equation}
@@
         \end{lstlisting}
-        \lstinline{ϵ} is needed because for regions where \lstinline{arr == 0} the gradient would result in singularities.
+        \lstinline{ϵ} is needed for regions where \lstinline{arr == 0} because otherwise the gradient return infinite values.
         Note, that definition here just demonstrates how the regularizer can be written down.
-        In our toolbox we allow for much for options. \verb|Tullio.jl| cannot handle multi dimensional data yet.
-        Via Julia's metaprogramming capability we create regularizers which can vary in step size, dimensionality and
-        different weighting in dimensions.
+        In our toolbox we allow for much more options. Since \verb|Tullio.jl| cannot handle generic multi-dimensional data yet
+        we create regularizers which can vary in step size, dimensionality and
+        different weighting in dimensions via Julia's metaprogramming capability.
         A call like 
@@
         and the third dimensions is weighted differently.
-        Such options are available for most of the regularizers.
+        Such options are available for most of the regularizers implemented in our toolbox.
 
@@
         Additionally, we want to demonstrate the mechanism to reduce wrap-around artifacts in the deconvolution.
-        In \autoref{fig:1D_dataset} we can see on the left hand side a data series which has been simulated 
-        as a convolution with a PSF and degraded with additive Gaussian noise.
-        \begin{figure}[h]
+        On the left hand side in \autoref{fig:1D_dataset} we can see a data series which has been simulated 
+        as a convolution with a PSF and degradation with additive Gaussian noise.
+        \begin{figure}[H]
             \begin{subfigure}[b]{.25\textwidth}
@@
         \end{lstlisting}
-    The firs statement applies a total padding of $1$ meaning that the size is doubled and therefore the measured data is padded.
-    As we can see, the blue curve in \autoref{fig:1D_datasetb} does not have the spikes at the boundaries as the green curve does have.
+    The first statement applies a total padding of $1$ meaning that the size is doubled and therefore the measured data is padded.
+    As we can see, the blue curve in \autoref{fig:1D_datasetb} does not show these intense spikes at the boundaries as the green curve shows.
     Also we notice that the deconvolved data in \autoref{fig:1D_datasetb} does not show all the details which are visible in the ground truth.
@@
         In this part we want to demonstrate the influence of the regularizer.
-        \autoref{fig:fabioa} is a simulated imaged which has been affected by Poisson shot noise and blurred by a PSF.
+        \autoref{fig:fabioa} is a simulated imaged which has been affected by Poisson shot noise and blurring by a PSF.
         \autoref{fig:fabiob} shows the results after 15 iterations of the deconvolution. 
@@
             \end{subfigure}%            
-            \caption{The left image has been convolved with a PSF and affected by Poisson shot noise (1000 photons expected for the brightest pixel).
-The image in the middle and the right are results from the deconvolution.}
+            \caption{a) has been convolved with a PSF and affected by Poisson shot noise (1000 photons expected for the brightest pixel).
+b) has been deconvolved for 15 iterations without an regularizer whereas c) was regularizer with Good's roughness.}
             \label{fig:image}
         \end{figure}
-        In \autoref{fig:fft_data_image} we show the absolute value of the FFT of the data. The blue curve is the measured data and as it can
-        be seen the value is lower than the red ground truth value. This is again due to the low pass filter effect of the PSF.
+        In \autoref{fig:fft_data_image} we show the absolute value of the FFT of the data. 
+        The meaning of this plot is to judge how the deconvolution enhances the contrast of frequencies which have 
+        been blurred by the convolution before.
+        The blue curve is the measured data and is below the red ground truth curve. This is due to the low pass filter effect of the PSF.
         The measured curve also contains high frequency information which has been added due to noise and would not be expected 
@@
     \subsection{Multi-Dimensional Microscopy Data}
-        To show the full power, we deconvolve a four dimensional dataset where the measured volume consists of a 3D datasets
-        with three different color channels. The PSF is only three dimensional.
+        To show the full ability, we deconvolve a four dimensional dataset where the measured volume consists of a 3D datasets
+        with three different color channels which is shown in \autoref{fig:result_3d}.
+        The PSF is only three dimensional.
         Julia's broadcast mechanism handles that the PSF is only three dimensional and therefore
         we only need to specify over which dimensions the convolution should happen.
-
-        \todo{4D dataset}
+        \begin{figure}[h]
+            \begin{subfigure}{.25\textwidth}
+                \centering
+                \includegraphics[width = .95\textwidth]{figures/deconvolved_rgb.png}
+            \end{subfigure}%
+            \begin{subfigure}{.25\textwidth}
+                \centering
+                \includegraphics[width = .95\textwidth]{figures/deconvolved_rgb.png}
+            \end{subfigure}
+            \caption{Slice of a 3D dataset with three different colors. a) is the raw data and b) is the
+                    deconvolved image.}
+            \label{fig:result_3d}
+        \end{figure} 
+        Clearly we can see that the deconvolution removed a lot of the background blur.
 
@@
             The GPU version seems to outperform the Julia version by roughly a factor of $2 - 3$ in both forward and gradient pass.
-            However, on the CPU \verb|Tullio.jl| is considerably faster on CPUs. 
-            One could always squeeze more performance out of the gradient calculations if the kernels would be hand optimized.
-            However, in our package we especially try avoid that because of the multi dimensionality it is much more convenient
+            However, on the CPU \verb|Tullio.jl| is considerably faster. 
+            In general one could always squeeze more performance out of the gradient calculations if the kernels would be hand optimized.
+            In our package we especially try avoid that because of the multi-dimensionality it is much more convenient
             to rely on AD and as shown above the performance is usually acceptable.
@@
         The aim of this comparison is not to compare the quality of the results but the computing time to achieve similar reconstructions.
-The algorithms used in \verb|DeconvOptim.jl| are not fundamentally different to a plain Lucy-Richardson deconvolution and therefore the results will
+The algorithms used in \verb|DeconvOptim.jl| are not fundamentally different to a plain Richardson-Lucy deconvolution and therefore the results will
         not exceed those results significantly in terms of quality.\\
@@
         in each package.
-        To account for the fact that we do not make a quantitative comparison of the results, we add a conservative \SI{50}{\percent} error
-        to the runtimes.
+        One should keep in mind that such performance comparison are usually biased since we are not
+        familiar with all options which should be choosen to achieve best performance.
+        The comparison should give a rough overview which runtime is expected for each toolbox.\\
         The different packages used were \verb|ThreeDeconv.jl| \cite{ikoma2018convex}, \verb|Huygens| Professional version 21.04 (Scientific Volume Imaging, The Netherlands, \url{http://svi.nl}), \verb|DeconvolutionLab2| \cite{deconvlab2} and \verb|GenericDeconv|.
 
-        For the results of \verb|GenericDeconv| (written in Matlab by Rainer Heintzmann) we used a Poisson loss function with a L-BFGS minimizer and a quadratic non-negativity constraint.
-        When the TV regularizer was added the weight was $\lambda = 0.002$.
-        The general idea of \verb|GenericDeconv| is very similar to \verb|DeconvOptim.jl|.
-        \verb|DeconvolutionLab2| offers a wide variety of different algorithms which however only run on a CPU.
-To put the numbers into context, even the non-iterative Tikhonov Regularization Inverse Filter (TRIF/TR) had a runtime of \SI{4}{\second}.
-In the table we show the results of an
-        iterative Lucy-Richardson deconvolution. As number of iterations we set 80 and as regularizer weight $\lambda=0.002$.\\
-        In \verb|DeconvOptim.jl| we measured the runtime of the default deconvolution routine with a Poisson loss function
-        and the runtime of straightforward Lucy-Richardson deconvolution without a regularizer.
-        \verb|ThreeDeconv.jl| is another Julia deconvolution toolbox for deconvolution of three dimensional data.
-        In contrast to their according publication \cite{ikoma2018convex} we needed more iterations to achieve good results
-        on our used dataset. The regularizer weight was $\lambda=10^{-7}$. 
-        The software requires a flat and a dark field image we could not provide. That might influence the quality of the reconstructed images
-        but in terms of performance the runtimes might by only by a factor of 2-4 faster than the runtimes we obtained(Ikoma et al. used 140 iterations in their deconvolutions.).
-
-        Since it is hard to compare all different images with a numerical loss function value, we compare them visually.
-        The CPU versions were multi threaded (if possible). \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
         \begin{table}[h]
@@
             \verb|DeconvOptim.jl| - TV & 18.9 & 1.55 \\
-            Lucy-Richardson (Julia) & 14.8 & 1.26 \\
+            Richardson-Lucy (Julia) & 14.8 & 1.26 \\
             \verb|ThreeDeconv.jl|& 2415 & 44.5 \\
@@
 
+        For the results of \verb|GenericDeconv| (written in Matlab by Rainer Heintzmann) we used a Poisson loss function with a L-BFGS minimizer and a quadratic non-negativity constraint.
+        When the TV regularizer was added the weight was $\lambda = 0.002$.
+        The general idea of \verb|GenericDeconv| is very similar to \verb|DeconvOptim.jl|.
+        \verb|DeconvolutionLab2| offers a wide variety of different algorithms which however only run on a CPU.
+To put the numbers into context, even the non-iterative Tikhonov Regularization Inverse Filter (TRIF/TR) had a runtime of \SI{4}{\second}.
+In the table we show the results of an
+        iterative Richardson-Lucy deconvolution. As number of iterations we set 80 and as regularizer weight $\lambda=0.002$.\\
+        In \verb|DeconvOptim.jl| we measured the runtime of the default deconvolution routine with a Poisson loss function
+        and the runtime of straightforward Richardson-Lucy deconvolution without a regularizer.
+        \verb|ThreeDeconv.jl| is another Julia deconvolution toolbox for deconvolution of three dimensional data.
+        In contrast to their according publication \cite{ikoma2018convex} we needed more iterations to achieve good results
+        on our used dataset. The regularizer weight was $\lambda=10^{-7}$. 
+        The software requires a flat and a dark field image we could not provide. That might influence the quality of the reconstructed images
+        but in terms of performance the runtimes might by only by a factor of 2-4 faster than the runtimes we obtained (Ikoma et al. used 140 iterations in their datasets).
+
+        Since it is hard to judge the quality of those results with a numerical loss function value, we compare them visually.
+        The CPU versions were multi threaded (if possible). \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
+
         \begin{table}[h]
@@
             \verb|DeconvOptim.jl| TV & Poisson & 15\\
-            Lucy-Richardson & Poisson & 120 \\
+            Richardson-Lucy & Poisson & 120 \\
             \verb|ThreeDeconv.jl|  & Gauss+Poisson& 500\\
@@
             \end{tabular}
-            \caption{Overview which loss function (noise model) and the number of iterations is used.}
+            \caption{Overview which loss function (noise model) and number of iterations are used.}
             \label{tab:deconvprop}
@@
         other packages.
-
         \begin{figure}[h]
@@
                 \includegraphics[width=\textwidth]{figures/Lucy_richardson_julia.png}
-                \caption{\texttt{DeconvOptim.jl} Lucy-Richardson}
+                \caption{\texttt{DeconvOptim.jl} Richardson-Lucy}
             \end{subfigure}
-            \bigskip
             \begin{subfigure}{.3\textwidth}
@@
                 \centering
+                \includegraphics[width=\textwidth, height=2.5cm]{example-image-a}
+                \caption{\texttt{GenericDeconv}}
+            \end{subfigure}
+            \begin{subfigure}{.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth, height=2.5cm]{example-image-a}
+                \caption{\texttt{Huygens}}
+            \end{subfigure}
+            \begin{subfigure}{.3\textwidth}
+                \centering
                 \includegraphics[width=\textwidth]{figures/noisy.png}
@@
 \section{Summary}
-    In conclusion, \verb|DeconvOptim.jl| is a very performant, flexible deconvolution software to deconvolve multi dimensional datasets.
+    In conclusion, \verb|DeconvOptim.jl| is a very performant, flexible deconvolution software to deconvolve multi-dimensional datasets.
     Its focus has been from the beginning to be fast and the source code should be automatic differentiated by the available
-    packages in Julia. Usually we would expect that AD decreases performances however our software is faster than
+    packages in Julia. Usually we would expect that AD decreases performances but still our software is faster than
     many other packages which have been written with hand-optimized gradients.
     Furthermore, our toolbox is not restricted in dimensionality and has mechanism to prevent wrap-around artifacts which
-    occurs with FFT based convolutions.
-    Julia's metaprogramming capabilities allow together with \verb|Tullio.jl| to generate regularizer which have high performance
+    occur with FFT based convolutions.
+    Julia's metaprogramming capabilities together with \verb|Tullio.jl| allow to generate regularizer which have high performance
     and are easy to adapt.

### 2021-07-01 paper/paper.tex
Update content of paper

@@
 Deconvolution is a versatile method to enhance the quality of signals measured with systems which can 
-be mathematically expressed as a convolution of a system's response function with a signal. 
+be expressed mathematically as a convolution of a system's response function with a signal. 
 In this paper, we present \verb|DeconvOptim.jl|, a flexible toolbox written in Julia to deconvolve multi-dimensional signals which have been
 degraded by a multi-dimensional signal response function. 
-\verb|DeconvOptim.jl| works both on CPUs and GPUs and utilizes recent advancements in Julias Automatic Differentiation ecosystem.
-The performance on CPUs surpasses the one of existing open source libraries.
-The library is applicable to one dimensional time series datasets but also to multi-dimensional microscopy imaging datasets.
+\verb|DeconvOptim.jl| works both on CPUs and GPUs and utilizes recent advancements in Julias automatic differentiation ecosystem.
+
+In this work we demonstrate that \verb|DeconvOptim.jl| surpasses the performance of existing open source libraries clearly
+and is applicable to one dimensional time series datasets but also to multi-dimensional microscopical imaging datasets.
 \end{abstract}
 
-\todo{fix code formatting}
-
 \section{Introduction}
-Deconvolution has been a long addressed problem especially in astronomical imaging, digital signal processing or microscopy imaging.
+Deconvolution has been a long addressed problem especially in astronomical imaging, digital signal processing or microscopical imaging.
 The assumption is that images are degraded by some kind of blur which can be described as a convolution between a kernel $h$ and the image $S$:
@@
 in the image.
-Often this convolution operation is disturbed by different types of noise where the most common are additive Gaussian noise due to the read out of the camera sensors or Poisson shot noise due to the quantum nature of photons:
+Often this convolution operation is disturbed by different types of noise where the most common are additive Gaussian noise (e.g.
+due to the read out of the camera sensors) or Poisson shot noise (e.g.
+due to the quantum nature of photons):
 \begin{align}
@@
 \end{align}
-Due to the noise and the low pass filter effect of the PSF, deconvolution is an ill-posed problem which cannot be solved directly.\\
+Due to noise and the low pass filter effect of the PSF, deconvolution is an ill-posed problem which cannot be solved directly.\\
 A well known approach, because of its simplicity, has been the iterative Richardson-Lucy deconvolution algorithm \cite{Richardson:72}, \cite{lucy:74} for Poisson noise degraded signals.
 Another common method is the non-iterative Wiener filter \cite{wiener2013extrapolation} because of its predictable runtime.
-Wiener filter assumes additive noise which is often not true, especially in low light conditions as in microscopy or astronomy. 
+The Wiener filter assumes additive noise which is often not true, especially in low light conditions as in microscopy or astronomy. 
 Recently machine learning based methods have become more and more favoured in deconvolution methods because
@@
         The time complexity to calculate \autoref{eq:fftconv} is $\mathcal{O}(N \cdot \log N)$ for a one dimensional discretized dataset with $N$ samples.
-        For a 2D dataset with size $N \times M$ it is $\mathcal{O}(N \cdot M \log(N + M))$ and similar for higher dimensions.
+        For a 2D dataset with size $N \times M$ it is $\mathcal{O}(N \cdot M \log(N + M))$ and accordingly for higher dimensions.
 
@@
 \subsection{Wrap-Around Artifacts in FFT based Convolutions}
-    One drawback of the FFT based convolution are wrap-around artifacts. The reason is, that the FFT operation calculates the discrete
+    One drawback of a FFT based convolution are wrap-around artifacts. The reason is, that the FFT operation calculates the discrete
     Fourier transform (DFT) which inherently assumes periodic data. If one applies a FFT on a finite data set the assumption is that
     this finite data set repeats itself. 
-    To weaken the wrap-around artifacts in the convolution one can zero or mean pad the image before convolution and remove the boundaries afterwards.
+    To weaken the wrap-around artifacts in the convolution one can zero or mean pad the image before convolution 
+    and remove the padding afterwards.
 
@@
 Since deconvolution is an ill-posed problem we regularize the loss function with a regularizer.
-Afterwards we calculate the gradient of the loss function with respect to reconstruction $x(\mathbf r)$ via automatic differentation (AD).
+Afterwards we calculate the gradient of the loss function with respect to the reconstruction $x(\mathbf r)$ via automatic differentation (AD).
 The values of the total loss and the gradient are then used by an optimizer (to minimize the total loss) to apply some kind of gradient descent optimization to get a proper reconstruction.\\
@@
 a few hundreds iterations. 
-However, as we will see later due to the more complex optimization routine the speed-up in using L-BFGS is for simple 
+However, as we will see later due to the more complex optimization routine the speed-up in using L-BFGS is for a simple 
 deconvolution minor.
@@
 The final source code has a modified version of \autoref{eq:gradpoisson} as registered gradient for \autoref{eq:poisson_loss}.
-The reason is, that for values of $\mu(\mathbf r) \leq 0$ the equation is not defined and has to be handled separately.
+The reason is, that for values of $\mu(\mathbf r) = 0$ the equation is not defined and has to be handled separately.
 
@@
         such as below, \verb|Tullio.jl| registers an analytical gradient and therefore allows to apply the same efficient mechanisms 
-        to the gradient calculation which have been used for the regularizer evaluation itself \todo{ask McAbott for reason}.
+        to the gradient calculation which have been used for the regularizer evaluation itself.
         A (smoothed) Total variation with \verb|Tullio.jl| is defined here:
@@
         \end{lstlisting}
-        \lstinline{ϵ} is needed for regions where \lstinline{arr == 0} because otherwise the gradient return infinite values.
-        Note, that definition here just demonstrates how the regularizer can be written down.
+        \lstinline{ϵ} is needed for regions where \lstinline{arr == 0} because otherwise the gradient returns infinite values.
+        Note, that definition just demonstrates how the regularizer can be written down.
         In our toolbox we allow for much more options. Since \verb|Tullio.jl| cannot handle generic multi-dimensional data yet
@@
         \autoref{fig:fabioa} is a simulated imaged which has been affected by Poisson shot noise and blurring by a PSF.
-        \autoref{fig:fabiob} shows the results after 15 iterations of the deconvolution. 
-        We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.
-        \autoref{fig:fabioc} shows the results after 15 iterations of the deconvolution but regularized with a Good's roughness regularizer.
-        The total image quality is much better. A larger regularizer weight dampens the artifacts even more but also results in lower
-        resolution.
         \begin{figure}[h]
@@
             \caption{a) has been convolved with a PSF and affected by Poisson shot noise (1000 photons expected for the brightest pixel).
-b) has been deconvolved for 15 iterations without an regularizer whereas c) was regularizer with Good's roughness.}
+b) has been deconvolved for 30 iterations without an regularizer whereas c) was regularizer with Good's roughness.}
             \label{fig:image}
         \end{figure}
+
+        This test chart is suited to judge the resolution of a reconstruction since the pieces of the Siemens star
+        are getting closer in the center which is equivalent to higher spatial frequencies.
+        \autoref{fig:fabiob} shows the result after 30 iterations of the deconvolution. 
+        We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.
+        Additionally, we notice that the core in the Siemens star is smaller meaning better spatial resolution. 
+        \autoref{fig:fabioc} shows the results after 30 iterations of the deconvolution but regularized with a Good's roughness regularizer.
+        The total image quality is much better since the regularizer dampens the artifacts but also results in lower
+        resolution. With the regularizer weight $\lambda$ one can adjust the strength.
         In \autoref{fig:fft_data_image} we show the absolute value of the FFT of the data. 
@@
         been blurred by the convolution before.
+        The vertical black line indicates the frequency where the PSF has its bandlimit.
         The blue curve is the measured data and is below the red ground truth curve. This is due to the low pass filter effect of the PSF.
-        The measured curve also contains high frequency information which has been added due to noise and would not be expected 
+        The measured curve also contains high frequency (above the frequency limit of the PSF) information which has been added due to noise and would not be expected 
         after a pure convolution.
@@
         \end{figure}
-        We see that the orange curve also contains high spatial frequency information. The reason is, that the deconvolution does amplify also noise
+        We see that the orange curve also contains high spatial frequency information. The reason is that deconvolution amplifies noise
         without a regularizer. The green curve shows that the regularizer indeed dampens the high frequencies and results in a visually much
-        nicer image which is also closer to the ground truth
+        nicer image which is also closer to the ground truth.
+        Both the orange and the green curve show better contrast in frequency regions below the PSF resolution limit.
 
@@
         The software requires a flat and a dark field image we could not provide. That might influence the quality of the reconstructed images
-        but in terms of performance the runtimes might by only by a factor of 2-4 faster than the runtimes we obtained (Ikoma et al. used 140 iterations in their datasets).
+        but in terms of performance the runtimes might be only by a factor of 2-5 smaller than the runtimes we obtained (Ikoma et al. used 140 iterations in their datasets).
 
@@
     In future, we want to support more regularizers on GPUs since they can not be handled efficiently with the current \verb|Tullio.jl| solution.
+    Also we plan to extend the package to deconvolution of spatially varying kernels which are of importance in optical systems
+    with large field of view or poor manufacturing quality.
 

### 2021-07-01 v0.3.0/search_index.js
build based on da59e22

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas, storage=copy(μ))\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas, storage=copy(μ))\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_gauss
[…]

### 2021-07-04 src/DeconvOptim.jl
Add normalized cross correlation and energy regain for analysis

@@ -13,6 +13,7 @@ include("requires.jl")
 using Optim
  #mean
 using Statistics
+using StatsBase
 using FFTW
 FFTW.set_num_threads(12)
 using LineSearches
@@ -40,6 +41,7 @@ include("conv.jl")
 include("generic_invert.jl")
 include("lucy_richardson.jl")
 include("deconvolution.jl")
+include("analysis_tools.jl")
 
 # refresh Zygote to load the custom rrules defined with ChainRulesCore
 using Zygote: gradient

### 2021-07-04 src/analysis_tools.jl

@@ -1,0 +1,87 @@
+"""
+    relative_energy_regain(ground_truth, rec)
+
+Calculates the relative energy regain between the `ground_truth`
+and the reconstruction.
+Assumes that both arrays are 2 dimensional
+
+"""
+function relative_energy_regain(ground_truth, rec)
+    # go to fourier space
+    ground_truth_fft = fft(ground_truth)
+    rec_fft = fft(rec)
+
+    # a dict to store the values for certain frequencies
+    # we store a list since some (rounded) frequencies occur more than once
+    ΔE_R_dict = Dict{Float64, Vector{Float64}}()
+    E_R_dict = Dict{Float64, Vector{Float64}}()
+
+    # round the frequencies to 4 digits, alternative would be to bin
+    round4(x) = round(x, digits=3)
+    
+    
+    # iterate over the frequencies and calculate the relative energy regain
+    for (i₂, f₂) in enumerate(fftfreq(size(rec_fft, 2)))
+        for (i₁, f₁) in enumerate(fftfreq(size(rec_fft, 1)))
+            f_res = round4(√(f₁^2 + f₂^2))
+            Δ_E_R = abs2(ground_truth_fft[i₁, i₂] - rec_fft[i₁, i₂]) 
+            E_R = abs2(ground_truth_fft[i₁, i₂]) 
+
+            update_dict_list!(ΔE_R_dict, f_res, Δ_E_R)
+            update_dict_list!(E_R_dict, f_res, E_R)
+        end
+    end
+    
+    
+    # finally transform everything into a list of frequencies and 
+    # a list of relative energy regains
+    freqs = Float64[]
+    G_R_list = Float64[]
+    for f in sort(Float64.(keys(ΔE_R_dict)))
+        push!(freqs, f)
+        mean_ΔE_r = mean(ΔE_R_dict[f])
+        mean_E_r = mean(E_R_dict[f])
+
+        push!(G_R_list, (mean_E_r - mean_ΔE_r) / mean_E_r)
+    end
+    
+    return freqs, G_R_list
+end
+
+
+
+
+"""
+    update_dict_list!(d, k, v)
+
+Updates the dict `d` which stores a list.
+If `k` is in the keys of `d` we simply push `v` to the list
+otherwise create a new list `[v]`
+"""
+function update_dict_list!(d, k, v)
+    if haskey(d, k)
+        push!(d[k], v)
+    else
+        d[k] = [v]
+    end
+    return d
+end
+
+
+"""
[…]

### 2021-07-04 paper/paper.tex
Add more progress of paper

@@
 but since the FFT (CuFFT in the CUDA library \cite{CUDA}) can be also executed in parallel fashion, both approaches profit from parallelization.
+If the kernel is separable over the dimensions (like a Gaussian kernel) the complexity changes to $\mathcal O(N \cdot K \cdot L +  N \cdot K \cdot L)$ however most optical PSF are not separable and therefore this is not general applicable.
 
@@
     To weaken the wrap-around artifacts in the convolution one can zero or mean pad the image before convolution 
-    and remove the padding afterwards.
-
+    and remove the padding afterwards. Such approaches still suffer from artifacts when boundary values do not fit
+    to the mean or to zero as it can be observed in \autoref{fig:withpad} at the top.
     \begin{figure}[h]
@@
     \end{figure}
-
+    To solve for the wrap-around artifacts in deconvolution we use a different approach which will be presented later. 
 \subsection{Preferred Convolution}
@@
             \end{subfigure}
-            \caption{1D data which has been convolved with a PSF and was degraded with additive Gaussian noise with $\sigma=1.0$.}
+            \caption{1D data which has been convolved with a PSF and was degraded with additive Gaussian noise with $\sigma=1.0$.
+Note that for the deconvolution we have chosen a position interval which is well within the full series so that there are not wrap-around artifacts in the measurement.}
             \label{fig:1D_dataset}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/fabio_blurry.png}
+                \includegraphics[width=\textwidth]{figures/resolution_test_chart_blurry.png}
                 \caption{Measured}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/fabio_deconv_no_reg_iter_30.png}
+                \includegraphics[width=\textwidth]{figures/resolution_test_chart_no_reg_iter_30.png}
                 \caption{Without regularizer}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/fabio_deconv_regularizer_005_iter_30.png}
+                \includegraphics[width=\textwidth]{figures/resolution_test_chart_regularizer_005_iter_30.png}
                 \caption{With regularizer}
@@
             \end{subfigure}%            
-            \caption{a) has been convolved with a PSF and affected by Poisson shot noise (1000 photons expected for the brightest pixel).
-b) has been deconvolved for 30 iterations without an regularizer whereas c) was regularizer with Good's roughness.}
+            \caption{a) has been convolved with a PSF and affected by Poisson shot noise (100 photons expected for the brightest pixel).
+b) has been deconvolved for 50 iterations without an regularizer whereas c) was regularizer with Good's roughness which converged after 20 iterations with $\lambda=0.03$.}
             \label{fig:image}
@@
             \centering
-            \includegraphics[width = .4\textwidth]{figures/frequencies_img.pdf}
+            \includegraphics[width = .4\textwidth]{figures/test_chart_relative_energy_regain.pdf}
             \caption{This plot shows the absolute value of the FFT of the data.}
@@
                 \centering
-                \includegraphics[width = .95\textwidth]{figures/deconvolved_rgb.png}
+                \includegraphics[width = .95\textwidth]{figures/raw_rgb.png}
             \end{subfigure}%

### 2021-07-04 src/analysis_tools.jl
Add debug function to access reconstruction during optimization

@@ -82,6 +82,6 @@ function normalized_cross_correlation(ground_truth, measured)
     ground_truth = fl(ground_truth)
     measured = fl(measured)
 
-    ncc = crosscor(ground_truth, measured, [0], demean=false)
+    ncc = crosscor(ground_truth, measured, [0], demean=false)[begin]
     return ncc
 end

### 2021-07-04 src/deconvolution.jl

@@ -30,7 +30,7 @@ regularizers and mappings.
         `padding=0` disables any padding.
 - `optim_options=nothing`: Can be a options file required by Optim.jl. Will overwrite iterations.
 - `optim_optimizer=LBFGS()`: The chosen Optim.jl optimizer. 
-
+- `debug_f=nothing`: A debug function which must take a single argument, the current reconstruction.
 
 # Example
 ```julia-repl
@@ -58,6 +58,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
         padding=0.00,
         optim_options=nothing,
         optim_optimizer=LBFGS(linesearch=BackTracking()),
+        debug_f=nothing,
         ) where {T, N}
 
 
@@ -150,7 +151,8 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
                           optim_optimizer=optim_optimizer,
                           optim_options=optim_options,
                           mapping=mapping,
-                          loss=loss)
+                          loss=loss,
+                          debug_f=debug_f)
 
     res_out .*= rescaling
     # since we do some padding we need to extract the center part

### 2021-07-04 src/generic_invert.jl

@@ -21,7 +21,7 @@ regularizers and mappings.
     definitely should stop. Will be overwritten if `optim_options` is provided.
 - `optim_options=nothing`: Can be a options file required by Optim.jl. Will overwrite iterations.
 - `optim_optimizer=LBFGS()`: The chosen Optim.jl optimizer. 
-
+- `debug_f=nothing`: A debug function which must take a single argument, the current reconstruction. 
 """
 function invert(measured, rec0, forward; 
                 iterations=10, λ=eltype(rec0)(0.05),
@@ -30,7 +30,8 @@ function invert(measured, rec0, forward;
                 optim_options=nothing,
                 mapping=Non_negative(),
                 loss=Poisson(),
-                real_gradient=true)
+                real_gradient=true,
+                debug_f=nothing)
 
     # if not special options are given, just restrict iterations
     if optim_options == nothing
@@ -38,6 +39,13 @@ function invert(measured, rec0, forward;
     end
 
 
+    debug_f = let
+        if isnothing(debug_f)
+            identity
+        else
+            debug_f
+        end
+    end
     
     # Get the mapping functions to achieve constraints
     # like non negativity
@@ -69,9 +77,13 @@ function invert(measured, rec0, forward;
     # This leads to the common "world age problem" in Julia
     # for more details on that check:
     # https://discourse.julialang.org/t/dynamically-create-a-function-initial-idea-with-eval-failed-due-to-world-age-issue/49139/17
-    function f!(F, G, rec)
+    function fg!(F, G, rec)
+    
         # Zygote calculates both derivative and loss, therefore do everything in one step
         if G != nothing
+            # apply debug function
+            debug_f(rec)
+
             y, back = Base.invokelatest(Zygote._pullback, total_loss, rec)
             # calculate gradient
             G .= take_real_or_not(Base.invokelatest(back, 1)[2])
@@ -87,7 +99,7 @@ function invert(measured, rec0, forward;
     optim_options = Optim.Options(iterations=iterations)
     
     # do the optimization with LBGFS
-    res = Optim.optimize(Optim.only_fg!(f!), rec0, optim_optimizer, optim_options)
+    res = Optim.optimize(Optim.only_fg!(fg!), rec0, optim_optimizer, optim_options)
     res_out = mf(Optim.minimizer(res))
 
 

### 2021-07-04 paper/paper.tex
New tex version

@@
             \caption{a) has been convolved with a PSF and affected by Poisson shot noise (100 photons expected for the brightest pixel). 
-b) has been deconvolved for 50 iterations without an regularizer whereas c) was regularizer with Good's roughness which converged after 20 iterations with $\lambda=0.03$.}
+                        Deconvolved b) for 50 iterations without an regularizer c) with Good's roughness regularizer and 
+                            converged after 20 iterations with $\lambda=0.03$.}
             \label{fig:image}
@@
         are getting closer in the center which is equivalent to higher spatial frequencies.
-        \autoref{fig:fabiob} shows the result after 30 iterations of the deconvolution. 
+        \autoref{fig:fabiob} shows the result after 50 iterations of the deconvolution. 
         We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.
         Additionally, we notice that the core in the Siemens star is smaller meaning better spatial resolution. 
-        \autoref{fig:fabioc} shows the results after 30 iterations of the deconvolution but regularized with a Good's roughness regularizer.
+        \autoref{fig:fabioc} shows the results after 20 iterations of the deconvolution but regularized with a Good's roughness regularizer.
         The total image quality is much better since the regularizer dampens the artifacts but also results in lower
         resolution. With the regularizer weight $\lambda$ one can adjust the strength.
-        In \autoref{fig:fft_data_image} we show the absolute value of the FFT of the data. 
-        The meaning of this plot is to judge how the deconvolution enhances the contrast of frequencies which have 
-        been blurred by the convolution before.
-        The vertical black line indicates the frequency where the PSF has its bandlimit.
-        The blue curve is the measured data and is below the red ground truth curve. This is due to the low pass filter effect of the PSF.
-        The measured curve also contains high frequency (above the frequency limit of the PSF) information which has been added due to noise and would not be expected 
-        after a pure convolution.
+        In \autoref{fig:rel_energy_regain} we show the relative energy regain $G_\textrm{R}$ \cite{rel_energy_regain} (REG).
+        The meaning of the relative energy regain is how well certain frequencies are reconstructed in comparison
+        to the ground truth. $G_\textrm{R} = 1$ is a perfect reconstruction, $G_\textrm{R} = 0$ indicates that 
+        this frequency could not be recovered at all, $G_\textrm{R} < 0$ means that the reconstruction introduces fake frequencies
+        which do not fit to the ground truth at all.
         \begin{figure}[h]
             \centering
-            \includegraphics[width = .4\textwidth]{figures/test_chart_relative_energy_regain.pdf}
-            \caption{This plot shows the absolute value of the FFT of the data.}
-            \label{fig:fft_data_image}
+            \begin{subfigure}[b]{.23\textwidth}
+                \centering
+                \includegraphics[width =\textwidth]{figures/test_chart_relative_energy_regain.pdf}
+                \caption{Relative energy regain $G_\textrm{R}$ over different frequencies.}
+                \label{fig:rel_energy_regain}
+            \end{subfigure}
+            \hfill
+            \begin{subfigure}[b]{.23\textwidth}
+                \centering
+                \includegraphics[width =0.97 \textwidth]{figures/test_chart_ncc.pdf}
+                \caption{Normalized correlation coefficient (NCC) over the number of iterations.}
+                \label{fig:ncc}
+            \end{subfigure}
+            \caption{NCC and REG are quantitative measurements to judge the quality of a deconvolution result.}
         \end{figure}
-        We see that the orange curve also contains high spatial frequency information. The reason is that deconvolution amplifies noise
-        without a regularizer. The green curve shows that the regularizer indeed dampens the high frequencies and results in a visually much
-        nicer image which is also closer to the ground truth.
-        Both the orange and the green curve show better contrast in frequency regions below the PSF resolution limit.
+        We can see that the red measured curve shows the typical contrast loss until the maximum frequency $f_\textrm{max}$ (the PSF has
+            zero transmittance over this frequency threshold).
+        Beyond $f_\textrm{max}$ Poisson noise introduces fake frequencies.
+        The green curve shows the relative energy regain of the deconvolution without a regularizer. For certain regions below  $f_\textrm{max}$
+        the deconvolution enhances the contrast. However, around and beyond $f_\textrm{max}$ several artifacts are introduced.
+        The regularized blue curve performs much better and only certain frequencies show a relative energy regain below zero.
+        To some extent the regularized version can also recover information above $f_\textrm{max}$ which are not supported by the PSF.
+        \autoref{fig:ncc} shows the normalized correlation coefficient over the number of iterations.
+        Especially the deconvolution without an regularizer suffers from poor performance after a high number of iterations.
+        Either one has to stop early after a hand optimized iteration number or use a regularizer.
 

### 2021-07-04 docs/make.jl
Update documenter

@@ -1,7 +1,7 @@
 using Documenter, DocumenterCitations, DeconvOptim
 
 
-cite_bib = CitationBibliography(joinpath(@__DIR__, "bibtex_references.md"))
+cite_bib = CitationBibliography(joinpath(@__DIR__, "../paper/ref.bib"))
 
 DocMeta.setdocmeta!(DeconvOptim, :DocTestSetup, :(using DeconvOptim); recursive=true)
 makedocs(cite_bib, modules=[DeconvOptim],
@@ -29,6 +29,7 @@ makedocs(cite_bib, modules=[DeconvOptim],
                     "function_references/mapping.md",
                     "function_references/regularizer.md",
                     "function_references/utils.md",
+                    "function_references/analysis.md",
                     ],
                 "References" => "references.md"
                 ],

### 2021-07-04 src/deconvolution.jl
added anscombe and tests and changed initial scaling from maximum to mean

@@ -90,7 +90,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
 
 
     # we divide by the maximum to normalize
-    rescaling = maximum(measured) 
+    rescaling = mean(measured) # was: maximum(measured) 
     measured = measured ./ rescaling
     # create rec0 which will be the initial guess for the reconstruction
     rec0 = similar(measured, (size_padded)...)

### 2021-07-04 src/lossfunctions.jl

@@ -1,7 +1,8 @@
 export Poisson, poisson_aux
 export Gauss, gauss_aux
 export ScaledGauss, scaled_gauss_aux
-
+export Anscombe, anscombe_aux
+using Tullio
 
 """
     poisson_aux(μ, meas, storage=copy(μ))
@@ -89,19 +90,19 @@ Calculates the scaled Gauss loss for `μ` and `meas`.
 `μ` can be of larger size than `meas`. In that case
 we extract a centered region from `μ` of the same size as `meas`.
 """
-function scaled_gauss_aux(μ, meas, storage=copy(μ))
-    μ[μ .<= 1f-8] .= 1f-8
-    storage .= 1/2f0 .* log.(μ) .+ (meas .- μ).^2 ./ (2 .* μ)
+function scaled_gauss_aux(μ, meas, storage=copy(μ); read_var=1)
+    # μ[μ .<= 1f-8] .= 1f-8
+    storage .= log.(μ .+read_var) .+ (meas .- μ).^2 ./ (μ.+read_var)
     return sum(storage)
 end
 
  # define custom gradient for speed-up
-function ChainRulesCore.rrule(::typeof(scaled_gauss_aux), μ, meas, storage=copy(μ))
-    Y = scaled_gauss_aux(μ, meas) 
+function ChainRulesCore.rrule(::typeof(scaled_gauss_aux), μ, meas, storage=copy(μ); read_var=1)
+    Y = scaled_gauss_aux(μ, meas, storage, read_var= read_var) 
     function scaled_gauss_aux_pullback(xbar)
-        ∇ = (μ + μ.^2 - meas.^2)./(2 .* μ.^2)
-        ∇[μ .<= 1f-8] .= 0 
-        return zero(eltype(μ)), ∇, zero(eltype(μ)) 
+        ∇ = (μ.^2 .- meas.^2 .+ μ .+ read_var.*(1 .- 2 .* (meas .- µ)))./((μ.+read_var).^2)
+        # ∇[μ .<= 1f-8] .= 0 
+        return zero(eltype(μ)), ∇, zero(eltype(μ)), zero(eltype(μ)), zero(eltype(μ)) 
     end
     return Y, scaled_gauss_aux_pullback
 end
@@ -113,6 +114,63 @@ end
 Returns a function to calculate scaled Gauss loss.
 Check the help of `scaled_gauss_aux`.
 """
-function ScaledGauss()
-    return scaled_gauss_aux
+function ScaledGauss(read_var=1)
[…]

### 2021-07-04 test/lossfunctions.jl

@@ -28,12 +28,23 @@ end
     N = 6
     img = abs.(randn((N, N)))
     
-    scaled_gauss = ScaledGauss()
+    scaled_gauss = ScaledGauss(0)
     
-    @test 1.7047189562170502 ≈ scaled_gauss([5.], [2.]) 
-    @test 1.7047189562170502 ≈ scaled_gauss_aux([5.], [2.]) 
+    @test 3.4094379124341003 ≈ scaled_gauss([5.], [2.]) 
+    @test 3.4094379124341003 ≈ scaled_gauss_aux([5.], [2.], read_var=0) 
     
-    @test all( -1 .≈ Zygote.gradient(scaled_gauss_aux, [1.], [2.])[1])
+    @test all( -0.75 .≈ Zygote.gradient(scaled_gauss_aux, [1.], [2.])[1])
+end
 
+@testset "Anscombe Loss" begin
+    N = 6
+    img = abs.(randn((N, N)))
+
+    anscombe = Anscombe(1.0)
+    @test 0 ≈ anscombe(img, img)
+
+    @test 0 ≈ anscombe_aux(img, img,b=1,sqrt_meas_b=sqrt.(img.+1))
+    
+    @test all(0 .≈ Zygote.gradient((im1,im2) -> anscombe_aux(im1,im2,b=1, sqrt_meas_b=sqrt.(img.+1)), img, img)[1])
 
 end

### 2021-07-04 src/analysis_tools.jl
add reference

@@ -5,6 +5,8 @@ Calculates the relative energy regain between the `ground_truth`
 and the reconstruction.
 Assumes that both arrays are 2 dimensional
 
+# Reference
+* [Rainer Heintzmann, \"Estimating missing information by maximum likelihood deconvolution\"](https://www.sciencedirect.com/science/article/abs/pii/S0968432806001272)
 """
 function relative_energy_regain(ground_truth, rec)
     # go to fourier space

### 2021-07-04 paper/paper.tex
Update paper tex

@@
 but since the FFT (CuFFT in the CUDA library \cite{CUDA}) can be also executed in parallel fashion, both approaches profit from parallelization.
-If the kernel is separable over the dimensions (like a Gaussian kernel) the complexity changes to $\mathcal O(N \cdot K \cdot L +  N \cdot K \cdot L)$ however most optical PSF are not separable and therefore this is not general applicable.
+If the kernel is separable over the dimensions (like a Gaussian kernel) the complexity changes to $\mathcal O(N \cdot M \cdot L +  N \cdot M \cdot K)$ however most optical PSFs are not separable and therefore this is not generally applicable.
 

### 2021-07-04 dev/search_index.js
build based on a83e35b

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas, storage=copy(μ))\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas, storage=copy(μ))\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_gauss
[…]

### 2021-07-04 src/lossfunctions.jl
Add scaled gaussian and anscombe norm

@@ -1,7 +1,7 @@
 export Poisson, poisson_aux
 export Gauss, gauss_aux
 export ScaledGauss, scaled_gauss_aux
-
+export Anscombe, anscombe_aux
 
 """
     poisson_aux(μ, meas, storage=copy(μ))
@@ -63,7 +63,7 @@ end
 function ChainRulesCore.rrule(::typeof(gauss_aux), μ, meas, storage=copy(μ))
     Y = gauss_aux(μ, meas) 
     function gauss_aux_pullback(xbar)
-        return zero(eltype(μ)), 2 .* (μ - meas), zero(eltype(μ)), zero(eltype(μ)) 
+        return zero(eltype(μ)), 2 .* xbar .* (μ - meas), zero(eltype(μ)), zero(eltype(μ)) 
     end
     return Y, gauss_aux_pullback
 end
@@ -84,24 +84,25 @@ end
 
 
 """
-    scaled_gauss_aux(μ, meas)
+    scaled_gauss_aux(μ, meas, storage=copy(μ); read_var=0)
 Calculates the scaled Gauss loss for `μ` and `meas`.
+`read_var=0` is the readout noise variance of the sensor.
 `μ` can be of larger size than `meas`. In that case
 we extract a centered region from `μ` of the same size as `meas`.
 """
-function scaled_gauss_aux(μ, meas, storage=copy(μ))
+function scaled_gauss_aux(μ, meas, storage=copy(μ); read_var=0)
     μ[μ .<= 1f-8] .= 1f-8
-    storage .= 1/2f0 .* log.(μ) .+ (meas .- μ).^2 ./ (2 .* μ)
+    storage .= log.(μ .+ read_var) .+ (meas .- μ).^2 ./ ((μ .+ read_var))
     return sum(storage)
 end
 
  # define custom gradient for speed-up
-function ChainRulesCore.rrule(::typeof(scaled_gauss_aux), μ, meas, storage=copy(μ))
+function ChainRulesCore.rrule(::typeof(scaled_gauss_aux), μ, meas, storage=copy(μ); read_var=0)
     Y = scaled_gauss_aux(μ, meas) 
     function scaled_gauss_aux_pullback(xbar)
-        ∇ = (μ + μ.^2 - meas.^2)./(2 .* μ.^2)
+        ∇ = xbar .* (μ.^2 .- meas.^2 .+ μ .+ read_var.*(1 .- 2 .* (meas .- µ)))./((μ .+read_var).^2)
         ∇[μ .<= 1f-8] .= 0 
[…]

### 2021-07-04 test/lossfunctions.jl

@@ -28,12 +28,23 @@ end
     N = 6
     img = abs.(randn((N, N)))
     
-    scaled_gauss = ScaledGauss()
-    
-    @test 1.7047189562170502 ≈ scaled_gauss([5.], [2.]) 
-    @test 1.7047189562170502 ≈ scaled_gauss_aux([5.], [2.]) 
-    
-    @test all( -1 .≈ Zygote.gradient(scaled_gauss_aux, [1.], [2.])[1])
+    scaled_gauss = ScaledGauss(0)
 
+    @test 3.4094379124341003 ≈ scaled_gauss([5.], [2.])
+    @test 3.4094379124341003 ≈ scaled_gauss_aux([5.], [2.], read_var=0)
+
+    @test all( -0.75 .≈ Zygote.gradient((a, b) -> scaled_gauss_aux(a, b, read_var=1), [1.], [2.])[1])
+end
+
+@testset "Anscombe Loss" begin
+    N = 6
+    img = abs.(randn((N, N)))
+
+    anscombe = Anscombe(1.0)
+    @test 0 ≈ anscombe(img, img)
+
+    @test 0 ≈ anscombe_aux(img, img,b=1)
+
+    @test all(0 .≈ Zygote.gradient(im1 -> anscombe_aux(im1,img, b=1), img)[1])
 
 end

### 2021-07-04 dev/search_index.js
build based on 03d5a6e

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas, storage=copy(μ))\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas, storage=copy(μ))\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_gauss
[…]

### 2021-07-04 test/regularizer.jl
Update runtests

@@ -14,6 +14,14 @@ end
     x = [1,2,3,1,3,1,12.0,2,2,3,2.0]
     reg = Tikhonov(num_dims=1, sum_dims=[1], weights=[1])
     @test 756 ≈ reg(x)
+
+    reg = Tikhonov(num_dims=1, mode="spatial_grad_square")
+    @test 188 ≈ reg(x)
+    
+    reg = Tikhonov(num_dims=1, mode="identity")
+    @test 190 ≈ reg(x)
+
+
 end
 
 @testset "Good's roughness" begin
@@ -34,8 +42,15 @@ end
     x = [1,2,3,1,3,1,12.0,2,2,3,2.0]
     reg = TV(num_dims=1, sum_dims=[1], weights=[1])
     @test 31.00010002845424 ≈ reg(x)
-    
+        
+    @test TV_cuda(num_dims=2)(x) ≈ reg(x)
+    @test TV_cuda(num_dims=3)(x) ≈ reg(x)
+
 
     x = generate_TV(4, [1,2], [5, 7], 1, -1, debug=true)
     @test x == Any[:(res = sqrt(5 * abs2(arr[i1 + 1, i2, i3, i4] - arr[i1 + -1, i2, i3, i4]) + 7 * abs2(arr[i1, i2 + 1, i3, i4] - arr[i1, i2 + -1, i3, i4]) + 1.0f-8))]
+
+
+    
+
 end

### 2021-07-04 test/runtests.jl

@@ -7,7 +7,9 @@ using TestImages, Noise
  # fix seed for reproducibility
 Random.seed!(42)
 
+
 @testset "Utils" begin
+    @test gpu_or_cpu(randn((2,2))) == Array
     include("utils.jl")
 end
 
@@ -23,3 +25,5 @@ include("lossfunctions.jl")
 include("regularizer.jl")
 
 include("main.jl")
+
+

### 2021-07-05 src/analysis_tools.jl
Change normalized cross correlation to mean subtract

@@ -84,6 +84,6 @@ function normalized_cross_correlation(ground_truth, measured)
     ground_truth = fl(ground_truth)
     measured = fl(measured)
 
-    ncc = crosscor(ground_truth, measured, [0], demean=false)[begin]
+    ncc = crosscor(ground_truth, measured, [0], demean=true)[begin]
     return ncc
 end

### 2021-07-05 src/lossfunctions.jl
Fix anscombe

@@ -163,5 +163,5 @@ Check the help of `anscombe_aux`.
 """
 
 function Anscombe(b=1)
-    (μ, meas) -> anscombe_aux(μ, meas, b=b)
+    (μ, meas, storage=copy(μ)) -> anscombe_aux(μ, meas, storage, b=b)
 end

### 2021-07-05 src/deconvolution.jl
Change to mean instead of maximum

@@ -91,7 +91,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
 
 
     # we divide by the maximum to normalize
-    rescaling = maximum(measured) 
+    rescaling = mean(measured) 
     measured = measured ./ rescaling
     # create rec0 which will be the initial guess for the reconstruction
     rec0 = similar(measured, (size_padded)...)

### 2021-07-05 src/generic_invert.jl
Fix debug function with mapping function

@@ -39,18 +39,20 @@ function invert(measured, rec0, forward;
     end
 
 
-    debug_f = let
-        if isnothing(debug_f)
-            identity
-        else
-            debug_f
-        end
-    end
     
     # Get the mapping functions to achieve constraints
     # like non negativity
     mf, m_invf = get_mapping(mapping)
     regularizer = get_regularizer(regularizer, eltype(rec0))
+
+
+    debug_f_n(x) = let
+        if isnothing(debug_f)
+            identity(x)
+        else
+            debug_f(mf(x))
+        end
+    end
     
     storage_μ = deepcopy(measured)
     function total_loss(rec)
@@ -82,7 +84,7 @@ function invert(measured, rec0, forward;
         # Zygote calculates both derivative and loss, therefore do everything in one step
         if G != nothing
             # apply debug function
-            debug_f(rec)
+            debug_f_n(rec)
 
             y, back = Base.invokelatest(Zygote._pullback, total_loss, rec)
             # calculate gradient

### 2021-07-05 paper/paper.tex
Update paper

@@
 However, those implementations are usually restricted to cases where experimental datasets are available for the characterization and training.
-\verb|DeconvOptim.jl| offers several deconvolution algorithms like the iterative Richardson-Lucy algorithms but also
-a much more flexible method which is based on a loss function being minimized by a gradient descent.
+\verb|DeconvOptim.jl| is a toolbox written in Julia \cite{bezanson2017julia} which offers several deconvolution algorithms like the iterative Richardson-Lucy algorithms but also
+a much more flexible methods which are based on a loss function being minimized by a gradient descent.
 Also this toolbox is not restricted in dimensionality and therefore can be applied to deconvolution problems in many different fields.
@@
         \begin{figure}[h]
-            \begin{subfigure}[b]{.166\textwidth}
+            \begin{subfigure}[b]{.25\textwidth}
                 \centering
                 \includegraphics[width=\textwidth]{figures/resolution_test_chart_blurry.png}
-                \caption{Measured}
+                \caption{Measured with Poisson noise}
                 \label{fig:fabioa}
             \end{subfigure}%
-            \begin{subfigure}[b]{.166\textwidth}
+            \hfill
+            \begin{subfigure}[b]{.25\textwidth}
                 \centering
-                \includegraphics[width=\textwidth]{figures/resolution_test_chart_no_reg_iter_30.png}
-                \caption{Without regularizer}
+                \includegraphics[width=\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
+                \caption{Without regularizer $N=50$}
                 \label{fig:fabiob}
             \end{subfigure}%
-            \begin{subfigure}[b]{.166\textwidth}
+            \hfill
+            \begin{subfigure}[b]{.25\textwidth}
                 \centering
-                \includegraphics[width=\textwidth]{figures/resolution_test_chart_regularizer_005_iter_30.png}
-                \caption{With regularizer}
+                \includegraphics[width=\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
+                \caption{Without regularizer $N=10$}
                 \label{fig:fabioc}
             \end{subfigure}%            
+            \hfill
+            \begin{subfigure}[b]{.25\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
+                \caption{With regularizer $N=21$.}
+                \label{fig:fabiod}
+            \end{subfigure}%            
             \caption{a) has been convolved with a PSF and affected by Poisson shot noise (100 photons expected for the brightest pixel). 
-                        Deconvolved b) for 50 iterations without an regularizer c) with Good's roughness regularizer and 
-                            converged after 20 iterations with $\lambda=0.03$.}
+                        Deconvolved b) for 50 iterations without a regularizer c) for 10 iterations without a regularizer d) with Good's roughness regularizer and 
+                            converged after 21 iterations with $\lambda=0.08$.}
             \label{fig:image}
@@
         are getting closer in the center which is equivalent to higher spatial frequencies.
-        \autoref{fig:fabiob} shows the result after 50 iterations of the deconvolution. 
+        \autoref{fig:fabioc} shows the result after 50 iterations of the deconvolution. 
         We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.
         Additionally, we notice that the core in the Siemens star is smaller meaning better spatial resolution. 
-        \autoref{fig:fabioc} shows the results after 20 iterations of the deconvolution but regularized with a Good's roughness regularizer.
+        \autoref{fig:fabioc} shows the results after 10 iterations of the deconvolution without a regularizer.
+        We have chosen 10 iterations since the normal cross correlation (NCC) shows the maximum at 10 iterations.
+        Optimizing for more iterations seems to introduce more and more artifacts to the image as it can be seen visually as well.
+        \autoref{fig:fabiod} shows the results after 21 iterations of the deconvolution but regularized with a Good's roughness regularizer.
         The total image quality is much better since the regularizer dampens the artifacts but also results in lower
@@
         In \autoref{fig:rel_energy_regain} we show the relative energy regain $G_\textrm{R}$ \cite{rel_energy_regain} (REG).
-        The meaning of the relative energy regain is how well certain frequencies are reconstructed in comparison
+        The meaning of the REG is how well certain frequencies are reconstructed in comparison
         to the ground truth. $G_\textrm{R} = 1$ is a perfect reconstruction, $G_\textrm{R} = 0$ indicates that 
@@
                 \includegraphics[width =\textwidth]{figures/test_chart_relative_energy_regain.pdf}
-                \caption{Relative energy regain $G_\textrm{R}$ over different frequencies.}
+                \caption{REG $G_\textrm{R}$ over different frequencies.}
                 \label{fig:rel_energy_regain}
@@
                 \centering
-                \includegraphics[width =0.97 \textwidth]{figures/test_chart_ncc.pdf}
-                \caption{Normalized correlation coefficient (NCC) over the number of iterations.}
+                \includegraphics[width =1 \textwidth]{figures/test_chart_ncc.pdf}
+                \caption{NCC over the number of iterations.}
                 \label{fig:ncc}
             \end{subfigure}
-            \caption{NCC and REG are quantitative measurements to judge the quality of a deconvolution result.}
+            \caption{NCC and REG are quantitative measurements to judge the quality of a deconvolution result. 
+                In a) we show the REG for the hand-optimized non-regularized version with 10 iterations and the (converged) regularized versions with $\lambda=0.08$ and $\lambda=0.5$.}
         \end{figure}
@@
         Beyond $f_\textrm{max}$ Poisson noise introduces fake frequencies.
-        The green curve shows the relative energy regain of the deconvolution without a regularizer. For certain regions below  $f_\textrm{max}$
+        The green curve shows the REG of the deconvolution without a regularizer. For certain regions below  $f_\textrm{max}$
         the deconvolution enhances the contrast. However, around and beyond $f_\textrm{max}$ several artifacts are introduced.
-        The regularized blue curve performs much better and only certain frequencies show a relative energy regain below zero.
+        The regularized blue curve performs better and only certain frequencies show a REG below zero.
         To some extent the regularized version can also recover information above $f_\textrm{max}$ which are not supported by the PSF.
-        \autoref{fig:ncc} shows the normalized correlation coefficient over the number of iterations.
+        \autoref{fig:ncc} shows the NCC over the number of iterations.
         Especially the deconvolution without an regularizer suffers from poor performance after a high number of iterations.
-        Either one has to stop early after a hand optimized iteration number or use a regularizer.
+        Either one has to stop early after a hand optimized iteration number (here 10) or use a regularizer.
+        The regularized version seems to be robust against a higher number of iterations and even converges after 21.
+        In conclusion we can say that both the regularized and the non-regularized versions produce good results. 
+        In the non-regularized one has to hand-optimize the number of iterations whereas in the regularized one has to optimize $\lambda$.
+        Advantage of the non-regularized version is, that it performs more than twice as fast but as it can be seen in \autoref{fig:fabioc} 
+        it shows slightly more artifacts in homogenous regions.
 

### 2021-07-09 paper/paper.tex
Update paper

@@
 be expressed mathematically as a convolution of a system's response function with a signal. 
-In this paper, we present \verb|DeconvOptim.jl|, a flexible toolbox written in Julia to deconvolve multi-dimensional signals which have been
+In this paper, we present \verb|DeconvOptim.jl|, a flexible toolbox written in Julia to deconvolve one or multiple multi-dimensional signals which have been
 degraded by a multi-dimensional signal response function. 
@@
 
+\todo{multi view deconvolution}
+
 \section{Introduction}
-Deconvolution has been a long addressed problem especially in astronomical imaging, digital signal processing or microscopical imaging.
-The assumption is that images are degraded by some kind of blur which can be described as a convolution between a kernel $h$ and the image $S$:
+Deconvolution has been a long addressed problem especially in astronomical imaging, digital signal processing or microscopy imaging.
+The assumption is that images are degraded by some kind of blur which can be described as a convolution of a kernel $h$ with the image $S$:
 \begin{equation}
@@
 \end{equation}
-$h$ is often called the point spread function (PSF) since it characterizes how the systems maps a point in the object to a blurred area
+where $*$ denotes a convolution operation.
+$h$ is often called the point spread function (PSF) since it characterizes how the systems maps a point in the object to a blurred spot 
 in the image.
@@
     Y_{\text{Poisson}}(\mathbf r) &= \text{Poisson}[(h * S)(\mathbf r)]\\
-    Y_{\text{Gauss}}(\mathbf r) &= (h * S)(\mathbf r) + \text{Gauss}_{\mu, \sigma}(\mathbf r)
+    Y_{\text{Gauss}}(\mathbf r) &= (h * S)(\mathbf r) + \text{Gauss}_{\sigma}(\mathbf r)
 \end{align}
@@
 Another common method is the non-iterative Wiener filter \cite{wiener2013extrapolation} because of its predictable runtime.
-The Wiener filter assumes additive noise which is often not true, especially in low light conditions as in microscopy or astronomy. 
-Recently machine learning based methods have become more and more favoured in deconvolution methods because
+The Wiener filter assumes additive noise which is often not a good approximation, especially in low light conditions as in microscopy or astronomy. 
+Recently machine learning based methods have become more and more favoured in deconvolution because
 of the possibility to add learned properties of similar images to the algorithm \cite{Kruse_2017_ICCV}.
@@
 \verb|DeconvOptim.jl| is a toolbox written in Julia \cite{bezanson2017julia} which offers several deconvolution algorithms like the iterative Richardson-Lucy algorithms but also
-a much more flexible methods which are based on a loss function being minimized by a gradient descent.
+much more flexible methods which are based on minimizing a 
+noise-dependent loss function with the help of modern gradient-descent minimization routines. 
 Also this toolbox is not restricted in dimensionality and therefore can be applied to deconvolution problems in many different fields.
@@
 To obtain efficient deconvolution algorithms we also need a efficient way to calculate the convolution operations.
-In these times, convolution operations of spatially small kernels $h$ can be calculated on GPUs very efficiently.
+Today, convolution operations of spatially small kernels $h$ can be calculated on GPUs very efficiently in real space.
 However, often the blurring kernel $h$ is not spatially small and might be also multi-dimensional. In that case, FFT based convolutions
@@
 \subsection{FFT Based Convolution}
-    The basis for fast convolution operations lies in the convolution theorem. It states that
+    The basis for fast convolution calculation via Fourier transforms lies in the convolution theorem. It states that
     \begin{equation}
@@
         The time complexity to calculate \autoref{eq:fftconv} is $\mathcal{O}(N \cdot \log N)$ for a one dimensional discretized dataset with $N$ samples.
-        For a 2D dataset with size $N \times M$ it is $\mathcal{O}(N \cdot M \log(N + M))$ and accordingly for higher dimensions.
+        For a 2D dataset with size $N \times M$ it is $\mathcal{O}(N \cdot M \log(N \cdot M))$ and accordingly for higher dimensions.
 
@@
 \subsection{Wrap-Around Artifacts in FFT based Convolutions}
-    One drawback of a FFT based convolution are wrap-around artifacts. The reason is, that the FFT operation calculates the discrete
+    One drawback of a FFT based convolution are wrap-around artifacts (see arrow in \autoref{fig:withoutpad}). The reason is, that the FFT operation calculates the discrete
     Fourier transform (DFT) which inherently assumes periodic data. If one applies a FFT on a finite data set the assumption is that
@@
     and remove the padding afterwards. Such approaches still suffer from artifacts when boundary values do not fit
-    to the mean or to zero as it can be observed in \autoref{fig:withpad} at the top.
+    to the mean or to zero as it can be observed in \autoref{fig:withpad} where the arrow is pointing to.
     \begin{figure}[h]
@@
                 \draw[color=red] (-1.6, -1.6) -- (0.9, -0.9);
+                \draw[<-, color=red, thick ](-0.85, 0) -- (-0.4, 0.6);
             \end{tikzpicture}
@@
                 \draw[color=red] (-1.6, -1.6) -- (0.9, -0.9);
+                \draw[<-, color=red, thick ](-0.8, -0.7) -- (-0.3, -0.3);
             \end{tikzpicture}
@@
         the bottom scattered into the bright sky.
-        Image b) was padded before blurring with 10 pixels on each side with value 0.7. The blur kernel was a Gaussian kernel
+        Image b) was padded before blurring with 10 pixels on each side with value 0.7 which results in bright regions around the image. The blur kernel was a Gaussian kernel
         with standard deviation $\sigma=\SI{3}{pixel}$.}
@@
     \end{figure}
-    To solve for the wrap-around artifacts in deconvolution we use a different approach which will be presented later. 
+    To solve for the wrap-around artifacts in deconvolution we use a different approach which will be presented in \autoref{sec:wrap}. 
 \subsection{Preferred Convolution}
 The current state of \verb|DeconvOptim.jl| uses the FFT approach to calculate the convolution.
-However, in principle one could add the possibility to change to spatially based convolutions.
+However, in principle one could add the possibility to choose spatially based convolutions.
 But since the runtime gets especially long in multi-dimensional signal deconvolution where FFT based methods
-are faster, we always use FFT based convolutions.
+are faster, we always use FFT based convolutions here.
 
@@
 At the beginning of the optimization we start with an initial guess $x(\mathbf r)$. 
-Via a mapping function we can impose some restrictions to the final solution (e.g. non-negativity, certain value intervals).
+Via a mapping function we can impose some restrictions to the final solution (e.g. non-negativity, value intervals).
 The forward model is then applied to the mapped reconstruction. We provide a default function where 
-the forward function is a convolution but we also allow to plug in a different forward model into the pipeline.
+the forward function is a convolution but we also allow to plug in a different forward model.
 This output of the forward function is compared
-with our noisy measurement under a certain loss function.
-Since deconvolution is an ill-posed problem we regularize the loss function with a regularizer.
+to our noisy measurement under a given loss function.
+Since deconvolution is an ill-posed problem, we regularize the loss function with a regularizer.
 Afterwards we calculate the gradient of the loss function with respect to the reconstruction $x(\mathbf r)$ via automatic differentation (AD).
-The values of the total loss and the gradient are then used by an optimizer (to minimize the total loss) to apply some kind of gradient descent optimization to get a proper reconstruction.\\
+The values of the total loss and the gradient are then used by an optimizer (to minimize the total loss) to apply a gradient descent optimization to get a proper reconstruction.\\
 
@@
 As default for the optimization we use the L-BFGS \cite{LBFGS} routine provided by \verb|Optim.jl| \cite{mogensen2018optim}.
-L-BFGS is suitable for optimization with many million parameters as it only stores a sparse representation of the inverse Hessian matrix
+L-BFGS is suitable for optimization with many million parameters as it only stores a sparse representation of the inverse Hessian matrix,
 which is built from a finite number of past function and gradient evaluations. 
-In comparison to the Richardson-Lucy algorithm results are often good after 10 to 30 iterations whereas Richardson-Lucy takes
+Results are often good after 10 to 30 iterations whereas Richardson-Lucy takes
 a few hundreds iterations. 
@@
 \subsection{Mapping Function}
-    Mapping functions are an easy way to constrain the resulting reconstruction to certain values.
+    Mapping functions are an easy way to constrain the resulting reconstruction to predefined ranges.
     For example, if the optimizer optimizes the variables $\text{rec}$ which are then squared, we know that
-    $\text{rec}^2$ is definitely non-negative. Instead of directly using $\text{rec}$ we compare
-    $\text{rec}^2$ with the measurement $Y$. This mapping function does not change the outcome as long
+    $\text{rec}^2$ is definitely non-negative. Instead of directly using $\text{fwd}(\text{rec})$ we compare
+    $\text{fwd}(\text{rec}^2)$ with the measurement $Y$. This mapping function does not change the outcome as long
     as it is an surjective function for the desired number space (e.g. a parabola is non-negative and covers all positive values) 
@@
 \subsection{Wrap-around Artifacts Suppression}
+    \label{sec:wrap}
     To prevent that wrap-around artifacts occur during deconvolution we can instead
@@
     Through the AD and the convolution operations we still optimize for the whole area (including the red one).
-    With that padding we prevent that images on the boundary influence in circular manner the reconstruction.
+    With that padding we reduce that images on the boundary influence in circular manner on reconstruction in the grey area.
 
 \section{Loss Function}
-    Besides the forward model, the loss function is the most critical part in the optimization.
-    It has to take account for the noise created by the measurement process or device.
+    Apart from forward model, the loss function is the most critical part in the optimization.
+    It has to account for the noise created by the measurement process or device.
 
 \subsection{Poisson Data Term}
-    As already mentioned, Poisson shot noise is often the dominant source of noise hence we 
+    Poisson shot noise is often the dominant source of noise hence we 
     explain the details.
-    The key idea is to interpret the measurement as a stochastic process. Our aim is to find a deconvolved image which describes as accurate as possible the measured image.
+    The key is to interpret the measurement as a stochastic process. 
+    Our aim is to find a deconvolved image which predicts the measured image as accurately as 
+    possible.
     Mathematically the probability for a certain measurement $Y$ under Poisson noise is
@@
 where $Y$ is the measurement, $\mu$ is the expected measurement (ideal measurement without noise) and $\Gamma$ is the generalized factorial function.
-In the deconvolution process we get $Y$ as measured input and want to find the ideal specimen $S$ which results in a measurement $\mu(\mathbf r) = (S * \text{PSF})(\mathbf r))$.
-Since we want to obtain for the best reconstruction, we want to find a $\mu(\mathbf r)$ so that $p(Y(\mathbf r) | \mu(\mathbf r))$ gets as large as possible. Because that means
+In the deconvolution process we get $Y$ as measured input and want to find the ideal specimen $S$ which results in a measurement $\mu(\mathbf r) = (S * \text{PSF})(\mathbf r)$.
+Since we want to obtain the best reconstruction, we want 
+to find a $\mu(\mathbf r)$ so that $p(Y(\mathbf r) | \mu(\mathbf r))$ gets maximized.
+Because that means
 that we find the specimen which describes the measurement with the highest probability.
@@
 \begin{align}
-&\underset{S(\mathbf r)}{\arg \min} (- \log(p(Y(\mathbf r)|\mu(\mathbf r)))) =\\ &\underset{S(\mathbf r)}{\arg \min} \sum_r (\mu(\mathbf r) + \log(\Gamma(Y(\mathbf r) + 1)) - Y(\mathbf r) \log(\mu(\mathbf r))
+&\underset{S(\mathbf r)}{\arg \min} (- \log(p(Y(\mathbf r)|\mu(\mathbf r)))) =\\ &\underset{S(\mathbf r)}{\arg \min} \sum_r \mu(\mathbf r) + \log(\Gamma(Y(\mathbf r) + 1)) - Y(\mathbf r) \log(\mu(\mathbf r))
 \end{align}
@@
 
-since the second term only depends on $Y(\mathbf r)$ but not on $\mu(\mathbf r)$.
+since the second term only depends on the constant $Y(\mathbf r)$ but not on $\mu(\mathbf r)$.
 The gradient of $L$ with respect to $\mu(\mathbf r)$ is simply
@@
 However, the loss is not defined for $\mu \leq 0$.
-In our source code we set all intensity values below a certain threshold $\epsilon$ to $\epsilon$ itself.
+In our source code we set all intensity values below a predefined threshold $\epsilon$ to $\epsilon$ itself.
 This prevents the evaluation of the logarithm at undefined values.
@@
                 \includegraphics[width=\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
-                \caption{With regularizer $N=21$.}
+                \caption{With regularizer $N=24$.}
                 \label{fig:fabiod}
@@
                         Deconvolved b) for 50 iterations without a regularizer c) for 10 iterations without a regularizer d) with Good's roughness regularizer and 
-                            converged after 21 iterations with $\lambda=0.08$.}
+                            converged after 24 iterations with $\lambda=0.03$.}
             \label{fig:image}
@@
         This test chart is suited to judge the resolution of a reconstruction since the pieces of the Siemens star
-        are getting closer in the center which is equivalent to higher spatial frequencies.
+        have decreasing spacing towards its middle which is equivalent to higher spatial frequencies.
         \autoref{fig:fabioc} shows the result after 50 iterations of the deconvolution. 
         We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.
-        Additionally, we notice that the core in the Siemens star is smaller meaning better spatial resolution. 
+        Additionally, we notice that the core in the Siemens star is denser is denser 
+        requiring higher spatial resolution to resolve. 
         \autoref{fig:fabioc} shows the results after 10 iterations of the deconvolution without a regularizer.
@@
         Optimizing for more iterations seems to introduce more and more artifacts to the image as it can be seen visually as well.
-        \autoref{fig:fabiod} shows the results after 21 iterations of the deconvolution but regularized with a Good's roughness regularizer.
+        \autoref{fig:fabiod} shows the results after 24 iterations of the deconvolution but regularized with a Good's roughness regularizer.
         The total image quality is much better since the regularizer dampens the artifacts but also results in lower
-        resolution. With the regularizer weight $\lambda$ one can adjust the strength.
+        resolution. With the regularizer weight $\lambda$ one can adjust the regularization strength.
         In \autoref{fig:rel_energy_regain} we show the relative energy regain $G_\textrm{R}$ \cite{rel_energy_regain} (REG).
@@
         to the ground truth. $G_\textrm{R} = 1$ is a perfect reconstruction, $G_\textrm{R} = 0$ indicates that 
-        this frequency could not be recovered at all, $G_\textrm{R} < 0$ means that the reconstruction introduces fake frequencies
-        which do not fit to the ground truth at all.
+        this frequency could not be recovered at all, $G_\textrm{R} < 0$ means that the reconstruction introduces 
+        wrong information at this frequencies
+        which are further from the ground truth then not reconstructing these frequencies. 
         \begin{figure}[h]
@@
             \caption{NCC and REG are quantitative measurements to judge the quality of a deconvolution result. 
-                In a) we show the REG for the hand-optimized non-regularized version with 10 iterations and the (converged) regularized versions with $\lambda=0.08$ and $\lambda=0.5$.}
+                In a) we show the REG for the hand-optimized non-regularized version with 10 iterations and the (converged) regularized versions with $\lambda=0.03$ and $\lambda=0.5$.}
         \end{figure}
@@
         Beyond $f_\textrm{max}$ Poisson noise introduces fake frequencies.
-        The green curve shows the REG of the deconvolution without a regularizer. For certain regions below  $f_\textrm{max}$
+        The green curve shows the REG of the deconvolution without a regularizer. 
+        For regions below  $f_\textrm{max}$
         the deconvolution enhances the contrast. However, around and beyond $f_\textrm{max}$ several artifacts are introduced.
-        The regularized blue curve performs better and only certain frequencies show a REG below zero.
+        The regularized blue curve performs better and only some frequencies show a REG below zero.
         To some extent the regularized version can also recover information above $f_\textrm{max}$ which are not supported by the PSF.
         \autoref{fig:ncc} shows the NCC over the number of iterations.
-        Especially the deconvolution without an regularizer suffers from poor performance after a high number of iterations.
+        Especially the deconvolution without a regularizer suffers from poor performance after a high number of iterations.
         Either one has to stop early after a hand optimized iteration number (here 10) or use a regularizer.
-        The regularized version seems to be robust against a higher number of iterations and even converges after 21.
+        The regularized version seems to be robust against a higher number of iterations and even converges after 24.
         In conclusion we can say that both the regularized and the non-regularized versions produce good results. 
@@
     \subsection{Multi-Dimensional Microscopy Data}
-        To show the full ability, we deconvolve a four dimensional dataset where the measured volume consists of a 3D datasets
-        with three different color channels which is shown in \autoref{fig:result_3d}.
-        The PSF is only three dimensional.
+        To more completely demonstrate the features available in \verb|DeconvOptim.jl|,
+        we deconvolve a four dimensional dataset where the measured volume consists of a 3D datasets
+        with three different color channels, shown in \autoref{fig:result_3d}.
+        Here we assumed a common single 3D PSF for all color channels.
         Julia's broadcast mechanism handles that the PSF is only three dimensional and therefore
@@
             In \autoref{tab:reg} we can see the runtimes for different TV regularizer implementations. As we can see, \verb|Tullio.jl| outperforms a plain 
-            Julia implementation by more than order of magnitude. Partially, that is caused by the reason that \verb|Tullio.jl| can make 
+            Julia implementation by more than order of magnitude. Partially, that is caused by \verb|Tullio.jl|
+            being able to 
             use of all threads whereas Julia's built in broadcast mechanism is not multi threaded.
@@
                 \hline
-                    & Jax & $\nabla$ JAX && \\
+                    & JAX & $\nabla$ JAX && \\
                 \hline
@@
                 \end{tabular}
-                \caption{Runtimes of the Total Variation regularizer for different Julia versions and Jax. 
+                \caption{Runtimes of a single Total Variation regularizer calculation for different Julia versions and JAX. 
                     We used a 3 dimensional Float32 array with size $300 \times 300 \times 300$.  }
@@
     \subsection{Full Deconvolution}
+        In \autoref{tab:deconv} we show the deconvolution time for a 3D dataset with size \todo{size footnote} 
+        The basic settings of the different algorithms and packages are noted in \autoref{tab:deconvprop}.
         The aim of this comparison is not to compare the quality of the results but the computing time to achieve similar reconstructions. 
@@
         not exceed those results significantly in terms of quality.\\
-        In \autoref{tab:deconv} we show the computing time for different algorithms and packages and in \autoref{tab:deconvprop} the basic settings
-        in each package.
-        One should keep in mind that such performance comparison are usually biased since we are not
-        familiar with all options which should be choosen to achieve best performance.
+        One should keep in mind that such performance comparisons are usually biased since we are not
+        familiar with all options which should be chosen to achieve best performance.
         The comparison should give a rough overview which runtime is expected for each toolbox.\\
@@
 
-        For the results of \verb|GenericDeconv| (written in Matlab by Rainer Heintzmann) we used a Poisson loss function with a L-BFGS minimizer and a quadratic non-negativity constraint.
+        For the results of \verb|GenericDeconv| (written in Matlab by Rainer Heintzmann) we used a Poisson loss function with a L-BFGS minimizer 
+        and a quadratic non-negativity constraint.
         When the TV regularizer was added the weight was $\lambda = 0.002$.
@@
         \verb|DeconvolutionLab2| offers a wide variety of different algorithms which however only run on a CPU. 
-To put the numbers into context, even the non-iterative Tikhonov Regularization Inverse Filter (TRIF/TR) had a runtime of \SI{4}{\second}.
-In the table we show the results of an
+        To put the numbers into context, even the non-iterative Tikhonov Regularization Inverse Filter (TRIF/TR) had a 
+        runtime of \SI{4}{\second}. In the table we show the results of an 
         iterative Richardson-Lucy deconvolution. As number of iterations we set 80 and as regularizer weight $\lambda=0.002$.\\
@@
         it is notably slower in comparison to our implementation.
-        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its performance is poor in comparison to all
-        other packages.
+        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is comparably poor.
         \begin{figure}[h]

### 2021-07-10 src/deconvolution.jl
added some more positivity contraint functions and a mechanism to adapt to other optimizers, specifically OptimNextGen.jl

@@ -59,7 +59,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
         optim_options=nothing,
         optim_optimizer=LBFGS(linesearch=BackTracking()),
         debug_f=nothing,
-        ) where {T, N}
+        use_optim=OptimOptim) where {T, N}
 
 
     # rec0 will be an array storing the final reconstruction
@@ -152,7 +152,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
                           optim_options=optim_options,
                           mapping=mapping,
                           loss=loss,
-                          debug_f=debug_f)
+                          debug_f=debug_f, use_optim=use_optim)
 
     res_out .*= rescaling
     # since we do some padding we need to extract the center part

### 2021-07-10 src/generic_invert.jl

@@ -1,4 +1,9 @@
-export invert 
+export invert, OptimInterface, OptimOptim, OptimNextGen
+using Infiltrator
+
+abstract type OptimInterface end  # To accomodate multiple optimizers which are incompatible
+struct OptimOptim <: OptimInterface end  # 
+struct OptimNextGen <: OptimInterface end  # 
 
 """
     invert(measured, rec0, forward; <keyword arguments>)
@@ -31,14 +36,13 @@ function invert(measured, rec0, forward;
                 mapping=Non_negative(),
                 loss=Poisson(),
                 real_gradient=true,
-                debug_f=nothing)
+                debug_f=nothing,
+                use_optim =OptimOptim)
 
     # if not special options are given, just restrict iterations
-    if optim_options == nothing
+    if isa(use_optim, OptimOptim) && optim_options == nothing
         optim_options = Optim.Options(iterations=iterations)
     end
-
-
     
     # Get the mapping functions to achieve constraints
     # like non negativity
@@ -98,11 +102,25 @@ function invert(measured, rec0, forward;
         end
     end
 
-    optim_options = Optim.Options(iterations=iterations)
-    
-    # do the optimization with LBGFS
-    res = Optim.optimize(Optim.only_fg!(fg!), rec0, optim_optimizer, optim_options)
-    res_out = mf(Optim.minimizer(res))
+    if isa(use_optim, Type{OptimOptim}) 
+        optim_options = Optim.Options(iterations=iterations)
+        
+        # do the optimization with LBGFS
+        res = Optim.optimize(Optim.only_fg!(fg!), rec0, optim_optimizer, optim_options)
+        res_out = mf(Optim.minimizer(res))
+    elseif isa(use_optim, Type{OptimNextGen})
+        res = copy(rec0)
+            
+        # @infiltrate
+        if isnothing(optim_options)
+            optim_optimizer((x,g) -> fg!(true, g, x), res; maxiter=iterations)
+        else
+            optim_optimizer((x,g) -> fg!(true, g, x), res; maxiter=iterations, optim_options...)
+        end
+        res_out = mf(res)
+    else
+        error("Unknown optimizer interface $(typeof(use_optim))")
+    end
 
 
     return res_out, res

### 2021-07-10 src/mappings.jl

@@ -1,5 +1,8 @@
 export Non_negative
 export Map_0_1
+export Piecewise_positive
+export Pow4_positive
+export Abs_positive
  
 
  # All these functions return a mapping function and 
@@ -69,3 +72,56 @@ end
 
 f01(x) = 1 .- exp.(.- x.^2)
 f01_inv(y) = sqrt.(.- log.(1 .- y))
+
+"""
+    Piecewise_positive()
+
+Returns a function and a inverse function inverse function
+to map numbers to larger than 0. 
+
+"""
+function Piecewise_positive()
+    return f02, f02_inv
+end
+
+f02(x) = ifelse.(x .> 0, one(eltype(x)) .+ x,one(eltype(x))./(one(eltype(x)).-x))
+f02_grad(x) = ifelse.(x .> 0, one(eltype(x)) , one(eltype(x))./abs2.(one(eltype(x)).-x))
+f02_inv(y) = ifelse.(y .> 1, y .- one(eltype(y)), one(eltype(y)) .- one(eltype(y))./y)
+
+function ChainRulesCore.rrule(::typeof(f02), x)
+    Y = f02(x)
+    function aux_pullback(barx)
+        return zero(eltype(Y)), barx .* f02_grad(x)
+    end
+    return Y, aux_pullback
+end
+
+
+"""
+    Pow4_positive()
+
+Returns a function and a inverse function inverse function
+to map numbers to larger than 0. 
+
+"""
+function Pow4_positive()
+    return f03, f03_inv
+end
+
+f03(x) = abs2.(abs2.(x))
+f03_inv(y) = sqrt.(sqrt.(y))
+
+
+"""
+    Abs_positive()
+
+Returns a function and a inverse function inverse function
+to map numbers to larger than 0. 
+
+"""
+function Abs_positive()
+    return f04, f04_inv
+end
+
+f04(x) = abs.(x)
+f04_inv(y) = abs.(y)

### 2021-07-10 test/main.jl

@@ -31,7 +31,11 @@
     #= @show deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1] =# 
     @test all(≈(res4, deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1], rtol=0.1))
 
-
+    # test NextGen optimizers
+    res5 = [0.49633      16.4936   0.00862045; 0.0139499    15.8587   2.31716; 0.000227487   9.263   19.5289]
+    #= @show deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1] =# 
+    @test all(≈(res5, deconvolution(img, psf, optim_optimizer=vmlmb!, optim_options=(mem=20, lower=0, lnsrch=OptimPackNextGen.LineSearches.MoreThuenteLineSearch()),
+    regularizer=nothing, padding=0.1, mapping=nothing, use_optim=OptimNextGen)[1], rtol=0.1))
     
     # test broadcasting with image having more dimensions
     img = zeros((3, 3, 2))

### 2021-07-10 src/generic_invert.jl
added a comment for the OptimNextGen style.

@@ -108,10 +108,9 @@ function invert(measured, rec0, forward;
         # do the optimization with LBGFS
         res = Optim.optimize(Optim.only_fg!(fg!), rec0, optim_optimizer, optim_options)
         res_out = mf(Optim.minimizer(res))
-    elseif isa(use_optim, Type{OptimNextGen})
+    elseif isa(use_optim, Type{OptimNextGen}) # supports a different interface as for example used in OptimPackNextGen for the function 'vmlmb!'
         res = copy(rec0)
             
-        # @infiltrate
         if isnothing(optim_options)
             optim_optimizer((x,g) -> fg!(true, g, x), res; maxiter=iterations)
         else

### 2021-07-10 test/main.jl
removed the test case

@@ -31,11 +31,10 @@
     #= @show deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1] =# 
     @test all(≈(res4, deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1], rtol=0.1))
 
-    # test NextGen optimizers
-    res5 = [0.49633      16.4936   0.00862045; 0.0139499    15.8587   2.31716; 0.000227487   9.263   19.5289]
-    #= @show deconvolution(img, psf, regularizer=nothing, padding=0.1, mapping=nothing)[1] =# 
-    @test all(≈(res5, deconvolution(img, psf, optim_optimizer=vmlmb!, optim_options=(mem=20, lower=0, lnsrch=OptimPackNextGen.LineSearches.MoreThuenteLineSearch()),
-    regularizer=nothing, padding=0.1, mapping=nothing, use_optim=OptimNextGen)[1], rtol=0.1))
+    # test OptimPackNextGen optimizers  (which is currently not officially released yet)
+    # res5 = [0.49633      16.4936   0.00862045; 0.0139499    15.8587   2.31716; 0.000227487   9.263   19.5289]
+    # @test all(≈(res5, deconvolution(img, psf, optim_optimizer=vmlmb!, optim_options=(mem=20, lower=0, lnsrch=OptimPackNextGen.LineSearches.MoreThuenteLineSearch()),
+    # regularizer=nothing, padding=0.1, mapping=nothing, use_optim=OptimNextGen)[1], rtol=0.1))
     
     # test broadcasting with image having more dimensions
     img = zeros((3, 3, 2))

### 2021-07-10 src/deconvolution.jl
renamed use_optim into optimizer_package

@@ -59,7 +59,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
         optim_options=nothing,
         optim_optimizer=LBFGS(linesearch=BackTracking()),
         debug_f=nothing,
-        use_optim=OptimOptim) where {T, N}
+        optimizer_package=OptimOptim) where {T, N}
 
 
     # rec0 will be an array storing the final reconstruction
@@ -152,7 +152,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
                           optim_options=optim_options,
                           mapping=mapping,
                           loss=loss,
-                          debug_f=debug_f, use_optim=use_optim)
+                          debug_f=debug_f, optimizer_package=optimizer_package)
 
     res_out .*= rescaling
     # since we do some padding we need to extract the center part

### 2021-07-10 src/generic_invert.jl

@@ -37,10 +37,10 @@ function invert(measured, rec0, forward;
                 loss=Poisson(),
                 real_gradient=true,
                 debug_f=nothing,
-                use_optim =OptimOptim)
+                optimizer_package =OptimOptim)
 
     # if not special options are given, just restrict iterations
-    if isa(use_optim, OptimOptim) && optim_options == nothing
+    if isa(optimizer_package, OptimOptim) && optim_options == nothing
         optim_options = Optim.Options(iterations=iterations)
     end
     
@@ -102,13 +102,13 @@ function invert(measured, rec0, forward;
         end
     end
 
-    if isa(use_optim, Type{OptimOptim}) 
+    if isa(optimizer_package, Type{OptimOptim}) 
         optim_options = Optim.Options(iterations=iterations)
         
         # do the optimization with LBGFS
         res = Optim.optimize(Optim.only_fg!(fg!), rec0, optim_optimizer, optim_options)
         res_out = mf(Optim.minimizer(res))
-    elseif isa(use_optim, Type{OptimNextGen}) # supports a different interface as for example used in OptimPackNextGen for the function 'vmlmb!'
+    elseif isa(optimizer_package, Type{OptimNextGen}) # supports a different interface as for example used in OptimPackNextGen for the function 'vmlmb!'
         res = copy(rec0)
             
         if isnothing(optim_options)
@@ -118,7 +118,7 @@ function invert(measured, rec0, forward;
         end
         res_out = mf(res)
     else
-        error("Unknown optimizer interface $(typeof(use_optim))")
+        error("Unknown optimizer interface $(typeof(optimizer_package))")
     end
 
 

### 2021-07-18 v0.4.0/search_index.js
build based on 5b6df96

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas, storage=copy(μ))\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas, storage=copy(μ))\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_ga
[…]

### 2021-07-20 paper/paper.tex
Update paper [no CI]

@@
         However, such approaches create often several copies of the data. 
-        We currently use \verb|Tullio.jl|\footnote{\url{https://github.com/mcabbott/Tullio.jl}} to create efficient functions 
+        We currently use \verb|Tullio.jl|\cite{michael_abbott_2021_5047410} to create efficient functions 
         calculating the regularizer and the gradient. For simple expressions
@@
         Here we assumed a common single 3D PSF for all color channels.
-        Julia's broadcast mechanism handles that the PSF is only three dimensional and therefore
-        we only need to specify over which dimensions the convolution should happen.
+        Julia's broadcast mechanism is able to understand that 
+        the data has more dimensions that the PSF and expands the PSF so that a multiplication still works.
+        We only need to specify for the FFT over which dimensions the convolution should happen.
         \begin{figure}[h]

### 2021-07-20 examples/juliacon_2021.jl
Update juliacon file [no CI]

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.14.8
+# v0.14.5
 
 using Markdown
 using InteractiveUtils
@@ -192,7 +192,7 @@ $(@bind iter Slider(0:50, show_value=true))
 regularizer = $(@bind reg_bool CheckBox())"
 
 # ╔═╡ 803368e6-53fd-4413-b3f5-ffe46ee8983e
-img_deconv, res_img = deconvolution(img, psf, regularizer=reg_bool ? reg : nothing, iterations=iter, λ=λ);
+img_deconv, res_img = deconvolution(img_blurry, psf, regularizer=reg_bool ? reg : nothing, iterations=iter, λ=λ);
 
 # ╔═╡ e58e1f63-2c81-48fb-866a-4bb70bd428a6
 Gray.(img_deconv)

### 2021-07-23 dev/search_index.js
build based on 340d8d5

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas, storage=copy(μ))\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas, storage=copy(μ))\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_ga
[…]

### 2021-08-07 paper/paper.tex
Update paper [no ci]

@@
 \begin{abstract}
-
+\todo{fix citations with PkgCite.jl}
 Deconvolution is a versatile method to enhance the quality of signals measured with systems which can 
@@
             \hline
-            \verb|DeconvOptim.jl| & 14.0 & 0.86\\
-            \verb|DeconvOptim.jl| - TV & 18.9 & 1.55 \\
-            Richardson-Lucy (Julia) & 14.8 & 1.26 \\
-            \verb|ThreeDeconv.jl|& 2415 & 44.5 \\
-            \verb|GenericDeconv|  & 127 & 5.9\\
-            \verb|GenericDeconv| - TV & 213 & 8.7 \\
-            \verb|Huygens|  & & \\
-            \verb|DeconvolutionLab2| - LR & 1089 & \\
-            \verb|DeconvolutionLab2| - LR TV& 1131 & 
+            \verb|DeconvOptim.jl| & 32.9 & 2.20\\
+            \verb|DeconvOptim.jl| - TV & 39.9 & 4.46 \\
+            Richardson-Lucy (Julia) & 40.0 & 3.05 \\
+            \verb|ThreeDeconv.jl|& 1550 & 27.1 \\
+            \verb|GenericDeconv|  & 140 & 6.32\\
+            \verb|GenericDeconv| - TV & 233 & 9.35 \\
+            \verb|Huygens| & 30.1 & 6.8 \\
+            \verb|DeconvolutionLab2| - LR& 1640 & \\
             \end{tabular}
@@
             \hline
-            \verb|DeconvOptim.jl| & Poisson & 15 \\
-            \verb|DeconvOptim.jl| TV & Poisson & 15\\
-            Richardson-Lucy & Poisson & 120 \\
-            \verb|ThreeDeconv.jl|  & Gauss+Poisson& 500\\
-            \verb|GenericDeconv|  & Poisson & 40\\
-            \verb|GenericDeconv| TV & Poisson & 40 \\
+            \verb|DeconvOptim.jl| & Poisson & 45 \\
+            \verb|DeconvOptim.jl| TV & Poisson & 45\\
+            Richardson-Lucy & Poisson & 300 \\
+            \verb|ThreeDeconv.jl|  & Gauss+Poisson& 300\\
+            \verb|GenericDeconv|  & Poisson & 45\\
+            \verb|GenericDeconv| TV & Poisson & 45 \\
             \verb|Huygens| & & \\
-            \verb|DeconvolutionLab2| LR & Poisson & 200\\
-            \verb|DeconvolutionLab2| LR TV& Poisson & 200 
+            \verb|DeconvolutionLab2| LR & Poisson & 300\\
+            \verb|DeconvolutionLab2| LR TV& Poisson & 300 
             \end{tabular}
@@
         \end{table}
+        As summary of those performance tests we can state that our Julia implementation is very competitive and especially on the GPU
+        it was the fastest of the tested packages. On the CPU it is only beaten by the commercial \verb|Huygens| software. 
+        Despite \verb|ThreeDeconv.jl| written in Julia it is notably slower in comparison to our implementation.
+        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is poor.
 
-        As summary of those performance tests we can state that our Julia implementation is very competitive and especially on the CPU it is only
-        beaten by the commercial \verb|Huygens| software. Despite \verb|ThreeDeconv.jl| written in Julia 
-        it is notably slower in comparison to our implementation.
-        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is comparably poor.
+        \todo{maximum intensity}
         \begin{figure}[h]
+            \centering
             \begin{subfigure}{.3\textwidth}
                 \centering
-                \includegraphics[width=\textwidth]{figures/DeconvOptim_cuda_no_regularizer_0.87s.png}
-                \caption{\texttt{DeconvOptim.jl} without regularizer}
+                \includegraphics[width=\textwidth]{figures/MIPs/mip_DeconvOptim.png}
+                \caption{\texttt{DeconvOptim.jl} . $\text{NCC}= 0.86$.}
             \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/DeconvOptim_TV_0.002.png}
-                \caption{\texttt{DeconvOptim.jl} with TV}
+                \includegraphics[width=\textwidth]{figures/MIPs/mip_DeconvOptim_RL.png}
+                \caption{Julia Richardson-Lucy. $\text{NCC}= 0.74$.}
             \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/Lucy_richardson_julia.png}
-                \caption{\texttt{DeconvOptim.jl} Richardson-Lucy}
+                \includegraphics[width=\textwidth]{figures/MIPs/mip_DeconvolutionLab2.png}
+                \caption{\texttt{Deconvolution Lab2}. $\text{NCC}= 0.76$.}
             \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/Deconvolution_Lab2_200iterations.PNG}
-                \caption{\texttt{Deconvolution\\Lab2} with TV}
+                \includegraphics[width=\textwidth]{figures/MIPs/mip_ThreeDeconv.png}
+                \caption{\texttt{ThreeDeconv.jl}. $\text{NCC}= 0.85$.}
             \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/ThreeDeconv_600_iterations.png}
-                \caption{\texttt{ThreeDeconv.jl}}
+                \includegraphics[width=\textwidth]{figures/MIPs/mip_GenericDeconv.png}
+                \caption{\texttt{GenericDeconv}. $\text{NCC}= 0.86$.}
             \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth, height=2.5cm]{example-image-a}
-                \caption{\texttt{GenericDeconv}}
+                \includegraphics[width=\textwidth]{figures/MIPs/mip_Huygens.png}
+                \caption{\texttt{Huygens}$\text{NCC}= 0.86$.}
             \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth, height=2.5cm]{example-image-a}
-                \caption{\texttt{Huygens}}
+                \includegraphics[width=\textwidth]{figures/MIPs/mip_raw.png}
+                \caption{Measured image. $\text{NCC}= 0.41$.}
             \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/noisy.png}
-                \caption{~~Measured image with Poisson noise}
+                \includegraphics[width=\textwidth]{figures/MIPs/mip_ground_truth.png}
+                \caption{Ground truth. $\text{NCC}= 1.0$}
             \end{subfigure}
@@
 
+\section{Acknowledgement}
+This work was partially funded by the Honours Programme of the Friedrich Schiller 
+University of Jena\footnote{\url{https://www.uni-jena.de/en/honours_programme}}. 
+Additionally, we want to thank Scientific Volume Imaging for providing a trial license for Huygens and especially Mark Koenis for advising
+us how to adjust the settings to get optimal performance.
+
 \input{bib.tex}

### 2021-08-07 paper/paper.tex

@@
 \begin{abstract}
-\todo{fix citations with PkgCite.jl}
 Deconvolution is a versatile method to enhance the quality of signals measured with systems which can 
@@
 \end{abstract}
-
-\todo{multi view deconvolution}
 
@@
 behind the convolutions in neural nets. The reason is that this operation can be parallelized easily and therefore 
-is suitable on GPUs. However, the computational complexity for a 2D kernel with size $K \times L$ applied on an image with
+is suited for GPUs. However, the computational complexity for a 2D kernel with size $K \times L$ applied on an image with
 $N \times M$ data points is $\mathcal O(N \cdot M \cdot K \cdot L)$. It is clear that for larger kernel sizes ($K,L \gg 1$) the sliding method 
@@
             \centering
-            \begin{tikzpicture}
+            \begin{tikzpicture}[scale=0.7]
                 \node at (0,0) {\includegraphics[width=.9\textwidth]{figures/full_house_no_pad.png}};
@@
             \centering
-            \begin{tikzpicture}
+            \begin{tikzpicture}[scale=0.7]
                 \node at (0,0) {\includegraphics[width=.9\textwidth]{figures/full_house_pad.png}};
@@
     \centering
-    \includegraphics[width = .5\textwidth]{figures/pipeline.pdf}
-    \caption{}
+    \includegraphics[width = .4\textwidth]{figures/pipeline.pdf}
+    \caption{General pipeline of our deconvolution approach.}
     \label{fig:pipeline}
@@
 Since deconvolution is an ill-posed problem, we regularize the loss function with a regularizer.
-Afterwards we calculate the gradient of the loss function with respect to the reconstruction $x(\mathbf r)$ via automatic differentation (AD).
+Afterwards we calculate the gradient of the loss function with respect to the reconstruction $x(\mathbf r)$ via automatic differentiation (AD).
 The values of the total loss and the gradient are then used by an optimizer (to minimize the total loss) to apply a gradient descent optimization to get a proper reconstruction.\\
 
-As typical for Julia packages, except \verb|FFTW.jl| and \verb|CUDA.jl| \cite{besard2018juliagpu}, all code is written in Julia.
+As typical for Julia packages, except \verb|FFTW.jl| and \verb|CUDA.jl| \cite{besard2018juliagpu}, \cite{LLVM.jl-2017}, all code is written in Julia.
 Therefore it is easy to replace the forward model with any Julia code, as long as we can 
@@
 which is built from a finite number of past function and gradient evaluations. 
-Results are often good after 10 to 30 iterations whereas Richardson-Lucy takes
+Results are often good after 10 to 50 iterations whereas Richardson-Lucy takes
 a few hundreds iterations. 
@@
     $\text{rec}^2$ is definitely non-negative. Instead of directly using $\text{fwd}(\text{rec})$ we compare
-    $\text{fwd}(\text{rec}^2)$ with the measurement $Y$. This mapping function does not change the outcome as long
+    $\text{fwd}(\text{rec}^2)$ with the measurement $Y$ where $\text{fwd}$ is the function describing the physical operation (mostly 
+            a convolution). 
+    This mapping function does not change the outcome as long
     as it is an surjective function for the desired number space (e.g. a parabola is non-negative and covers all positive values) 
@@
         \centering
-        \begin{tikzpicture}
+        \begin{tikzpicture}[scale=0.7]
             \draw[fill=red!20!white] (0,0) rectangle (4,4);
@@
             \draw[fill=gray!40!white] (0.5,0.5) rectangle (3.5,3.5); 
-            \node[text width=2.5cm, color=black] at (2, 2) {area compared with measurement};
+            \node[text width=2.0cm, color=black] at (2.1, 2) {area compared with measurement};
         \end{tikzpicture}
@@
     Apart from forward model, the loss function is the most critical part in the optimization.
-    It has to account for the noise created by the measurement process or device.
+    It has to account for the noise created by the measurement process or instrument.
 
@@
     As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.
-
+    Our experiments additionally made use of the following packages: ArrayInterface.jl\cite{DifferentialEquations.jl-2017}, 
+    BenchmarkTools.jl\cite{BenchmarkTools.jl-2016}, FFTW.jl\cite{FFTW05}, LLVM.jl\cite{LLVM.jl-2017}, Optim.jl\cite{mogensen2018optim}
+    and  Zygote.jl\cite{Zygote.jl-2018}. 
     \subsection{One-Dimensional Time Series}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/resolution_test_chart_blurry.png}
+                \includegraphics[width=0.85\textwidth]{figures/resolution_test_chart_blurry.png}
                 \caption{Measured with Poisson noise}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
+                \includegraphics[width=0.85\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
                 \caption{Without regularizer $N=50$}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
+                \includegraphics[width=0.85\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
                 \caption{Without regularizer $N=10$}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
+                \includegraphics[width=0.85\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
                 \caption{With regularizer $N=24$.}
@@
         We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.
-        Additionally, we notice that the core in the Siemens star is denser is denser 
+        Additionally, we notice that the core in the Siemens star is denser 
         requiring higher spatial resolution to resolve. 
@@
         resolution. With the regularizer weight $\lambda$ one can adjust the regularization strength.
-        In \autoref{fig:rel_energy_regain} we show the relative energy regain $G_\textrm{R}$ \cite{rel_energy_regain} (REG).
+        In \autoref{fig:rel_energy_regain} we show the relative energy regain $G_\textrm{R}$ (REG) \cite{rel_energy_regain}.
         The meaning of the REG is how well certain frequencies are reconstructed in comparison
@@
         wrong information at this frequencies
-        which are further from the ground truth then not reconstructing these frequencies. 
+        which are further from the ground truth than not reconstructing these frequencies. 
         \begin{figure}[h]
@@
     \subsection{Full Deconvolution}
-        In \autoref{tab:deconv} we show the deconvolution time for a 3D dataset with size \todo{size footnote} 
+        In \autoref{tab:deconv} we show the deconvolution time for a 3D dataset with a size of $512 \times 256 \times 128$ 
+        \footnote{Dataset was taken from \url{http://bigwww.epfl.ch/deconvolution/data/microtubules/}\cite{deconvlab2}.} 
         The basic settings of the different algorithms and packages are noted in \autoref{tab:deconvprop}.
@@
         and a quadratic non-negativity constraint.
-        When the TV regularizer was added the weight was $\lambda = 0.002$.
+        When the TV regularizer was added the weight was $\lambda = 0.001$.
         The general idea of \verb|GenericDeconv| is very similar to \verb|DeconvOptim.jl|.
         \verb|DeconvolutionLab2| offers a wide variety of different algorithms which however only run on a CPU. 
-        To put the numbers into context, even the non-iterative Tikhonov Regularization Inverse Filter (TRIF/TR) had a 
-        runtime of \SI{4}{\second}. In the table we show the results of an 
-        iterative Richardson-Lucy deconvolution. As number of iterations we set 80 and as regularizer weight $\lambda=0.002$.\\
+        In the table we show the results of an 
+        iterative Richardson-Lucy deconvolution. The regularizer weight was $\lambda=0.001$.\\
         In \verb|DeconvOptim.jl| we measured the runtime of the default deconvolution routine with a Poisson loss function
-        and the runtime of straightforward Richardson-Lucy deconvolution without a regularizer.
-        \verb|ThreeDeconv.jl| is another Julia deconvolution toolbox for deconvolution of three dimensional data.
-        In contrast to their according publication \cite{ikoma2018convex} we needed more iterations to achieve good results
-        on our used dataset. The regularizer weight was $\lambda=10^{-7}$. 
-        The software requires a flat and a dark field image we could not provide. That might influence the quality of the reconstructed images
-        but in terms of performance the runtimes might be only by a factor of 2-5 smaller than the runtimes we obtained (Ikoma et al. used 140 iterations in their datasets).
-
-        Since it is hard to judge the quality of those results with a numerical loss function value, we compare them visually.
-        The CPU versions were multi threaded (if possible). \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
+        and the runtime of straightforward Richardson-Lucy deconvolution without a regularizer.\\
+        \verb|ThreeDeconv.jl| is another Julia deconvolution toolbox for deconvolution of three dimensional data, the regularizer weight was $\lambda=10^{-7}$. 
+        Since it is hard to judge the quality of those results with a numerical loss function value, 
+        we compare them by the NCC, see \autoref{img:results}.
+        The CPU versions were multi threaded (if possible). 
+        \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
 
@@
         As summary of those performance tests we can state that our Julia implementation is very competitive and especially on the GPU
-        it was the fastest of the tested packages. On the CPU it is only beaten by the commercial \verb|Huygens| software. 
+        it was the fastest of the tested packages. 
+        We also see that our routine was faster than a plain Richardson-Lucy mainly due to the much lower number
+        of iterations.
+        On the CPU \verb|DeconvOptim.jl| is only beaten by the commercial \verb|Huygens| software. 
         Despite \verb|ThreeDeconv.jl| written in Julia it is notably slower in comparison to our implementation.
-        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is poor.
+        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is poor in
+        comparison to all other packages.
 
-        \todo{maximum intensity}
         \begin{figure}[h]
@@
             \end{subfigure}
-            \caption{Overview of some of the deconvolution results of different packages.}
+            \caption{Maximum intensity projections along one dimensions of some of the deconvolution results.}
             \label{img:results}

### 2021-08-08 docs/generate_images.jl
Update docs with changing conv_psf

@@ -24,8 +24,8 @@ function ideal_freq()
     psf ./= sum(psf)
     psf = convert(Array{Float32}, psf)
     
-    #img_b = center_extract(conv_psf(center_set!(copy(z1), img), ifftshift(center_set!(z, fftshift(psf))), [1, 2]), size(img))
-    img_b = conv_psf(img, psf, [1, 2])
+    #img_b = center_extract(conv(center_set!(copy(z1), img), ifftshift(center_set!(z, fftshift(psf))), [1, 2]), size(img))
+    img_b = conv(img, psf, [1, 2])
     img_n = poisson(img_b, N_phot)
     
     reg = DeconvOptim.TV(num_dims=2, sum_dims=[1, 2])

### 2021-08-08 docs/make.jl

@@ -16,6 +16,7 @@ makedocs(cite_bib, modules=[DeconvOptim],
                         "workflow/3D_dataset.md",
                         "workflow/cuda.md",
                         "workflow/flexible_invert.md",
+                        "workflow/performance_tips.md",
                     ],
                 "Background" => Any[
                     "background/physical_background.md",

### 2021-08-08 src/deconvolution.jl

@@ -41,7 +41,7 @@ julia> img = Float32.(testimage("resolution_test_512"));
 
 julia> psf = Float32.(generate_psf(size(img), 30));
 
-julia> img_b = conv_psf(img, psf);
+julia> img_b = conv(img, psf);
 
 julia> img_n = poisson(img_b, 300);
 
@@ -99,7 +99,7 @@ function deconvolution(measured::AbstractArray{T, N}, psf;
     fill!(rec0, one(eltype(measured))) 
     
     # alternative rec0_center, unused at the moment
-    #rec0_center = m_invf(abs.(conv_psf(measured, psf, conv_dims)))
+    #rec0_center = m_invf(abs.(conv(measured, psf, conv_dims)))
     #
     # take the mean as the initial guess
     # therefore has the same total energy at the initial guess as

### 2021-08-08 dev/search_index.js
build based on 8646df5

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas, storage=similar(μ))\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas, storage=similar(μ))\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_gauss_a
[…]

### 2021-08-08 test/runtests.jl
Update tests regarding analysis tools

@@ -17,6 +17,7 @@ Random.seed!(42)
 end
 
 
+include("analysis_tools.jl")
 include("conv.jl")
 include("mappings.jl")
 

### 2021-08-08 test/runtests.jl
Update tests

@@ -18,6 +18,7 @@ end
 
 
 include("analysis_tools.jl")
+include("hessian_schatten_norm.jl")
 include("conv.jl")
 include("mappings.jl")
 

### 2021-08-09 paper/paper.tex
Update paper [no ci]

@@
 Due to noise and the low pass filter effect of the PSF, deconvolution is an ill-posed problem which cannot be solved directly.\\
-A well known approach, because of its simplicity, has been the iterative Richardson-Lucy deconvolution algorithm \cite{Richardson:72}, \cite{lucy:74} for Poisson noise degraded signals.
+A well known approach, because of its simplicity, has been the iterative Richardson-Lucy deconvolution algorithm 
+\cite{Richardson:72}, \cite{lucy:74} for Poisson noise degraded signals.
 Another common method is the non-iterative Wiener filter \cite{wiener2013extrapolation} because of its predictable runtime.
 The Wiener filter assumes additive noise which is often not a good approximation, especially in low light conditions as in microscopy or astronomy. 
-Recently machine learning based methods have become more and more favoured in deconvolution because
+Recently, machine learning based methods have become more and more favoured in deconvolution because
 of the possibility to add learned properties of similar images to the algorithm \cite{Kruse_2017_ICCV}.
 However, those implementations are usually restricted to cases where experimental datasets are available for the characterization and training.
-\verb|DeconvOptim.jl| is a toolbox written in Julia \cite{bezanson2017julia} which offers several deconvolution algorithms like the iterative Richardson-Lucy algorithms but also
+\verb|DeconvOptim.jl| is a toolbox written in Julia \cite{bezanson2017julia} which offers several deconvolution algorithms 
+like the iterative Richardson-Lucy algorithm but also
 much more flexible methods which are based on minimizing a 
@@
     \end{equation} 
-        which means that a Fourier transform of a  convolution operation is equivalent to a point wise multiplication of the Fourier transforms 
+        which means that a Fourier transform $\mathcal F$ of a convolution operation is equivalent to a point wise multiplication of the Fourier transforms 
         of $h$ and $S$.
@@
         For a 2D dataset with size $N \times M$ it is $\mathcal{O}(N \cdot M \log(N \cdot M))$ and accordingly for higher dimensions.
-
-\subsection{Sliding Convolution Windows}
-Convolutions can be also calculated with a sliding kernel in real space which is the direct approach to
-solve the integral in \autoref{eq:conv}.
-That mechanism is the working principle
-behind the convolutions in neural nets. The reason is that this operation can be parallelized easily and therefore 
-is suited for GPUs. However, the computational complexity for a 2D kernel with size $K \times L$ applied on an image with
-$N \times M$ data points is $\mathcal O(N \cdot M \cdot K \cdot L)$. It is clear that for larger kernel sizes ($K,L \gg 1$) the sliding method 
+        Spatially based convolution kernels with size $K \times L$ applied on an image with
+        $N \times M$ data points have a runtime of $\mathcal O(N \cdot M \cdot K \cdot L)$.
+        It is clear that for larger kernel sizes ($K,L \gg 1$) the sliding method 
         has worse computational complexity than the FFT based convolutions. The many cores of a GPU can mitigate that to a certain extent
-but since the FFT (CuFFT in the CUDA library \cite{CUDA}) can be also executed in parallel fashion, both approaches profit from parallelization.
-If the kernel is separable over the dimensions (like a Gaussian kernel) the complexity changes to $\mathcal O(N \cdot M \cdot L +  N \cdot M \cdot K)$ however most optical PSFs are not separable and therefore this is not generally applicable.
+        but since the FFT (CuFFT in the CUDA library \cite{CUDA}) can be also executed in parallel fashion, 
+        both approaches profit from parallelization.
 
@@
             \begin{tikzpicture}[scale=0.7]
-                \node at (0,0) {\includegraphics[width=.9\textwidth]{figures/full_house_no_pad.png}};
+                \node at (0,0) {\includegraphics[width=.63\textwidth]{figures/full_house_no_pad.png}};
                 \draw[red] (-2.0, -1.6) rectangle (-1.6, -1.2);
-                \node[color=red] at (0,0) {\includegraphics[width=.4\textwidth]{figures/edge_house_no_pad.png}};
+                \node[color=red] at (0,0) {\includegraphics[width=.28\textwidth]{figures/edge_house_no_pad.png}};
                 \draw[color=red] (-0.91, -0.9) rectangle (0.9, 0.9); 
@@
             \begin{tikzpicture}[scale=0.7]
-                \node at (0,0) {\includegraphics[width=.9\textwidth]{figures/full_house_pad.png}};
+                \node at (0,0) {\includegraphics[width=.63\textwidth]{figures/full_house_pad.png}};
                 \draw[red] (-2.0, -1.6) rectangle (-1.6, -1.2);
-                \node[color=red] at (0,0) {\includegraphics[width=.4\textwidth]{figures/edge_house_pad.png}};
+                \node[color=red] at (0,0) {\includegraphics[width=.28\textwidth]{figures/edge_house_pad.png}};
                 \draw[color=red] (-0.90, -0.9) rectangle (0.9, 0.9); 
@@
     As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.
-    Our experiments additionally made use of the following packages: ArrayInterface.jl\cite{DifferentialEquations.jl-2017}, 
+    Our experiments additionally made use of the following packages in Julia 1.6.2: ArrayInterface.jl\cite{DifferentialEquations.jl-2017}, 
     BenchmarkTools.jl\cite{BenchmarkTools.jl-2016}, FFTW.jl\cite{FFTW05}, LLVM.jl\cite{LLVM.jl-2017}, Optim.jl\cite{mogensen2018optim}
@@
                 \centering
-                \includegraphics[width=0.85\textwidth]{figures/resolution_test_chart_blurry.png}
+                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_blurry.png}
                 \caption{Measured with Poisson noise}
@@
                 \centering
-                \includegraphics[width=0.85\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
+                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
                 \caption{Without regularizer $N=50$}
@@
                 \centering
-                \includegraphics[width=0.85\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
+                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
                 \caption{Without regularizer $N=10$}
@@
                 \centering
-                \includegraphics[width=0.85\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
+                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
                 \caption{With regularizer $N=24$.}
@@
         In the non-regularized one has to hand-optimize the number of iterations whereas in the regularized one has to optimize $\lambda$.
+        However, without the ground truth image it is not clear which iteration or $\lambda$ is optimal and hence
+        this depends on the user.
         Advantage of the non-regularized version is, that it performs more than twice as fast but as it can be seen in \autoref{fig:fabioc} 
@@
         the data has more dimensions that the PSF and expands the PSF so that a multiplication still works.
-        We only need to specify for the FFT over which dimensions the convolution should happen.
         \begin{figure}[h]
@@
                 \centering
-                \includegraphics[width = .95\textwidth]{figures/raw_rgb.png}
+                \includegraphics[width = .85\textwidth]{figures/raw_rgb.png}
             \end{subfigure}%
@@
                 \centering
-                \includegraphics[width = .95\textwidth]{figures/deconvolved_rgb.png}
+                \includegraphics[width = .85\textwidth]{figures/deconvolved_rgb.png}
             \end{subfigure}
@@
         \end{figure} 
+        We only need to specify for the FFT over which dimensions the convolution should happen.
         Clearly we can see that the deconvolution removed a lot of the background blur.
@@
                 \hline
-                CPU & \SI{83.9}{\milli\second} & \SI{7.18}{\second} & \SI{5.53}{\milli\second}  & \SI{119.8}{\milli\second}   \\ 
-                GPU & \SI{2.5}{\milli\second}  & \SI{22.9}{\milli\second}& \SI{4.00}{\milli\second}  & \SI{12.53}{\second} \\
+                CPU & \SI{83.9}{\milli\second} & \SI{7180}{\milli\second} & \SI{5.53}{\milli\second}  & \SI{119.8}{\milli\second}   \\ 
+                GPU & \SI{2.5}{\milli\second}  & \SI{22.9}{\milli\second}& \SI{4.00}{\milli\second}  & \SI{12530}{\milli\second} \\
                 \hline
@@
                 CPU & \SI{48}{\milli\second}   & \SI{364}{\milli\second}&   & \\
-                GPU & \SI{887}{\micro\second}   & \SI{10.2}{\milli\second}&   &
+                GPU & \SI{0.887}{\milli\second}   & \SI{10.2}{\milli\second}&   &
                 \end{tabular}
@@
     \subsection{Full Deconvolution}
-        In \autoref{tab:deconv} we show the deconvolution time for a 3D dataset with a size of $512 \times 256 \times 128$ 
-        \footnote{Dataset was taken from \url{http://bigwww.epfl.ch/deconvolution/data/microtubules/}\cite{deconvlab2}.} 
+        In \autoref{tab:deconv} we show the deconvolution time for a 3D dataset with a size of $512 \times 256 \times 128$\footnote{Dataset was taken from \url{http://bigwww.epfl.ch/deconvolution/data/microtubules/}\cite{deconvlab2}.
+During our experiments we noticed a pixel offset between the ground truth and the noisy image.
+To reproduce our results, one has to correct this offset if the images are compared quantitatively.}
         The basic settings of the different algorithms and packages are noted in \autoref{tab:deconvprop}.
@@
         \begin{table}[h]
-            \begin{tabular}{l l l}
-                &  CPU in s& GPU in s\\ 
+            \begin{tabular}{l l l l }
+                &  CPU in \si{\second}& GPU in \si{\second} & NCC\\ 
             \hline
-            \verb|DeconvOptim.jl| & 32.9 & 2.20\\
-            \verb|DeconvOptim.jl| - TV & 39.9 & 4.46 \\
-            Richardson-Lucy (Julia) & 40.0 & 3.05 \\
-            \verb|ThreeDeconv.jl|& 1550 & 27.1 \\
-            \verb|GenericDeconv|  & 140 & 6.32\\
-            \verb|GenericDeconv| - TV & 233 & 9.35 \\
-            \verb|Huygens| & 30.1 & 6.8 \\
-            \verb|DeconvolutionLab2| - LR& 1640 & \\
+            \verb|DeconvOptim.jl| & 32.9 & 2.20 & 0.86\\
+            \verb|DeconvOptim.jl| - TV & 39.9 & 4.46 & 0.79\\
+            Richardson-Lucy (Julia) & 40.0 & 3.05 & 0.74 \\
+            \verb|ThreeDeconv.jl|& 1550 & 27.1 & 0.85\\
+            \verb|GenericDeconv|  & 140 & 6.32 & 0.86\\
+            \verb|GenericDeconv| - TV & 233 & 9.35 & 0.73\\
+            \verb|Huygens| & 30.1 & 6.8 & 0.86\\
+            \verb|DeconvolutionLab2| - LR& 1640 & & 0.76\\
             \end{tabular}
-            \caption{Runtimes of different deconvolution implementations.}
+            \caption{Runtimes of different deconvolution implementations. See \autoref{tab:deconvprop} for the number of iterations
+            for each method. We have chosen the same number of iterations for the deconvolutions with and without regularizers.}
             \label{tab:deconv}
@@
         \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
-
+        \todo{anscombe norm speed}
+        \todo{Fix table }
         \begin{table}[h]
@@
             \verb|DeconvolutionLab2| LR & Poisson & 300\\
-            \verb|DeconvolutionLab2| LR TV& Poisson & 300 
             \end{tabular}
@@
         Despite \verb|ThreeDeconv.jl| written in Julia it is notably slower in comparison to our implementation.
-        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is poor in
+        \verb|DeconvolutionLab2| is written in Java and also uses hand written gradients but still its speed is poor in
         comparison to all other packages.
@@
     University of Jena\footnote{\url{https://www.uni-jena.de/en/honours_programme}}.
+    We want to thank Michael Abbott because he had the
+    initial idea for the metaprogramming regularizers based on \verb|Tullio.jl|. 
     Additionally, we want to thank Scientific Volume Imaging for providing a trial license for Huygens and especially Mark Koenis for advising

### 2021-08-09 paper/paper.tex

@@
 \verb|DeconvOptim.jl| is a toolbox written in Julia \cite{bezanson2017julia} which offers several deconvolution algorithms 
-like the iterative Richardson-Lucy algorithm but also
+like the iterative Richardson-Lucy algorithms but also
 much more flexible methods which are based on minimizing a 
@@
     \end{equation} 
-        which means that a Fourier transform $\mathcal F$ of a convolution operation is equivalent to a point wise multiplication of the Fourier transforms 
+        which means that a Fourier transform of a  convolution operation is equivalent to a point wise multiplication of the Fourier transforms 
         of $h$ and $S$.
@@
         For a 2D dataset with size $N \times M$ it is $\mathcal{O}(N \cdot M \log(N \cdot M))$ and accordingly for higher dimensions.
-        Spatially based convolution kernels with size $K \times L$ applied on an image with
-        $N \times M$ data points have a runtime of $\mathcal O(N \cdot M \cdot K \cdot L)$.
-        It is clear that for larger kernel sizes ($K,L \gg 1$) the sliding method 
+
+\subsection{Sliding Convolution Windows}
+Convolutions can be also calculated with a sliding kernel in real space which is the direct approach to
+solve the integral in \autoref{eq:conv}.
+That mechanism is the working principle
+behind the convolutions in neural networks. The reason is that this operation can be parallelized easily and therefore 
+is suited for GPUs. However, the computational complexity for a 2D kernel with size $K \times L$ applied on an image with
+$N \times M$ data points is $\mathcal O(N \cdot M \cdot K \cdot L)$. It is clear that for larger kernel sizes ($K,L \gg 1$) the sliding method 
 has worse computational complexity than the FFT based convolutions. The many cores of a GPU can mitigate that to a certain extent
-        but since the FFT (CuFFT in the CUDA library \cite{CUDA}) can be also executed in parallel fashion, 
-        both approaches profit from parallelization.
+but since the FFT (CuFFT in the CUDA library \cite{CUDA}) can be also executed in parallel fashion, both approaches profit from parallelization.
+If the kernel is separable over the dimensions (like a Gaussian kernel) the complexity changes to $\mathcal O(N \cdot M \cdot L +  N \cdot M \cdot K)$ however most optical PSFs are not separable and therefore this is not generally applicable.
 
@@
         In the non-regularized one has to hand-optimize the number of iterations whereas in the regularized one has to optimize $\lambda$.
-        However, without the ground truth image it is not clear which iteration or $\lambda$ is optimal and hence
-        this depends on the user.
         Advantage of the non-regularized version is, that it performs more than twice as fast but as it can be seen in \autoref{fig:fabioc} 
@@
                 \hline
-                CPU & \SI{83.9}{\milli\second} & \SI{7180}{\milli\second} & \SI{5.53}{\milli\second}  & \SI{119.8}{\milli\second}   \\ 
-                GPU & \SI{2.5}{\milli\second}  & \SI{22.9}{\milli\second}& \SI{4.00}{\milli\second}  & \SI{12530}{\milli\second} \\
+                CPU & \SI{83.9}{\milli\second} & \SI{7.18}{\second} & \SI{5.53}{\milli\second}  & \SI{119.8}{\milli\second}   \\ 
+                GPU & \SI{2.5}{\milli\second}  & \SI{22.9}{\milli\second}& \SI{4.00}{\milli\second}  & \SI{12.53}{\second} \\
                 \hline
@@
                 CPU & \SI{48}{\milli\second}   & \SI{364}{\milli\second}&   & \\
-                GPU & \SI{0.887}{\milli\second}   & \SI{10.2}{\milli\second}&   &
+                GPU & \SI{887}{\micro\second}   & \SI{10.2}{\milli\second}&   &
                 \end{tabular}
@@
     \subsection{Full Deconvolution}
-        In \autoref{tab:deconv} we show the deconvolution time for a 3D dataset with a size of $512 \times 256 \times 128$\footnote{Dataset was taken from \url{http://bigwww.epfl.ch/deconvolution/data/microtubules/}\cite{deconvlab2}.
-During our experiments we noticed a pixel offset between the ground truth and the noisy image.
-To reproduce our results, one has to correct this offset if the images are compared quantitatively.}
+        In \autoref{tab:deconv} we show the deconvolution time for a 3D dataset with a size of $512 \times 256 \times 128$\footnote{Dataset was taken from \url{http://bigwww.epfl.ch/deconvolution/data/microtubules/}\cite{deconvlab2}.}
         The basic settings of the different algorithms and packages are noted in \autoref{tab:deconvprop}.
@@
             \end{tabular}
-            \caption{Runtimes of different deconvolution implementations. See \autoref{tab:deconvprop} for the number of iterations
-            for each method. We have chosen the same number of iterations for the deconvolutions with and without regularizers.}
+            \caption{Runtimes of different deconvolution implementations.}
             \label{tab:deconv}
@@
         \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
-        \todo{anscombe norm speed}
-        \todo{Fix table }
+
         \begin{table}[h]
@@
             \verb|DeconvolutionLab2| LR & Poisson & 300\\
+            \verb|DeconvolutionLab2| LR TV& Poisson & 300 
             \end{tabular}
@@
         Despite \verb|ThreeDeconv.jl| written in Julia it is notably slower in comparison to our implementation.
-        \verb|DeconvolutionLab2| is written in Java and also uses hand written gradients but still its speed is poor in
+        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is poor in
         comparison to all other packages.

### 2021-08-09 src/conv.jl
Update conv method to return reference instead of fresh copy to save memory [no ci]

@@ -3,9 +3,11 @@ export conv, plan_conv, conv_psf, plan_conv_psf
 
 """
     conv(u, v[, dims])
-    Convolve `u` with `v` over `dims` dimensions with an FFT based method.
-    Note, that this method introduces wrap-around artifacts without
-    proper padding/windowing.
+
+Convolve `u` with `v` over `dims` dimensions with an FFT based method.
+Note, that this method introduces wrap-around artifacts without
+proper padding/windowing.
+
 # Arguments
 * `u` is an array in real space.
 * `v` is the array to be convolved in real space as well.
@@ -14,10 +16,12 @@ export conv, plan_conv, conv_psf, plan_conv_psf
     If `dims` is an array with integers, we perform convolution 
     only over these dimensions. Eg. `dims=[1,3]` would perform the convolution
     over the first and third dimension. Second dimension is not convolved.
+
 If `u` and `v` are both a real valued array we use `rfft` and hence
 the output is real as well.
 If either `u` or `v` is complex we use `fft` and output is hence complex.
- # Examples
+
+# Examples
 1D with FFT over all dimensions. We choose `v` to be a delta peak.
 Therefore convolution should act as identity.
 ```jldoctest
@@ -79,6 +83,7 @@ end
 
 """
     plan_conv(u, v [, dims])
+
 Pre-plan an optimized convolution for arrays shaped like `u` and `v` (based on pre-plan FFT)
 along the given dimenions `dims`.
 `dims = 1:ndims(u)` per default.
@@ -89,6 +94,13 @@ The second return is the convolution function `pconv`.
 `pconv` itself has two arguments. `pconv(u, v_ft=v_ft)` where `u` is the object and `v_ft` the v_ft.
 This function achieves faster convolution than `conv(u, u)`.
 Depending whether `u` is real or complex we do `fft`s or `rfft`s
+
+# Warning
+The resulting output of the `pconv` function is a reference to an internal, allocated array.
+If you use the `pconv` function for different tasks, 
+a new call to `pconv` will change the previous result (since the previous result was only a reference, not a new array). 
+
+
 # Examples
 ```jldoctest
 julia> u = [1 2 3 4 5]
@@ -124,6 +136,7 @@ end
 
 """
[…]

### 2021-08-10 paper/header.tex
Update paper draft
Update paper and add images to git

@@
 
-\title{DeconvOptim.jl - Image Deconvolution with Julia}
+\title{DeconvOptim.jl - Signal Deconvolution with Julia}
 
@@
 \author[1, 2, 3]{Rainer Heintzmann}
-\affil[1]{Faculty of Physics and Astronomy, Friedrich-Schiller-University,Jena, Germany}
-\affil[2]{Leibniz Institute of Photonic Technology, Albert-Einstein-Straße 9,07745 Jena, Germany}
+\affil[1]{Faculty of Physics and Astronomy, Friedrich-Schiller-University, Jena, Germany}
+\affil[2]{Leibniz Institute of Photonic Technology, Albert-Einstein-Straße 9, 07745 Jena, Germany}
 \affil[3]{Institute of Physical Chemistry and Abbe Center of Photonics, Friedrich-Schiller-University, Helmholtzweg 4, Jena, Germany}

### 2021-08-10 dev/search_index.js
build based on 3328124

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"references/#References","page":"References","title":"References","text":"","category":"section"},{"location":"references/","page":"References","title":"References","text":"See here for a list of references","category":"page"},{"location":"references/","page":"References","title":"References","text":"","category":"page"},{"location":"function_references/loss/#Loss-Functions","page":"Loss Functions","title":"Loss Functions","text":"","category":"section"},{"location":"function_references/loss/","page":"Loss Functions","title":"Loss Functions","text":"Poisson\npoisson_aux\nGauss\ngauss_aux\nScaledGauss\nscaled_gauss_aux","category":"page"},{"location":"function_references/loss/#DeconvOptim.Poisson","page":"Loss Functions","title":"DeconvOptim.Poisson","text":"Poisson()\n\nReturns a function to calculate Poisson loss Check the help of poisson_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.poisson_aux","page":"Loss Functions","title":"DeconvOptim.poisson_aux","text":"poisson_aux(μ, meas, storage=similar(μ))\n\nCalculates the Poisson loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.Gauss","page":"Loss Functions","title":"DeconvOptim.Gauss","text":"Gauss()\n\nReturns a function to calculate Gauss loss. Check the help of gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.gauss_aux","page":"Loss Functions","title":"DeconvOptim.gauss_aux","text":"gauss_aux(μ, meas, storage=similar(μ))\n\nCalculates the Gauss loss for μ and meas. μ can be of larger size than meas. In that case we extract a centered region from μ of the same size as meas.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.ScaledGauss","page":"Loss Functions","title":"DeconvOptim.ScaledGauss","text":"ScaledGauss()\n\nReturns a function to calculate scaled Gauss loss. Check the help of scaled_gauss_aux.\n\n\n\n\n\n","category":"function"},{"location":"function_references/loss/#DeconvOptim.scaled_gauss_a
[…]

### 2021-08-10 paper/header.tex
Update date [no ci]

--- 2021-06-29 paper/header.tex
@@
 
-\title{DeconvOptim.jl - Image Deconvolution with Julia}
+\title{My JuliaCon proceeding}
 
-\author[1, 2]{Felix Wechsler}
-\author[1, 2, 3]{Rainer Heintzmann}
-\affil[1]{Faculty of Physics and Astronomy, Friedrich-Schiller-University,Jena, Germany}
-\affil[2]{Leibniz Institute of Photonic Technology, Albert-Einstein-Straße 9,07745 Jena, Germany}
-\affil[3]{Institute of Physical Chemistry and Abbe Center of Photonics, Friedrich-Schiller-University, Helmholtzweg 4, Jena, Germany}
+\author[1]{1st author}
+\author[1, 2]{2nd author}
+\author[2]{3rd author}
+\affil[1]{University}
+\affil[2]{National Lab}
 
-\keywords{Julia, Image Processing, Deconvolution, Microscopy}
+\keywords{Julia, Optimization, Game theory, Compiler}
 
 \hypersetup{
-pdftitle = {DeconvOptim.jl - Image Deconvolution with Julia},
+pdftitle = {My JuliaCon proceeding},
 pdfsubject = {JuliaCon 2019 Proceedings},
-pdfauthor = {Felix Wechsler, Rainer Heintzmann},
-pdfkeywords = {Julia, Image Processing, Deconvolution, Microscopy},
+pdfauthor = {1st author, 2nd author, 3rd author},
+pdfkeywords = {Julia, Optimization, Game theory, Compiler},
 }

### 2021-08-16 examples/juliacon_2021.jl
added compat for higher ChainRulesCore.jl versions.

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.14.8
+# v0.15.1
 
 using Markdown
 using InteractiveUtils
@@ -22,14 +22,32 @@ end
 # ╔═╡ 3310d2f7-450a-4cd1-9c3a-46d02d23a7c6
 using Revise
 
+# ╔═╡ 226f5316-3bfb-4ccc-b3e2-7efd0bae2456
+using TestImages, ImageShow, Plots, LinearAlgebra, IndexFunArrays, Noise, FourierTools, SpecialFunctions, FFTW, LaTeXStrings, PlutoUI, Images, Tullio
+
 # ╔═╡ d27b2d72-d264-11eb-0be5-13dcacfd2adc
-using DeconvOptim, TestImages, ImageShow, Plots, LinearAlgebra, IndexFunArrays, Noise, FourierTools, SpecialFunctions, FFTW, LaTeXStrings, PlutoUI, Images, Tullio
+using DeconvOptim
+
+# ╔═╡ 18a1b7e0-5619-40a7-b5f7-1915f4f5ebda
+
+
+# ╔═╡ aba859e7-be5a-43f8-8dd4-28fe966a9c98
+
+
+# ╔═╡ df685450-e964-11eb-1878-c5888e6932f0
+
+
+# ╔═╡ f6d583cb-18d5-4000-a5b3-bc22f5d3e52e
+
 
 # ╔═╡ 952b251c-207b-4412-b6e1-268fce1647d9
 begin
-	img = Float32.(testimage("fabio_gray"));
+	img = Float32.(testimage("resolution_512"));
 	img_1D = img[:, 200]
 end;
+
+# ╔═╡ a7606eb2-d7d9-4cd4-aa06-1379affe0785
+
 
 # ╔═╡ fa8cd9c9-a2fd-495c-8d22-ada7bb9c39f6
 otf(x, Δx=1) = begin
@@ -192,7 +210,7 @@ $(@bind iter Slider(0:50, show_value=true))
 regularizer = $(@bind reg_bool CheckBox())"
 
 # ╔═╡ 803368e6-53fd-4413-b3f5-ffe46ee8983e
[…]

### 2021-08-17 src/DeconvOptim.jl
New FillArrays dependency

@@ -25,6 +25,7 @@ using Interpolations
 using ChainRulesCore
 using LinearAlgebra
 
+using FillArrays
 
 gpu_or_cpu(x) = Array
 

### 2021-08-17 src/conv.jl
Fix error with gradient buffers

@@ -164,7 +164,14 @@ function ChainRulesCore.rrule(::typeof(p_conv_aux!), P, P_inv, u, v, u_ft_stor, 
                 conj(v)
             end
         end
-        ∇ = p_conv_aux!(P, P_inv, collect(eltype(u).(barx)), conj_v, u_ft_stor, out)
+        barx = let
+            if typeof(barx) <: FillArrays.Fill
+                collect(eltype(u).(barx))
+            else
+                barx
+            end
+        end
+        ∇ = p_conv_aux!(P, P_inv, barx, conj_v, u_ft_stor, copy(out))
         return NoTangent(), z, z, ∇, z, z, z
     end 
     return Y, conv_pullback

### 2021-08-17 src/generic_invert.jl

@@ -58,7 +58,7 @@ function invert(measured, rec0, forward;
         end
     end
     
-    storage_μ = similar(measured)
+    storage_μ = deepcopy(measured)
     function total_loss(rec)
         # handle if there is a provided mapping function
         mf_rec = mf(rec) 

### 2021-08-18 paper/figures/pipeline.tex

--- 2020-11-03 docs/src/assets/tex/pipeline.tex
@@
     text centered, rounded corners, minimum height=2.5em]
+\tikzstyle{output} = [rectangle, draw, fill=green!60, 
+    text centered, rounded corners, minimum height=2.5em]
 \tikzstyle{line} = [draw, ->]
@@
 
-        \node[block] (start) {rec \\(variables to optimize for)};
-        \node[block, below of=start] (map) {Mapping \\ \footnotesize (sets constraints like positivity)};
+        \node[block] (start) {rec \\\footnotesize (variables to optimize for)};
+        \node[input, above of=start] (guess) {Initial guess};
+        \node[block, below of=start] (map) {Mapping \\ \footnotesize (sets constraints like $\geq 0$)};
         \node[block, below of=map, left of=map] (forw) {Forward \\\footnotesize(convolution)};
@@
 
+        \node[output, node distance=3cm, below of=opt] (res) {Result \\ \footnotesize(Mapping(rec))};
+
+        \path [line] (guess) -- (start);
         \path [line] (start) -- (map);
@@
         \path [line] (tloss) -- (opt);
-        \path [line] (reg) --node [midway] {Weighting with $\lambda \cdot$} (tloss) ;
+        \path [line] (reg) --node [midway] {Weighting with $\lambda$} (tloss) ;
+        \path [line] (opt) -- node[midway] {if result is good enough} (res);
 
-        \path[line] (opt) --++ (5, 0) --++ (0, 10.2) node[] {AD calculates gradient \\ to optimize for rec} -- (start) ;
+        \path[line] (opt) --++ (5, 0) --++ (0, 10.2) node[] {AD based gradient update} -- (start) ;
 

### 2021-09-15 paper/header.tex
Update latex header [no ci]

--- 2021-08-10 paper/header.tex
@@
 \hypersetup{
-pdftitle = {DeconvOptim.jl - Image Deconvolution with Julia},
+pdftitle = {DeconvOptim.jl - Signal Deconvolution with Julia},
 pdfsubject = {JuliaCon 2019 Proceedings},

### 2021-09-22 src/conv.jl
Change to NoTangent()

@@ -73,7 +73,6 @@ function ChainRulesCore.rrule(::typeof(conv), u::AbstractArray{T, N}, v::Abstrac
                               dims=ntuple(+, min(N, M))) where {T, D, N, M}
     Y = conv(u, v, dims)
     function conv_pullback(barx)
-        z = zero(eltype(u))
         return NoTangent(), conv(barx, conj(v), dims), NoTangent(), NoTangent()
     end 
     return Y, conv_pullback
@@ -156,7 +155,6 @@ end
 function ChainRulesCore.rrule(::typeof(p_conv_aux!), P, P_inv, u, v, u_ft_stor, out)
     Y = p_conv_aux!(P, P_inv, u, v, u_ft_stor, out)
     function conv_pullback(barx)
-        z = zero(eltype(u))
         conj_v = let
             if eltype(v) <: Real
                 v
@@ -172,7 +170,7 @@ function ChainRulesCore.rrule(::typeof(p_conv_aux!), P, P_inv, u, v, u_ft_stor, 
             end
         end
         ∇ = p_conv_aux!(P, P_inv, barx, conj_v, u_ft_stor, copy(out))
-        return NoTangent(), z, z, ∇, z, z, z
+        return NoTangent(), NoTangent(), NoTangent(), ∇, NoTangent(), NoTangent(), NoTangent()
     end 
     return Y, conv_pullback
 end

### 2021-09-22 src/lossfunctions.jl
Fix ChainRulesCore error

@@ -23,12 +23,12 @@ end
  # define custom gradient for speed-up
  # ChainRulesCore offers the possibility to define a backward AD rule
  # which can be used by several different AD systems
-function ChainRulesCore.rrule(::typeof(poisson_aux), μ, meas, storage=similar(μ))
+function ChainRulesCore.rrule(::typeof(poisson_aux), μ, meas, storage)
     Y = poisson_aux(μ, meas, storage)
 
     function poisson_aux_pullback(xbar)
         storage .= xbar .* (one(eltype(μ)) .- meas ./ μ)
-        return NoTangent(), storage, NoTangent(), NoTangent() 
+        return NoTangent(), storage, ChainRulesCore.NotImplemented, ChainRulesCore.NotImplemented 
     end
 
     return Y, poisson_aux_pullback
@@ -60,10 +60,10 @@ function gauss_aux(μ, meas, storage=similar(μ))
 end
 
  # define custom gradient for speed-up
-function ChainRulesCore.rrule(::typeof(gauss_aux), μ, meas, storage=nothing)
+function ChainRulesCore.rrule(::typeof(gauss_aux), μ, meas, storage)
     Y = gauss_aux(μ, meas) 
     function gauss_aux_pullback(xbar)
-        return NoTangent(), 2 .* xbar .* (μ - meas), NoTangent(), NoTangent() 
+        return NoTangent(), 2 .* xbar .* (μ - meas), ChainRulesCore.NotImplemented, ChainRulesCore.NotImplemented 
     end
     return Y, gauss_aux_pullback
 end
@@ -97,12 +97,12 @@ function scaled_gauss_aux(μ, meas, storage=similar(μ); read_var=0)
 end
 
  # define custom gradient for speed-up
-function ChainRulesCore.rrule(::typeof(scaled_gauss_aux), μ, meas, storage=nothing; read_var=0)
+function ChainRulesCore.rrule(::typeof(scaled_gauss_aux), μ, meas, storage; read_var=0)
     Y = scaled_gauss_aux(μ, meas) 
     function scaled_gauss_aux_pullback(xbar)
         ∇ = xbar .* (μ.^2 .- meas.^2 .+ μ .+ read_var.*(1 .- 2 .* (meas .- µ)))./((μ .+read_var).^2)
         ∇[μ .<= 1f-8] .= 0 
-        return NoTangent(), ∇, zero(eltype(μ)), NoTangent(), NoTangent() 
[…]

### 2021-09-22 src/lossfunctions.jl
Fix rrules for loss functions

@@ -28,7 +28,7 @@ function ChainRulesCore.rrule(::typeof(poisson_aux), μ, meas, storage)
 
     function poisson_aux_pullback(xbar)
         storage .= xbar .* (one(eltype(μ)) .- meas ./ μ)
-        return NoTangent(), storage, ChainRulesCore.NotImplemented, ChainRulesCore.NotImplemented 
+        return NoTangent(), storage, (ChainRulesCore.@not_implemented "Save computation"), (ChainRulesCore.@not_implemented "Save computation") 
     end
 
     return Y, poisson_aux_pullback
@@ -63,7 +63,7 @@ end
 function ChainRulesCore.rrule(::typeof(gauss_aux), μ, meas, storage)
     Y = gauss_aux(μ, meas) 
     function gauss_aux_pullback(xbar)
-        return NoTangent(), 2 .* xbar .* (μ - meas), ChainRulesCore.NotImplemented, ChainRulesCore.NotImplemented 
+        return NoTangent(), 2 .* xbar .* (μ - meas), (ChainRulesCore.@not_implemented "Save computation"), (ChainRulesCore.@not_implemented "Save computation") 
     end
     return Y, gauss_aux_pullback
 end
@@ -102,7 +102,7 @@ function ChainRulesCore.rrule(::typeof(scaled_gauss_aux), μ, meas, storage; rea
     function scaled_gauss_aux_pullback(xbar)
         ∇ = xbar .* (μ.^2 .- meas.^2 .+ μ .+ read_var.*(1 .- 2 .* (meas .- µ)))./((μ .+read_var).^2)
         ∇[μ .<= 1f-8] .= 0 
-        return NoTangent(), ∇, zero(eltype(μ)), ChainRulesCore.NotImplemented, ChainRulesCore.NotImplemented 
+        return NoTangent(), ∇, (ChainRulesCore.@not_implemented "Save computation"), (ChainRulesCore.@not_implemented "Save computation"), (ChainRulesCore.@not_implemented "Save computation")
     end
     return Y, scaled_gauss_aux_pullback
 end
@@ -148,7 +148,7 @@ function ChainRulesCore.rrule(::typeof(anscombe_aux), μ, meas, storage; b=1)
     Y = anscombe_aux(μ, meas, storage, b=b)
     function anscombe_aux_pullback(xbar)
             storage .= xbar .* (one(eltype(μ)) .- sqrt.((meas .+ b) ./ (μ.+b)))
[…]

### 2022-08-11 paper/paper.tex
Remove additional file so that paper.tex compiles again
Incoporate review to paper [skip ci]

--- 2021-08-09 paper/paper.tex
@@
 \usepackage{pgfplots}
+% \pgfplotsset{compat=1.17}
 \usepackage{siunitx}
@@
 \end{equation}
-To obtain efficient deconvolution algorithms we also need a efficient way to calculate the convolution operations.
+To obtain efficient deconvolution algorithms we also need an efficient way to calculate the convolution operations.
 Today, convolution operations of spatially small kernels $h$ can be calculated on GPUs very efficiently in real space.
@@
     In this section we show some experiments and compare parts of the software to other solutions.
-    All experiments were executed on Ubuntu 20.04 using a AMD Ryzen 5 5600X 6-Core processor (12 threads) with \SI{32}{GB} DDR4 RAM and Julia 1.6.1.
+All experiments were executed on Ubuntu 20.04 using a AMD Ryzen 5 5600X 6-Core processor (12 threads) with \SI{32}{GB} DDR4 RAM and Julia 1.6.2.
     If possible, all threads were used.
@@
         \end{figure}
-        On the right hand we can see the results of the following deconvolution:
+        On the right hand we can see the results of the following deconvolution.
+    The first statement applies a total padding of $1$ meaning that the size is doubled and therefore the measured data is padded.
+    As we can see, the blue curve in \autoref{fig:1D_datasetb} does not show these intense spikes at the boundaries as the green curve shows.
         \begin{lstlisting}[language=Julia]
@@
         \end{lstlisting}
-    The first statement applies a total padding of $1$ meaning that the size is doubled and therefore the measured data is padded.
-    As we can see, the blue curve in \autoref{fig:1D_datasetb} does not show these intense spikes at the boundaries as the green curve shows.
     Also we notice that the deconvolved data in \autoref{fig:1D_datasetb} does not show all the details which are visible in the ground truth.
@@
         \begin{figure}[h]
-            \begin{subfigure}[b]{.25\textwidth}
+            \begin{subfigure}[b]{.16\textwidth}
                 \centering
-                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_blurry.png}
-                \caption{Measured with Poisson noise}
+                \includegraphics[width=0.99\textwidth]{figures/resolution_test_512.png}
+                %\caption{Ground truth.}
+                \caption{}
+                \label{fig:gt}
+            \end{subfigure}%
+            \begin{subfigure}[b]{.16\textwidth}
+                \centering
+                \includegraphics[width=.99\textwidth]{figures/resolution_test_chart_blurry.png}
+                %\caption{Measured with Poisson noise}
+                \caption{}
                 \label{fig:fabioa}
             \end{subfigure}%
-            \hfill
-            \begin{subfigure}[b]{.25\textwidth}
+            \begin{subfigure}[b]{.16\textwidth}
                 \centering
-                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
-                \caption{Without regularizer $N=50$}
+                \includegraphics[width=.99\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
+                %\caption{Without regularizer $N=50$}
+                \caption{}
                 \label{fig:fabiob}
@@
             \hfill
-            \begin{subfigure}[b]{.25\textwidth}
+            \begin{subfigure}[b]{.16\textwidth}
                 \centering
-                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
-                \caption{Without regularizer $N=10$}
+                \includegraphics[width=0.99\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
+                %\caption{Without regularizer $N=10$}
+                \caption{}
                 \label{fig:fabioc}
             \end{subfigure}%            
-            \hfill
-            \begin{subfigure}[b]{.25\textwidth}
+            \begin{subfigure}[b]{.16\textwidth}
                 \centering
-                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
-                \caption{With regularizer $N=24$.}
+                \includegraphics[width=0.99\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
+                %\caption{With regularizer $N=24$.}
+                \caption{}
                 \label{fig:fabiod}
             \end{subfigure}%            
-            \caption{a) has been convolved with a PSF and affected by Poisson shot noise (100 photons expected for the brightest pixel). 
-                        Deconvolved b) for 50 iterations without a regularizer c) for 10 iterations without a regularizer d) with Good's roughness regularizer and 
-                            converged after 24 iterations with $\lambda=0.03$.}
+            \caption{a) is the ground truth image. b) has been convolved with a PSF and affected by Poisson shot noise (100 photons expected for the brightest pixel). 
+            c) is deconvolved for 50 iterations without a regularizer, d) for 10 iterations without a regularizer. e) converged with Good's roughness regularizer and 
+                            after 24 iterations with $\lambda=0.03$.}
             \label{fig:image}
@@
         have decreasing spacing towards its middle which is equivalent to higher spatial frequencies.
-        \autoref{fig:fabioc} shows the result after 50 iterations of the deconvolution. 
-        We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.
+        \autoref{fig:fabiob} shows the result after 50 iterations of the deconvolution. 
+        We see that the image is heavily affected by some artifacts (the dotted patterns) which usually occur after too many iterations without a regularizer.
         Additionally, we notice that the core in the Siemens star is denser 
@@
         To more completely demonstrate the features available in \verb|DeconvOptim.jl|,
-        we deconvolve a four dimensional dataset where the measured volume consists of a 3D datasets
+        we deconvolve a four dimensional (three spatial dimensions and a color dimension) dataset where the measured volume consists of a 3D datasets
         with three different color channels, shown in \autoref{fig:result_3d}.
@@
             being able to 
-            use of all threads whereas Julia's built in broadcast mechanism is not multi threaded.
+            use of threads whereas Julia's built in broadcast mechanism is not multi threaded.
             By \textit{plain Julia} we are referring to an implementation which is written with standard Julia Base functions.
@@
                 \end{tabular}
-                \caption{Runtimes of a single Total Variation regularizer calculation for different Julia versions and JAX. 
+                \caption{Runtimes of a single Total Variation regularizer calculation for different Julia versions and JAX. $\nabla$ indicates the gradient calculation. 
                     We used a 3 dimensional Float32 array with size $300 \times 300 \times 300$.  }
@@
         \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
-        \todo{anscombe norm speed}
-        \todo{Fix table }
         \begin{table}[h]
@@
             \verb|GenericDeconv| TV & Poisson & 45 \\
-            \verb|Huygens| & & \\
+            \verb|Huygens| & Poisson & 25\\
             \verb|DeconvolutionLab2| LR & Poisson & 300\\
@@
     occur with FFT based convolutions.
-    Julia's metaprogramming capabilities together with \verb|Tullio.jl| allow to generate regularizer which have high performance
+    Julia's metaprogramming capabilities together with \verb|Tullio.jl| allow to generate regularizers which have high performance
     and are easy to adapt.
@@
     us how to adjust the settings to get optimal performance. 
-
+\newpage
 \input{bib.tex}

### 2022-08-11 paper/paper.tex
Fix code listing wrap [skip ci]
Convert figures to PDF to avoid including issue with whedon [skip ci]

@@
 \usepackage{pgfplots}
-% \pgfplotsset{compat=1.17}
+\pgfplotsset{compat=newest}
 \usepackage{siunitx}
@@
 \newcommand\todo[1]{\textcolor{red}{\textbf{TODO: #1}}}
+
+%\usetikzlibrary{external}
+%\tikzexternalize[prefix=figures/]
+
 \begin{document}
@@
         \begin{split}
-            \text{Reg}(S(\mathbf r)) = \sum_{x,y} \big[& |S(x + 1, y) - S(x, y)|^2 \\ 
+            \text{Reg}(S(\mathbf r)) = \sum_{x,y} \big[& |S(x + 1, y) - S(x, y)|^2 \\[-0.4cm] 
                                                 & + |S(x, y + 1) - S(x, y)|^2\big]^{\frac12}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/1d_plot_data_blurred.pdf}
+                \includegraphics[width=\textwidth]{figures/1d_plot_data_blurred.png}
                 \caption{}
@@
                 \centering
-                \includegraphics[width=\textwidth]{figures/1d_plot_data_res_pad_vs_nopad.pdf}
+                \includegraphics[width=\textwidth]{figures/1d_plot_data_res_pad_vs_nopad.png}
                 \caption{}
@@
                 \centering
-                \includegraphics[width =\textwidth]{figures/test_chart_relative_energy_regain.pdf}
+                \includegraphics[width =\textwidth]{figures/test_chart_relative_energy_regain.png}
                 \caption{REG $G_\textrm{R}$ over different frequencies.}
@@
                 \centering
-                \includegraphics[width =1 \textwidth]{figures/test_chart_ncc.pdf}
+                \includegraphics[width =1 \textwidth]{figures/test_chart_ncc.png}
                 \caption{NCC over the number of iterations.}

### 2022-09-28 src/DeconvOptim.jl
Include SnoopPrecompile to speed up TTFP

@@ -27,8 +27,7 @@ using LinearAlgebra
 
 using FillArrays
 
-gpu_or_cpu(x) = Array
-
+using SnoopPrecompile
 
 
 include("forward_models.jl")
@@ -46,6 +45,20 @@ include("analysis_tools.jl")
 
 # refresh Zygote to load the custom rrules defined with ChainRulesCore
 using Zygote: gradient
+
+
+# doesn't save too much but a little
+@precompile_setup begin
+    img = abs.(randn((4,4,2)))
+    psf = abs.(randn((4,4,2)))
+
+    @precompile_all_calls begin
+        deconvolution(Float32.(img), Float32.(psf), regularizer=TV(num_dims=3), iterations=2)
+        deconvolution(img, psf, regularizer=TV(num_dims=3), iterations=2)
+
+    end
+
+end
 
 
 # end module

### 2022-09-28 test/runtests.jl
Fix tests

@@ -12,7 +12,6 @@ Random.seed!(42)
 
 
 @testset "Utils" begin
-    @test gpu_or_cpu(randn((2,2))) == Array
     include("utils.jl")
 end
 

### 2022-11-14 paper/paper.tex
Add feedback from reviewer

@@
 \end{equation}
-where $*$ denotes a convolution operation.
+where $*$ denotes a convolution operation. $I$ indicates the ideal measured image. $\mathbf r$ is the position vector or the pixel positions in the discrete case.
 $h$ is often called the point spread function (PSF) since it characterizes how the systems maps a point in the object to a blurred spot 
@@
         For a 2D dataset with size $N \times M$ it is $\mathcal{O}(N \cdot M \log(N \cdot M))$ and accordingly for higher dimensions.
-        Spatially based convolution kernels with size $K \times L$ applied on an image with
+        Real space based convolution kernels with size $K \times L$ applied on an image with
         $N \times M$ data points have a runtime of $\mathcal O(N \cdot M \cdot K \cdot L)$.
@@
     One drawback of a FFT based convolution are wrap-around artifacts (see arrow in \autoref{fig:withoutpad}). The reason is, that the FFT operation calculates the discrete
-    Fourier transform (DFT) which inherently assumes periodic data. If one applies a FFT on a finite data set the assumption is that
-    this finite data set repeats itself. 
+    Fourier transform (DFT) which inherently assumes periodic data. If one applies a FFT on a finite object the assumption is that
+    this finite object repeats itself. 
     To weaken the wrap-around artifacts in the convolution one can zero or mean pad the image before convolution 
@@
 
-As typical for Julia packages, except \verb|FFTW.jl| and \verb|CUDA.jl| \cite{besard2018juliagpu}, \cite{LLVM.jl-2017}, all code is written in Julia.
+Except \verb|FFTW.jl| and \verb|CUDA.jl| \cite{besard2018juliagpu}, the entire package is written in Julia.
 Therefore it is easy to replace the forward model with any Julia code, as long as we can 
@@
 \section{Loss Function}
-    Apart from forward model, the loss function is the most critical part in the optimization.
+    Apart from the forward model, the loss function is the most critical part in the optimization.
     It has to account for the noise created by the measurement process or instrument.
@@
     Most real samples are smooth over large regions and such regularizers enhance the quality of the reconstruction.
-    In our toolbox we currently implement several regularizer like (smoothed) Total variation, Good's roughness \cite{Verveer:98}, \cite{Good:71} and Tikhonov. 
+    In our toolbox we currently implement several regularizer like (smoothed) Total Variation, Good's roughness \cite{Verveer:98}, \cite{Good:71} and Tikhonov. 
     \subsubsection{Total Variation as example}
-        As the name suggests, Total variation tries to penalize variation in the image intensity. Therefore it sums up the gradient strength at each point
+        As the name suggests, Total Variation tries to penalize variation in the image intensity. Therefore it sums up the gradient strength at each point
         of the image:
@@
         \end{equation}
-        In many frameworks such a regularizer is implemented via functions like \lstinline{circshift}. 
+        In many frameworks, such a regularizer is implemented via functions like \lstinline{circshift}. 
         However, such approaches create often several copies of the data. 
@@
         to the gradient calculation which have been used for the regularizer evaluation itself.
-        A (smoothed) Total variation with \verb|Tullio.jl| is defined here:
+        A (smoothed) Total Variation with \verb|Tullio.jl| is defined here:
         \begin{lstlisting}[language = Julia]

### 2022-11-16 paper/paper.tex
Update paper

@@
                 \begin{tabular}{l l l l l}
-                    & plain & $\nabla$ plain & \verb|Tullio.jl| & $\nabla$ \verb|Tullio.jl| \\
+                a) & plain & $\nabla$ plain & \verb|Tullio.jl| & $\nabla$ \verb|Tullio.jl| \\
                 \hline
-                CPU & \SI{83.9}{\milli\second} & \SI{7180}{\milli\second} & \SI{5.53}{\milli\second}  & \SI{119.8}{\milli\second}   \\ 
-                GPU & \SI{2.5}{\milli\second}  & \SI{22.9}{\milli\second}& \SI{4.00}{\milli\second}  & \SI{12530}{\milli\second} \\
+                CPU & \SI{84}{\milli\second} & \SI{1.1}{\second} & \SI{4.8}{\milli\second}  & \SI{117}{\milli\second}   \\ 
+                GPU & \SI{3.2}{\milli\second}  & \SI{30}{\milli\second}& \SI{3.4}{\milli\second}  & \SI{13.7}{\second} \\
                 \hline
@@
                 \hline
-                CPU & \SI{48}{\milli\second}   & \SI{364}{\milli\second}&   & \\
-                GPU & \SI{0.887}{\milli\second}   & \SI{10.2}{\milli\second}&   &
+                CPU & \SI{49}{\milli\second}   & \SI{360}{\milli\second}&   & \\
+                GPU & \SI{1.06}{\milli\second}   & \SI{11.4}{\milli\second}&   \\
+                \hline
+                &&&&\\
+                b)    & plain & $\nabla$ plain & \verb|Tullio.jl| & $\nabla$ \verb|Tullio.jl| \\
+                \hline
+                CPU & \SI{390}{\micro\second} & \SI{2.7}{\milli\second} & \SI{19.5}{\micro\second}  & \SI{533}{\micro\second}   \\ 
+                GPU & \SI{45}{\micro\second}  & \SI{470}{\micro\second}& \SI{51.0}{\micro\second}  & \SI{450}{\micro\second} \\
+                \hline
+                \hline
+                    & JAX & $\nabla$ JAX && \\
+                \hline
+                CPU & \SI{150}{\micro\second}   & \SI{1.31}{\milli\second}&   & \\
+                GPU & \SI{26}{\micro\second}   & \SI{885}{\micro\second}&   &
+
                 \end{tabular}
                 \caption{Runtimes of a single Total Variation regularizer calculation for different Julia versions and JAX. $\nabla$ indicates the gradient calculation. 
-                    We used a 3 dimensional Float32 array with size $300 \times 300 \times 300$.  }
+                    For a) we used a 3 dimensional Float32 array with size $300 \times 300 \times 300$. For b) the size was $512 \times 512$.}
                 \label{tab:reg}

### 2022-11-21 paper/paper.tex
Update references section

@@
     As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.
-    Our experiments additionally made use of the following packages in Julia 1.6.2: ArrayInterface.jl\cite{DifferentialEquations.jl-2017}, 
-    BenchmarkTools.jl\cite{BenchmarkTools.jl-2016}, FFTW.jl\cite{FFTW05}, LLVM.jl\cite{LLVM.jl-2017}, Optim.jl\cite{mogensen2018optim}
-    and  Zygote.jl\cite{Zygote.jl-2018}. 
+    Our experiments were done in Julia 1.6.2 under the use of BenchmarkTools.jl\cite{BenchmarkTools.jl-2016}.
+
     \subsection{One-Dimensional Time Series}

### 2024-02-10 paper/paper.tex
Fix style of BenchmarkTools.jl [skip ci]

@@
         In many frameworks, such a regularizer is implemented via functions like \lstinline{circshift}. 
-        However, such approaches create often several copies of the data. 
-        We currently use \verb|Tullio.jl|\cite{michael_abbott_2021_5047410} to create efficient functions 
-        calculating the regularizer and the gradient. For simple expressions
-        such as below, \verb|Tullio.jl| registers an analytical gradient and therefore allows to apply the same efficient mechanisms 
-        to the gradient calculation which have been used for the regularizer evaluation itself.
-        A (smoothed) Total Variation with \verb|Tullio.jl| is defined here:
-        \begin{lstlisting}[language = Julia]
+        \begin{lstlisting}[language = Julia, caption={Smoothed Total Variation \label{algo1}}]
 function total_variation(arr, ϵ=eltype(arr)(1e-8))
@@
         \end{lstlisting}
+        However, such approaches create often several copies of the data. 
+        We currently use \verb|Tullio.jl| \cite{michael_abbott_2021_5047410} to create efficient functions 
+        calculating the regularizer and the gradient. For simple expressions
+        such as below, \verb|Tullio.jl| registers an analytical gradient and therefore allows to apply the same efficient mechanisms 
+        to the gradient calculation which have been used for the regularizer evaluation itself.
+        A (smoothed) Total Variation with \verb|Tullio.jl| is defined in \autoref{algo1}.
         \lstinline{ϵ} is needed for regions where \lstinline{arr == 0} because otherwise the gradient returns infinite values.
@@
         different weighting in dimensions via Julia's metaprogramming capability.
+
         A call like 
@@
     As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.
-    Our experiments were done in Julia 1.6.2 under the use of BenchmarkTools.jl\cite{BenchmarkTools.jl-2016}.
+    Our experiments were done in Julia 1.6.2 under the use of \texttt{BenchmarkTools.jl}\cite{BenchmarkTools.jl-2016}.
 
